### 2019-02-10 STAT0030_ICA2/STAT0030_ICA2.Rmd
STAT0039 Rmd to PDF test
Rmd to PDF test

---
title: "STAT0030_ICA2"
author: "Hongwei Peng"
date: "10/02/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-02-11 STAT0030_ICA2/STAT0030_ICA2.R
PDF create

@@ -1,0 +1,5 @@
+rawdata <- read.table("/Users/hongwei/Documents/GitHub/STAT/STAT0030_ICA2/cars.dat",header=TRUE) #input data question_1_a
+summary(rawdata)
+plot(rawdata,main="Plot Between all Variables") #
+logdata <- cbind(rawdata[,1],log(rawdata[,c(2,3,4)])) #log data
+sunflowerplot(rawdata)

### 2019-02-17 STAT0030_ICA2/STAT0030_ICA2.Rmd
PDF create
STAT0030_begin

@@
 date: "10/02/2019"
-output: pdf_document
+output:
+  pdf_document: default
+  html_document:
+    df_print: paged
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
 
@@
 
-```{r pressure, echo=FALSE}
+```{r pressure, echo=TRUE}
 plot(pressure)
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+
+```{r table}
+library(knitr)
+kable(cars)
+```
+
+```{r table2}
+kable(PlantGrowth, col.names=c("Weight", "Group"), align=c("c","c"), 
+      caption = "Table 2. Plant Growth Data")#this is a test
+```

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
vision 1

@@
 
-## R Markdown
+# R Question 1
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+## Question 1a read the data
+```{R question_1_a}
+setwd('/Users/hongwei/Documents/GitHub/STAT/STAT0030_ICA2')
+rawdata <- read.table("cars.dat", #input data
+                      header=TRUE) #the first line as the names of the variables 
 ```
 
-## Including Plots
+##  Question 1b
 
-You can also embed plots, for example:
-
-```{r pressure, echo=TRUE}
-plot(pressure)
+```{R question_1_b}
+summary(rawdata)
+table(rawdata$tr)
+plot(rawdata,main="Plot Between all Variables") #overlook
+pairs(rawdata[,2:4], # plot hp, wt, mpg 
+      main = "Plot Between all Variables -- 3 species", #add the main title
+      pch = c(21,24)[unclass(rawdata$tr)+1], #different tr shows different shape
+      bg = c("red", "green3")[unclass(rawdata$tr)+1]) #different tr shows different colour
+logdata <- cbind(rawdata[,1],log(rawdata[,c(2,3,4)])) #log the data
+names(logdata) <- c("tr","hp","wt","mpg")#rename the names of the variables 
+plot(logdata,main="Plot Between log Variables") #overlook
+pairs(logdata[,2:4], # plot log(hp), log(wt), log(mpg)
+      main = "Plot Between log Variables -- 3 species", #add the main title
+      pch = c(21,24)[unclass(logdata$tr)+1], #different tr shows different shape
+      bg = c("red", "green3")[unclass(logdata$tr)+1]) #different tr shows different colour
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+##  question 1c
 
-```{r table}
-library(knitr)
-kable(cars)
+```{R question_1_c}
+boxplot(mpg~tr, #MPG by TR
+        data=rawdata, #set the dataset
+        xlab="Gear Transmission Type" , #add the xlab title
+        ylab="Miles Per Gallon", #add the ylab title
+        main="MPG by Gear Transmission Type", #add the main title
+        names=c("Automatic","Manual")) #change xlab value to character
+t.test(mpg~tr, data=logdata)
+model<-lm(mpg~tr+hp+wt, data=logdata); # i.e, full without qsec and gears
+summary(model)
+summary(model$residuals)
+par(mfrow=c(2,2))
+plot(model)
+
+best<-step(model, direction="both")
+summary(best)
+summary(best$residuals)
+par(mfrow=c(2,2))
+plot(best)
+
 ```
-
-```{r table2}
-kable(PlantGrowth, col.names=c("Weight", "Group"), align=c("c","c"), 
-      caption = "Table 2. Plant Growth Data")#this is a test
-```

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
Hongwei
vision  2 question 1 c

@@
   pdf_document: default
+  word_document: default
   html_document:
@@
 summary(model$residuals)
-par(mfrow=c(2,2))
-plot(model)
+par(mfrow=c(2,2)) #put 4 graphes together
+plot(model) #plot 4 graphes as following
 
@@
 summary(best$residuals)
-par(mfrow=c(2,2))
-plot(best)
+par(mfrow=c(2,2)) #put 4 graphes together
+plot(best)#plot 4 graphes as following
 

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.R
Update STAT0030_ICA2.R

@@ -1,5 +1,39 @@
-rawdata <- read.table("/Users/hongwei/Documents/GitHub/STAT/STAT0030_ICA2/cars.dat",header=TRUE) #input data question_1_a
+#question_1_a
+setwd('/Users/hongwei/Documents/GitHub/STAT/STAT0030_ICA2')
+rawdata <- read.table("cars.dat", #input data
+                      header=TRUE) #the first line as the names of the variables 
+#question_1_b
 summary(rawdata)
-plot(rawdata,main="Plot Between all Variables") #
-logdata <- cbind(rawdata[,1],log(rawdata[,c(2,3,4)])) #log data
-sunflowerplot(rawdata)
+table(rawdata$tr)
+plot(rawdata,main="Plot Between all Variables") #overlook
+pairs(rawdata[,2:4], # plot hp, wt, mpg 
+      main = "Plot Between all Variables -- 3 species", #add the main title
+      pch = c(21,24)[unclass(rawdata$tr)+1], #different tr shows different shape
+      bg = c("red", "green3")[unclass(rawdata$tr)+1]) #different tr shows different colour
+logdata <- cbind(rawdata[,1],log(rawdata[,c(2,3,4)])) #log the data
+names(logdata) <- c("tr","hp","wt","mpg")#rename the names of the variables 
+plot(logdata,main="Plot Between log Variables") #overlook
+pairs(logdata[,2:4], # plot log(hp), log(wt), log(mpg)
+      main = "Plot Between log Variables -- 3 species", #add the main title
+      pch = c(21,24)[unclass(logdata$tr)+1], #different tr shows different shape
+      bg = c("red", "green3")[unclass(logdata$tr)+1]) #different tr shows different colour
+
+boxplot(mpg~tr, #MPG by TR
+        data=rawdata, #set the dataset
+        xlab="Gear Transmission Type" , #add the xlab title
+        ylab="Miles Per Gallon", #add the ylab title
+        main="MPG by Gear Transmission Type", #add the main title
+        names=c("Automatic","Manual")) #change xlab value to character
+t.test(mpg~tr, data=logdata)
+model<-lm(mpg~tr+hp+wt, data=logdata); # i.e, full without qsec and gears
+summary(model)
+summary(model$residuals)
+par(mfrow=c(2,2)) #put 4 graphes together
+plot(model) #plot 4 graphes as following
+
+best<-step(model, direction="both")
+summary(best)
[…]

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.R
Update STAT0030_ICA2.R

@@ -17,23 +17,27 @@ pairs(logdata[,2:4], # plot log(hp), log(wt), log(mpg)
       main = "Plot Between log Variables -- 3 species", #add the main title
       pch = c(21,24)[unclass(logdata$tr)+1], #different tr shows different shape
       bg = c("red", "green3")[unclass(logdata$tr)+1]) #different tr shows different colour
-
 boxplot(mpg~tr, #MPG by TR
         data=rawdata, #set the dataset
         xlab="Gear Transmission Type" , #add the xlab title
         ylab="Miles Per Gallon", #add the ylab title
         main="MPG by Gear Transmission Type", #add the main title
         names=c("Automatic","Manual")) #change xlab value to character
-t.test(mpg~tr, data=logdata)
+t.test(mpg~tr, data=logdata)# the t-test above MPG is related to TR.
+
+#question_1_c
 model<-lm(mpg~tr+hp+wt, data=logdata); # i.e, full without qsec and gears
 summary(model)
 summary(model$residuals)
 par(mfrow=c(2,2)) #put 4 graphes together
-plot(model) #plot 4 graphes as following
-
+plot(model) #plot 4 graphes as following. 
+#ddition: if you run the last line code directly, there will be an error "figure margins too large".
+#there two way to fix it: 1, click "clear all plots" and then run it. 
+#                         2, run >>x11() at first if you are run in Windows computer.
+#BTW: there is no error if i use it in R Markdown
 best<-step(model, direction="both")
 summary(best)
 summary(best$residuals)
 par(mfrow=c(2,2)) #put 4 graphes together
-plot(best)#plot 4 graphes as following
+plot(best)#there will be the same error as line 33 and line 34-36 is the solvtion.
 

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
finished question 1 abc

--- 2019-02-17 STAT0030_ICA2/STAT0030_ICA2.Rmd
@@
 
-## R Markdown
+# R Question 1
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+## Question 1a read the data
+```{R question_1_a}
+rawdata <- read.table("cars.dat", #input data
+                      header=TRUE) #the first line as the names of the variables 
 ```
 
-## Including Plots
+##  Question 1b
 
-You can also embed plots, for example:
-
-```{r pressure, echo=TRUE}
-plot(pressure)
+```{R question_1_b}
+summary(rawdata)
+table(rawdata$tr)
+logdata <- cbind(rawdata[,1],log(rawdata[,c(2,3,4)])) #log the data
+names(logdata) <- c("tr","hp","wt","mpg")#rename the names of the variables 
+pairs(logdata[,2:4], # plot log(hp), log(wt), log(mpg)
+      main = "Plot Between log Variables -- 3 species", #add the main title
+      pch = c(21,24)[unclass(logdata$tr)+1], #different tr shows different shape
+      bg = c("red", "green3")[unclass(logdata$tr)+1]) #different tr shows different colour
+boxplot(mpg~tr, #MPG by TR
+        data=rawdata, #set the dataset
+        xlab="Gear Transmission Type" , #add the xlab title
+        ylab="Miles Per Gallon", #add the ylab title
+        main="MPG by Gear Transmission Type", #add the main title
+        names=c("Automatic","Manual")) #change xlab value to character
+t.test(mpg~tr, data=logdata)# the t-test above MPG is related to TR.
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+##  question 1c
 
-```{r table}
-library(knitr)
-kable(cars)
+```{R question_1_c}
+rawdata_model<-lm(mpg~tr+hp+wt, data=rawdata) #rawdata linear model
+logdata_model<-lm(mpg~tr+hp+wt, data=logdata) #logdata linear model
+summary(rawdata_model)
+summary(logdata_model)
+summary(logdata_model$residuals)
+best_model<-step(logdata_model, direction="both")
+summary(best_model)
+summary(best_model$residuals)
+par(mfrow=c(2,2)) #put 4 graphes together
+plot(best_model)#plot 4 graphes as following. 
+#addition: if you run the last line code directly, there will be an error "figure margins too large".
+#there two way to fix it: 1, click "clear all plots" and then run it. 
+#                         2, run >>x11() at first if you are run in Windows computer.
+#BTW: there is no error if i use it in R Markdown
+
 ```
-
-```{r table2}
-kable(PlantGrowth, col.names=c("Weight", "Group"), align=c("c","c"), 
-      caption = "Table 2. Plant Growth Data")#this is a test
-```

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.R

@@ -1,7 +1,8 @@
+#SN:17052480
 #question_1_a
-setwd('/Users/hongwei/Documents/GitHub/STAT/STAT0030_ICA2')
 rawdata <- read.table("cars.dat", #input data
                       header=TRUE) #the first line as the names of the variables 
+
 #question_1_b
 summary(rawdata)
 table(rawdata$tr)
@@ -31,7 +32,7 @@ summary(model)
 summary(model$residuals)
 par(mfrow=c(2,2)) #put 4 graphes together
 plot(model) #plot 4 graphes as following. 
-#ddition: if you run the last line code directly, there will be an error "figure margins too large".
+#addition: if you run the last line code directly, there will be an error "figure margins too large".
 #there two way to fix it: 1, click "clear all plots" and then run it. 
 #                         2, run >>x11() at first if you are run in Windows computer.
 #BTW: there is no error if i use it in R Markdown
@@ -39,5 +40,5 @@ best<-step(model, direction="both")
 summary(best)
 summary(best$residuals)
 par(mfrow=c(2,2)) #put 4 graphes together
-plot(best)#there will be the same error as line 33 and line 34-36 is the solvtion.
+plot(best)#there will be the same error as "plot(model)" and above addition is the solvtion.
 

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
ICA +1

--- 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
@@
 author: "Hongwei Peng"
-date: "10/02/2019"
+date: "Student_Number:17052480"
 output:
-  pdf_document: default
+  pdf_document: 
+    fig_caption: yes
+  word_document: default
   html_document:
@@
 
-## Question 1a read the data
+## Question 1(a)
 ```{R question_1_a}
-setwd('/Users/hongwei/Documents/GitHub/STAT/STAT0030_ICA2')
 rawdata <- read.table("cars.dat", #input data
@@
 ```
+**Read the data into R.
+**
 
-##  Question 1b
+ &nbsp;
 
-```{R question_1_b}
+##  Question 1(b)
+
+```{R question_1_b.1}
 summary(rawdata)
 table(rawdata$tr)
-plot(rawdata,main="Plot Between all Variables") #overlook
-pairs(rawdata[,2:4], # plot hp, wt, mpg 
-      main = "Plot Between all Variables -- 3 species", #add the main title
-      pch = c(21,24)[unclass(rawdata$tr)+1], #different tr shows different shape
-      bg = c("red", "green3")[unclass(rawdata$tr)+1]) #different tr shows different colour
+```
+
+**From this result, it shows that there are four variables. The range of the values between the last three variables is relatively large, so it is necessary to log the original data.
+From the table results, the sample is divided into manual and automatic transmissions, of which 19 are automatic and 13 are manual.
+**
+
+ &nbsp;
+
+```{R question_1_b.2, warning=FALSE}
 logdata <- cbind(rawdata[,1],log(rawdata[,c(2,3,4)])) #log the data
 names(logdata) <- c("tr","hp","wt","mpg")#rename the names of the variables 
-plot(logdata,main="Plot Between log Variables") #overlook
 pairs(logdata[,2:4], # plot log(hp), log(wt), log(mpg)
-      main = "Plot Between log Variables -- 3 species", #add the main title
+      main = "Plot Between log Variables", #add the main title
       pch = c(21,24)[unclass(logdata$tr)+1], #different tr shows different shape
@@
 
-##  question 1c
-
-```{R question_1_c}
+```{R question_1_b.3, fig.height=3, fig.width=6, warning=FALSE}
+par(mfrow=c(1,3))
+boxplot(hp~tr, #HP by TR
+        data=rawdata, #set the dataset
+        xlab="Gear Transmission Type" , #add the xlab title
+        ylab="Horsepower", #add the ylab title
+        main="GP by TR", #add the main title
+        names=c("Automatic","Manual")) #change xlab value to character
+boxplot(wt~tr, #WT by TR
+        data=rawdata, #set the dataset
+        xlab="Gear Transmission Type" , #add the xlab title
+        ylab="Weight of the Car in Pounds", #add the ylab title
+        main="WT by TR", #add the main title
+        names=c("Automatic","Manual")) #change xlab value to character
 boxplot(mpg~tr, #MPG by TR
@@
         ylab="Miles Per Gallon", #add the ylab title
-        main="MPG by Gear Transmission Type", #add the main title
+        main="MPG by TR", #add the main title
         names=c("Automatic","Manual")) #change xlab value to character
-t.test(mpg~tr, data=logdata)
-model<-lm(mpg~tr+hp+wt, data=logdata); # i.e, full without qsec and gears
-summary(model)
-summary(model$residuals)
-par(mfrow=c(2,2))
-plot(model)
+```
 
-best<-step(model, direction="both")
-summary(best)
-summary(best$residuals)
-par(mfrow=c(2,2))
-plot(best)
+**The box plot shows a significant change between the automatic and manual gears between the various variables.
+**
 
+ &nbsp;
+
+```{R question_1_b.4}
+t.test(mpg~tr, data=logdata)# the t-test above MPG is related to TR.
 ```
+
+##  question 1(c)
+
+```{R question_1_c.1}
+rawdata_model<-lm(mpg~tr+hp+wt, data=rawdata) #rawdata linear model
+summary(rawdata_model)
+logdata_model<-lm(mpg~tr+hp+wt, data=logdata) #logdata linear model
+summary(logdata_model)
+```
+```{R question_1_c.2, message=FALSE, warning=FALSE,results = 'hide'}
+best_model<-step(logdata_model, direction="both")
+```
+```{R question_1_c.3}
+summary(best_model)
+par(mfrow=c(2,2)) #put 4 graphes together
+plot(best_model)#plot 4 graphes as following. 
+```

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.Rmd
finish question1

@@
 
-```{R question_1_b.3, fig.height=3, fig.width=6, warning=FALSE}
+**We can see from the plot that the point group by TR is significantly different in the other three variables, but the  plot is not easy to see what kind of specific difference it is.
+So next step we will do boxplots.
+**
+
+ &nbsp;
+
+```{R question_1_b.3, fig.height=3, fig.width=6, warning=FALSE,echo=FALSE}
 par(mfrow=c(1,3))
@@
 
-**The box plot shows a significant change between the automatic and manual gears between the various variables.
+**The box plot shows a significant change between the automatic and manual gears between three variables. The automatic cars have higher HP and WT. And the manual cars have the higher MPG.
 **
@@
 
+**In fact, we can infer from the t-test that the MPG is related to the TR.
+According to Two Sample t-test, the p-value is less than 0.01, so we should reject the null hypothesis and conclude: The manual transmission car has the better fuel efficiency in miles per gallon than the automatic transmission car.
+However, this t-test cannot prove that the TR is the only significant variables for the MPG.
+We need to add more variables for regression to get more accurate results.
+In other words, the type of transmission may be linearly related to other variables, such as the weight of the car, so we need to make more regressions to ensure a better explanation of the change in the MPG.
+**
+
+ &nbsp;
+
 ##  question 1(c)
 
+**Through computing, it is easy to find: each of the variables has a statistically significant relationship with the MPG.
+Because the results are too much, so there is no result displayed here.
+Firstly, MPG is regressed with all variables to observe the effect of the overall regression.
+**
 ```{R question_1_c.1}
@@
 ```
+**This two regression shows logdata has better R-squared and p-value than rawdata. This means logarithm of rawdata has better performance in regeression and logdata will be used as following.
+**
+
+ &nbsp;
+
+**
+From the regression, we can know a variable is not significant to the MPG. So using stepwise regression to distinguish significant variables.
+**
 ```{R question_1_c.2, message=FALSE, warning=FALSE,results = 'hide'}
@@
 summary(best_model)
+```
+```{R question_1_c.4, echo=FALSE}
+cat("The final model is  \n                 MPG = ",
+    best_model$coefficients[1],
+    best_model$coefficients[2],"*HP",
+    best_model$coefficients[2],"*WT")
+```
+**According to the stepwise regression, the transmission type was moved out in this regression, and MPG was related to HP and WT.
+Therefore, we can not determine whether the type of transmission has a significant influence on MPG.
+**
+
+ &nbsp;
+
+##  question 1(d)
+```{R question_1_d}
 par(mfrow=c(2,2)) #put 4 graphes together
@@
 ```
+
+**Residuals looks like normally distributed, independent, random and has no outliers. This means the result of regression is accepted.
+**
+
+ &nbsp;
+
+ **Conclution:After adding the HP and the WT, the gear transmission type disappears.
+So we are not sure if the gear transmission type has an significant effect on the MPG.
+According to the regression result, we can conclude that the MPG decreases as the HP rises and the WT rises.
+**

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.2.R
ICA.2

@@ -1,0 +1,17 @@
+#SN:17052480
+#question_2_a
+rawdata <- read.table("osl.dat", #input data
+                      header=TRUE) #the first line as the names of the variables 
+
+#question_2_b
+par(mfrow=c(2,1))
+plot(rawdata$se,rawdata$de
+     xlab="Gear Transmission Type" , #add the xlab title
+     ylab="Horsepower", #add the ylab title
+     main="GP by TR" )#add the main title
+hist(rawdata$de)
+text(3,40,paste0("the number of grains is ",length(rawdata$de),
+                 "\nthe mean of the equivalent doses is ",format(mean(rawdata$de),digits = 4),
+                 "\nthe standard deviation of the equivalent doses is ",format(sd(rawdata$de),digits = 4)))
+
+     

### 2019-02-18 STAT0030_ICA2/17052480.R
the Ending

@@ -1,0 +1,40 @@
+#SN:17052480
+#question_2_a
+rawdata <- read.table("osl.dat", #input data
+                      header=TRUE) #the first line as the names of the variables 
+
+#question_2_b
+par(mfrow=c(2,1))
+plot(rawdata$de,rawdata$se,
+     ylab="Standard Errors" , #add the ylab title
+     xlab="Equivalent Dose", #add the xlab title
+     main="Standard Errors against Equivalent Dose" )#add the main title
+hist(rawdata$de,
+     xlab="Equivalent Dose" , #add the xlab title
+     main="Equivalent Dose by Frequency" )#add the main title
+text(3,40,paste0("the number of grains is ",length(rawdata$de),
+                 "\nthe mean of the equivalent doses is ",format(mean(rawdata$de),digits = 4),
+                 "\nthe standard deviation of the equivalent doses is ",format(sd(rawdata$de),digits = 4)))
+     
+#question_2_c
+negll <- function(params,dat) {
+  l <- -0.5*sum(log(params[2]^2+dat[,2]^2)+
+                  (dat[,1]-params[1])^2/(params[2]^2+dat[,2]^2)) #the log-likelihood omitting the constant term
+  return(-l) #the negative log-likelihood
+}
+
+#question_2_d
+dat <- rawdata[,c(2,3)]
+params1 <- c(mean(rawdata[,2]),sd(rawdata[,2])) #params1 use the sd(rawdata[,2])
+cat("the the negative log-likelihood value by params1 is ",negll(params1,dat))
+params2 <- c(mean(rawdata[,2]),mean(rawdata[,3])) #params2 use the mean(rawdata[,3])
+cat("the the negative log-likelihood value by params2 is ",negll(params2,dat))
+
+#question_2_e
+est <- nlm(negll,c(1,5),dat=rawdata[,c(2,3)],hessian=T) #nlm estimation
+utils::str(nlm(negll,c(1,5),dat=rawdata[,c(2,3)]),hessian=T) #control the output
+cat("the estimates of μ and σ are ",est$estimate[1]," and ",est$estimate[2])
+
+#question_2_f
+se<-diag(solve(est$hessian)) #the parameters standard errors for these estimates
+cat("the μ and σ standard errors for these estimates are ",se[1]," and ",se[2])

### 2019-02-18 STAT0030_ICA2/STAT0030_ICA2.2.R
the ending clean

@@ -38,3 +38,4 @@ cat("the estimates of μ and σ are ",est$estimate[1]," and ",est$estimate[2])
 #question_2_f
 se<-diag(solve(est$hessian)) #the parameters standard errors for these estimates
 cat("the μ and σ standard errors for these estimates are ",se[1]," and ",se[2])
+

### 2019-02-19 STAT0030_ICA2/STAT0030_ICA2.2.Rmd

---
title: "STAT0030_ICA2"
author: "Hongwei Peng"
date: "Student_Number:17052480"
output:
  pdf_document: 
    fig_caption: yes
  word_document: default
  html_document:
    df_print: paged
---

# R Question 1
##question_2_a
```{R question_2_a}
rawdata <- read.table("osl.dat", #input data
                      header=TRUE) #the first line as the names of the variables 
```
##question_2_b
```{R question_2_b, fig.height=7.5, fig.width=6}
par(mfrow=c(2,1))
plot(rawdata$de,rawdata$se,
     ylab="Standard Errors" , #add the ylab title
     xlab="Equivalent Dose", #add the xlab title
     main="Standard Errors against Equivalent Dose" )#add the main title
hist(rawdata$de,
     xlab="Equivalent Dose" , #add the xlab title
     main="Equivalent Dose by Frequency" )#add the main title
text(3,40,paste0("the number of grains is ",
                 length(rawdata$de),
                 "\nthe mean of the equivalent doses is ",
                 format(mean(rawdata$de),digits = 4),
                 "\nthe standard deviation of the equivalent doses is ",
                 format(sd(rawdata$de),digits = 4)))
```

##question_2_c

```{R question_2_c}
negll <- function(params,dat) {
  l <- -0.5*sum(log(params[2]^2+dat[,2]^2)+(dat[,1]-params[1])^2/
                  (params[2]^2+dat[,2]^2)) #the log-likelihood omitting the constant term
  return(-l) #the negative log-likelihood
}
```
##question_2_d
```{R question_2_d}
#question_2_d
dat <- rawdata[,c(2,3)]
params1 <- c(mean(rawdata[,2]),sd(rawdata[,2])) #params1 use the sd(rawdata[,2])
cat("the the negative log-likelihood value by params1 is ",negll(params1,dat))
params2 <- c(mean(rawdata[,2]),mean(rawdata[,3])) #params2 use the mean(rawdata[,3])
cat("the the negative log-likelihood value by params2 is ",negll(params2,dat))
```
##question_2_e
```{R question_2_e}
est <- nlm(negll,c(1,5),dat=rawdata[,c(2,3)],hessian=T) #nlm estimation
utils::str(nlm(negll,c(1,5),dat=rawdata[,c(2,3)]),hessian=T) #control the output
cat("the estimates of mu and sigma are ",est$estimate[1]," and ",est$estimate[2])
```
##question_2_f
```{R question_2_f}
se<-diag(solve(est$hessian)) #the parameters standard errors for these estimates
cat("the mu and sigma standard errors for these estimates are ",se[1]," and ",se[2])
```

### 2019-03-19 STAT0017_ICA1/SN17052480.Rmd
STAT0017 ICA1

---
output:
  pdf_document: default
  html_document: default
---

<!-- saved from url=(0100)https://moodle-1819.ucl.ac.uk/pluginfile.php/1342515/mod_resource/content/7/stat0017ica1template.Rmd -->
<html><head><meta http-equiv="Content-Type" content="text/html; charset=UTF-8"></head><body>---
title: "STAT0017 ICA 1 2018-19"
author: "Student number: xxxxxxxx"
date: "`r Sys.Date()`"
output:
  rmarkdown::pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_width: 6
    fig_height: 4
---

```{r, include = FALSE}
# Load the data (you will need to edit this to point to the correct directory
# on your computer)
load(file = "/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/wm.Rdata")
load(file = "/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pot.Rdata")
# You will also need to load any R libraries that you want to use.
# Some parts of the analyses are based on simulation.
# We set a set a random number seed so that
# 1. The numeric results on which you comments will not change each time you run
#    your code (unless you change the order of the analyses)
# 2. Your work is easier for me to mark.
#### PLEASE DO NOT CHANGE THE FOLLOWING LINE OF CODE (KEEP THE SEED as 17) ####
set.seed(17)
```

---
# [This is a comment block that will not appear in your PDF file]
# Add your text (perhaps with LaTeX code in it) and R code in the 
# relevant sections below.
# There is an example of an R code `chunk' in the Winter maxima (wm) section
---

# Extremal Types Example

${}$\hspace*{\fill} [25]

---
# You could put LaTeX code into this section to give your answer to Part A.
# You can only use basic LaTeX code (no extra packages).
# If you don't do this then please don't delete the Extremal Types Example
# heading above: just leave this section blank.
---

# Exploratory analysis

## Winter maxima (wm)

```{r}
# Add R code here (and similarly elsewhere)
```

## Storm peaks (pot)

## Comments

${}$\hspace*{\fill} [10]

# Extreme value (EV) modelling of $H_s$

## GEV modelling of winter maxima

### Maximum Likelihood-Based Inference

### Comments

### Bayesian Inference

### Comments

## Binomial-GP modelling of storm peaks

### Threshold selection

### Maximum Likelihood-Based Inference

### Comments

### Bayesian Inference

### Comments

${}$\hspace*{\fill} [25]

## Reporting to your client

${}$\hspace*{\fill} [15]

# EV regression modelling of winter maximum $H_s$ on NAO

## Build a GEV regression model

${}$\hspace*{\fill} [15]

## Inference for $H_s^{100}$

${}$\hspace*{\fill} [10]

<script type="text/x-mathjax-config">
   MathJax.Hub.Config({  "HTML-CSS": { minScaleAdjust: 125, availableFonts: [] }  });
</script>
</body></html>

### 2019-03-19 STAT0017_Topic2/STAT0017_topic2.R
STAT0017 topic1

@@ -1,0 +1,2 @@
+mydataframe <- read.table("/Users/hongwei/Documents/GitHub/STAT/STAT0030_Lab9_GLMs/nino3.dat",header = TRUE)
+gamma.glm <- glm(y ~ x1 + x2, family=Gamma, data=mydataframe)

### 2019-03-19 STAT0017_Topic2/STAT0017_topics1_part1.R

@@ -1,0 +1,514 @@
+## Install CDVine package (and others)
+install.packages("CDVine")
+library("CDVine")
+
+install.packages("gridExtra","ggplot2")
+library("gridExtra")
+library("ggplot2")
+opar <- par("mfrow","mar")
+
+
+# simulate from a bivariate Gaussian copula, rho=0.3
+simdata1 = BiCopSim(1000,1,0.3,par2=0)
+plot(simdata1, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.3")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=0.7
+simdata2 = BiCopSim(1000,1,0.7,par2=0)
+plot(simdata2, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.7")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=0.9
+simdata3 = BiCopSim(1000,1,0.9,par2=0)
+plot(simdata3, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.9")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=0.99999
+simdata4 = BiCopSim(1000,1,0.99999,par2=0)
+plot(simdata4, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.99999")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=1, i.e. comonotonicity copula
+u = runif(1000)
+simdata5=cbind(u,u)
+plot(simdata5, pch=1, cex=0.8,xlab= "u",col.lab="red",ylab= "u",main=expression(paste("Gaussian copula, ",rho,"=1, (comonotonicity)")), font.main=1)
+
+
+par(mfrow=c(2,2))
+plot(simdata1, pch=1, cex=0.7,xlab= "u1", col.main="blue", col.lab="red", ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.3")), font.main=1,xaxs="i", yaxs="i", xlim=c(0, 1),ylim=c(0, 1))
[…]

### 2019-03-19 STAT0017_Topic2/STAT0017_topics1_part2.R

@@ -1,0 +1,101 @@
+# uniform data
+data(worldindices) 
+u=worldindices
+rm(worldindices)
+
+
+
+cor(u[,1:3],method = c("kendall"))
+
+u2u3u1=cbind(u[,2],u[,3],u[,1])
+vinemodel=CDVineCopSelect(u2u3u1,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel
+
+N=2000
+u2u3u1_sim=CDVineSim(N, family=vinemodel$family, vinemodel$par,  vinemodel$par2, type=2)
+cor(u2u3u1_sim,method = c("kendall"))
+cor(u2u3u1,method = c("kendall"))
+vinemodel_sim=CDVineCopSelect(u2u3u1_sim,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel_sim
+
+# Vine selection "manually"
+model_1 = BiCopSelect(u[,2],u[,3],familyset=c(1:10,13,14,16,23,24,26))
+model_1
+model_2 = BiCopSelect(u[,1],u[,3],familyset=c(1:10,13,14,16,23,24,26))
+model_2
+h1 = BiCopHfunc(u[,2],u[,3],model_1$family,model_1$par,model_1$par2)
+h2 = BiCopHfunc(u[,1],u[,3],model_2$family,model_2$par)
+model_3 = BiCopSelect(h1$hfunc2,h2$hfunc2,familyset=c(1:10,13,14,16,23,24,26))
+
+
+###########
+
+
+
+N=10000
+u_sim=CDVineSim(N, family=model$family, model$par,  model$par2, type=2)
+cor(u_sim,method = c("kendall"))
+model_sim=CDVineCopSelect(u_sim,type=2,familyset=c(1:10,13,14,23,24))
+
+
+
+# Inverse CDF Skewed T distribution
+param=coef(model)
+z1 <- qnorm(u[,1], mean = 0, sd = 1)
+sigmat <- model@h.t[length(model@h.t)]
+
+rest<-res[length(res)]
+
+sigma_tplus1 <- param[5] + param[6]*sigmat*rest^2 + param1[6]*sigmat
+epsilon <- sqrt(sigma_tplus1)*z1
+
+x2_t <- matrix(0, nrow = N, ncol = 1)
+x2_lag <- ret[length(ret)]
+
+x_t <- param[1] + param[2]*x2_lag + epsilon  
+
+plot(x1_sim, type='line')
[…]

### 2019-03-19 STAT0030_Lab10_Simulation/Lab10_Solns.r
STAT0030_lab9_simulation

@@ -1,0 +1,111 @@
+##################################################
+# R code for STAT0030 Lab 10 on Statistical simulation #
+##################################################
+#
+#
+# Define congruential generator:
+test.cg <- function(n=1,y=9) {
+    out <- rep(NA,n)
+    for(i in 1:n) {
+        y <- (1229*y+1) %% 2048
+    out[i] <- y/2048
+    }
+    out
+}
+#
+##################################################
+# Exercises: sampling from various distributions #
+##################################################
+#
+# Using the test generator test.cg() above and compare 
+# results with R results. 
+# 
+# Number of samples in comparison (choose an even S):
+S <- 1000
+U1 <- test.cg(S)
+U2 <- runif(n=S,0,1)
+#
+# Function for printing comparison to the screen:
+compare <- function(X1,X2, Mean=NA, Var=NA,digits=5){
+  cat("\n______________________________________")
+  cat("\nTest with",length(X1),"values for both methods:\n")
+  mns <- c(mean(X1),mean(X2),Mean)
+  sds <- c(sd(X1),sd(X2),sqrt(Var))
+  rnames <- c("Method 1","Method 2","Theoretical")
+  test.table <- data.frame(Mean=mns,SD=sds, row.names=rnames)
+  print(round(test.table,digits=digits))
+  cat("______________________________________\n\n")
+}
+#
+# 1. Uniform(-30,10)
+X1 <- 40*U1-30
+X2 <- 40*U2-30
+cat("\nDistribution U(-30,10):")
+compare(X1,X2,Mean=-10,Var=40^2/12)
+#
+# 2. Bernouilli(0.6):
+X1 <- as.numeric(U1 <= 0.6)
+X2 <- as.numeric(U2<= 0.6)
+cat("\nDistribution Bernouilli(0.6):")
+compare(X1,X2,Mean=0.6,Var=0.6*0.4)
+#
+# 3. Exponential(0.5):
[…]

### 2019-03-22 STAT0017_ICA1/SN17052480.Rmd
selected topics ICA1 questiona 1 and beginning of 2

@@
 # on your computer)
-load(file = "/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/wm.Rdata")
-load(file = "/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pot.Rdata")
+setwd("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1")
+raw_wm <- load("wm.Rdata")
+raw_pot <- load("pot.Rdata")
 # You will also need to load any R libraries that you want to use.
+library("evd")
+library("evdbayes")
+library("ismev")
+library("revdbayes")
+library("threshr")
+library("bayesplot")
+library("coda")
+source("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pjnfunctions.R")
 # Some parts of the analyses are based on simulation.
@@
 ## Build a GEV regression model
-
+test123
 ${}$\hspace*{\fill} [15]

### 2019-03-22 STAT0017_ICA1/SN17052480_NEW.Rmd
selected topics ICA1 questiona 1 and beginning of 2

---
title: "SN17052480"
author: "Hongwei Peng"
date: "21/03/2019"
output:
  pdf_document: default
  html_document: default
---

# Part A
## Question 1 (a)
From the question we can see:
$$ F(x)= P(X \leq x)= \begin{cases} 1-e^{1/x}, & \text {for $x < 0$ .} \\ 1, & \text{for $x \geq 0$ .} \end{cases} \tag {1}$$
$$ M_n=max \lbrace x_1,...,x_n \rbrace $$ 
Hazard Function:
\begin{align}
h(x) & =\frac{1-F(x)}{f(x)} \\
  & = \frac{e^{1/x}}{e^{1/x} \times (-x^{-2})} \\
  & =-x^{2}
\end{align} 
Derivative of h(x):
$h^{'}= -2x$

\begin{align}
\lim_{x \to x^F} h^{'}(x) \to \xi \\
Let\ \xi = -2M_n \\
We\ can\ see:\  x \sim GEV(0,1,-2M_n)
\end{align}

From the slides we have:
$$\begin{cases} 1-F(b_n)=1/n \\ a_n=h(b_n) \end{cases}$$
solve it we have: 
$$\begin{cases} b_n=- \frac{1}{log(n)} \\ a_n=- \frac{1}{{log^2(n)}} \end{cases}$$

## Question 1 (b)
When $\xi < 0$ the GEV distribution has light upper tail with the finite upper limit which is  $\mu - \sigma / \xi$.

Let $\mu - \sigma / \xi = 0$ then this distribution with a finite upper end point of 0  has an upper end point of infinity.

## Question 1 (c)
We assume $A = \{ x: 0< F(x)<1 \}$ , and $x^*=sup_{x \in A} A$.

Here F(x) can be any function including the question's function(1).

For $\forall x, x<x^*$, we have $Pr(M_n \leq x)=F^n(x) \to 0, as \  n \to \infty$.

For $\forall x, x \geq x^*$, we have $Pr(M_n \leq x)=F^n(x) \to 1 , as \ n \to \infty$.

This is mean whatever x or F(x), $M_n = 0 or 1$ when $n \to \infty$.

The $M_n$ is Degenerate distribution, which is useless.

That is why we need fit a GEV model.

## Question 1 (d)
The log-likelihood:
$$l( \phi ) = l(\mu , \sigma, \xi)=log L(\mu , \sigma, \xi)=log \prod_{i=1}^m g(z_i;\mu , \sigma, \xi)$$

# Part B
## Task 1
```{r}
setwd("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1")
raw_wm <- load("wm.Rdata")
raw_pot <- load("pot.Rdata")
```

## Task 2

## Task 3.1

## Task 3.2

## Task 3.3

## Task 4.1

## Task 4.2

### 2019-03-22 STAT0017_ICA1/portpirie.R

@@ -1,0 +1,253 @@
+#=============================================================================#
+#   STAT0017 : R code for the portpirie sea level example from Coles (2001)   #
+#=============================================================================#
+
+# Load revdbayes, to access the portpirie data
+library(revdbayes)
+
+?portpirie                                     ### description of the data
+
+# if ismev version of data is loaded then convert it to evd/revdbayes format ...
+if (!is.null(ncol(portpirie))) {
+  portpirie <- portpirie[, "SeaLevel"]
+}  
+
+par(mfrow = c(1, 1))
+plot(portpirie, bty = "l", pch = 16, ylab = "sea level / m", xlab = "year") 
+
+#=============================================================================#
+#         Frequentist inference using maximum likelihood estimation           # 
+#=============================================================================#
+
+library(ismev)
+
+#-----------------------------------------------------------------------------#
+#                                Fit GEV model                                #
+#-----------------------------------------------------------------------------#
+
+portpirie.gev <- gev.fit(portpirie) 
+
+portpirie.gev$mle           ### GEV MLEs
+portpirie.gev$se            ### standard errors of MLEs
+
+#-----------------------------------------------------------------------------#
+#                              Model diagnostics                              #
+#-----------------------------------------------------------------------------#
+
+# PJN's GEV diagnostics (ismev::gev.diag has PP axis labels the wrong way round) 
+pjn.gev.diag(portpirie.gev) 
+
+# Do you notice something strange about the behaviour of the lower limit of 
+# the confidence in the bottom left plot, for long return periods?
+# Why do you think that this occurs?  How could we improve this plot?
+
+#-----------------------------------------------------------------------------#
+#               Inference about parameters and return levels                  #
+#-----------------------------------------------------------------------------#
+
+### Symmetric 100*conf% confidence intervals for mu, sigma and xi ...
+
+pjn.gev.conf(portpirie.gev, conf = 0.95)
+
+### Profile log-likelihood for the GEV shape parameter xi ...
+
+?gev.profxi
+
+# PJN's version of ismev::gev.profxi (CI limits added to plots)
+pjn.gev.profxi(portpirie.gev, -0.3, 0.3, conf = 0.95)          
+
[…]

### 2019-03-22 STAT0017_ICA1/waves.R

@@ -1,0 +1,192 @@
+#=============================================================================#
+#   STAT0017 : R code for the wave heights data from Northrop et al (2017)    #
+#=============================================================================#
+
+# In this script far fewer commands are provided than in portpirie.R.  
+# The general idea is the same: we wish to fit and check an extreme value model 
+# and inferences; but now our modelling is based on the GP distribution.
+
+# Where general instructions are provided rather than code please make use of 
+# the help system to help you to construct the code that you need.
+# In some cases code has been provided but with missing arguments (?).
+
+#=============================================================================#
+#          Storm peak significant wave heights from the North Sea             #
+#=============================================================================#
+
+# Load the threshr package, to access the ns data
+library(threshr)
+
+# Read the help file for the ns data
+?ns
+
+# Plot the data (how you do it is up to you)
+
+# Set a threshold, u
+# For the moment we set a threshold in an arbitrary manner: 
+# at the sample 80% quantile
+# We return to the issue of threshold selection later
+
+u <- quantile(ns, probs = 0.8)
+
+# The mean number of observations per year (npy)
+
+# We need to know this to make extreme value inferences (return levels etc)
+# It tells us (indirecty) how many years are spanned by the data 
+# (it's 31 years - note that the data are from Oct-Mar winter seasons)
+ns.npy <- length(ns) / 31
+
+#=============================================================================#
+#         Frequentist inference using maximum likelihood estimation           # 
+#=============================================================================#
+
+library(ismev)
+
+#-----------------------------------------------------------------------------#
+#                                Fit GP model                                 #
+#-----------------------------------------------------------------------------#
+
+?gpd.fit
+
+# Fit the GP model to excesses of threshold u
+# Don't forget npy !
+ns.gp <- ?
+
+ns.gp$mle
+ns.gp$se
+ns.gp$rate
+# What is the following quantity?
+sqrt(ns.gp$rate * (1 - ns.gp$rate) / ns.gp$nexc)
+
+#-----------------------------------------------------------------------------#
+#                              Model diagnostics                              #
+#-----------------------------------------------------------------------------#
+
+# PJN's GP diagnostics (ismev::gpd.diag has PP axis labels the wrong way round) 
+pjn.gpd.diag(ns.gp)                
+
+#-----------------------------------------------------------------------------#
[…]

### 2019-03-22 STAT0017_ICA1/SN17052480_NEW.Rmd
little change

@@
 raw_pot <- load("pot.Rdata")
+library("evd")
+library("evdbayes")
+library("ismev")
+library("revdbayes")
+library("threshr")
+library("bayesplot")
+library("coda")
+source("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pjnfunctions.R")
 ```

### 2019-03-22 STAT0017_ICA1/waves.R

@@ -47,10 +47,10 @@ library(ismev)
 #-----------------------------------------------------------------------------#
 
 ?gpd.fit
-
+data(rain)
 # Fit the GP model to excesses of threshold u
 # Don't forget npy !
-ns.gp <- ?
+ns.gp <- gpd.fit(rain, 10)
 
 ns.gp$mle
 ns.gp$se
@@ -77,7 +77,7 @@ pjn.gpd.conf(ns.gp, conf = 0.95)
 ?gpd.profxi
 
 # PJN's version of ismev::gpd.profxi (CI limits added to plots)
-pjn.gpd.profxi(ns.gp, xlow = ?, xup = ?, conf = 0.95)          
+pjn.gpd.profxi(ns.gp, xlow = 0, xup = 0.2, conf = 0.95)          
 
 ### Symmetric 100*conf% confidence intervals for the m-year return level ...
 

### 2019-03-22 STAT0017_ICA1/fremantle.R
ADD practice2 to read

@@ -1,0 +1,71 @@
+#------------------------------- The ismev package ---------------------------#
+
+library(ismev)
+data(fremantle) # See page 111 of Coles (2001)
+?fremantle # in ismev
+
+plot(fremantle[,1],fremantle[,2],pch=16,xlab="year",ylab="sea level (m)")
+plot(fremantle[,3],fremantle[,2],pch=16,xlab="SOI",ylab="sea level (m)")
+
+fit0 <- gev.fit(fremantle[,2])                  # no covariates
+gev.diag(fit0)                                  # model diagnostics
+
+ydat <- fremantle[,c(1,3)]                      # year in column 1, SOI in column 2
+fit1 <- gev.fit(fremantle[,2],ydat=ydat,mul=1)  # convergence problems !
+
+# Try again ...
+scaled.year <- (fremantle[,1]-1897)/(1989-1897) # scale year to [0,1]
+ydat <- cbind(scaled.year,fremantle[,3])        # year in column 1, SOI in column 2
+
+fit1 <- gev.fit(fremantle[,2],ydat=ydat,mul=1)  # does reg. coeff (2nd parameter) seem signficant?
+pchisq(2*(fit0$nllh-fit1$nllh),1,lower.tail=F)  # p-value from lik ratio test
+gev.diag(fit1)                                  # model diagnostics
+
+# Add SOI ...
+
+fit2 <- gev.fit(fremantle[,2],ydat=ydat,mul=1:2)
+pchisq(2*(fit1$nllh-fit2$nllh),1,lower.tail=F)  # p-value from lik ratio test
+gev.diag(fit2)                                  # model diagnostics
+
+# Covariate effects on scale (sigma)?
+
+# Sometimes it can help to set initial estimates that start the estimation
+# from a fitted simpler model
+muinit <- fit2$mle[1:3]
+siginit <- c(log(fit2$mle[4]), 0)
+shinit <- fit2$mle[5]
+fit3 <- gev.fit(fremantle[,2], ydat = ydat, mul = 1:2, sigl = 1, siglink = exp,
+                muinit = muinit, siginit = siginit, shinit = shinit)
+pchisq(2*(fit2$nllh-fit3$nllh),1,lower.tail=F)  # p-value from lik ratio test
+gev.diag(fit3)                                  # model diagnostics
+
+fit4 <- gev.fit(fremantle[,2], ydat = ydat, mul = 1:2, sigl = 2, siglink = exp,
+                muinit = muinit, siginit = siginit, shinit = shinit)
[…]

### 2019-03-22 STAT0017_ICA1/rain.R

@@ -1,0 +1,130 @@
+#==============================================================================#
+#       STAT0017 : R code for the rainfall example from Coles (2001)           #
+#==============================================================================#
+
+library(ismev)
+
+data(rain)
+?rain  # in ismev
+
+# Time series plot
+
+my.date <- seq(as.Date("1914/1/1"), by="day", length.out=length(rain))
+plot(my.date,rain,bty="l",pch=20,ylab="rainfall total / mm",xlab="year")
+
+#-----------------------------------------------------------------------------#
+#                                Fit GEV model                                #
+#-----------------------------------------------------------------------------#
+
+year <- 1900 + as.POSIXlt(my.date)$year       ### extract year from data
+rain.AM <- as.numeric(tapply(rain,year,max))  ### calculate annual maxima
+plot(min(year):max(year),rain.AM,pch=16,xlab="year",
+     ylab="annual maximum daily rainfall / mm")
+
+rain.gev <- gev.fit(rain.AM) ### fit GEV model
+rain.gev$mle                 ### GEV MLEs
+rain.gev$se                  ### standard errors of MLEs
+
+#-----------------------------------------------------------------------------#
+#                              Model diagnostics                              #
+#-----------------------------------------------------------------------------#
+
+pjn.gev.diag(rain.gev) ### PJN's GEV diagnostics
+
+#-----------------------------------------------------------------------------#
+#               Inference about parameters and return levels                  #
+#-----------------------------------------------------------------------------#
+
+### Symmetric 100*conf% confidence intervals for mu, sigma and xi ...
+
+pjn.gev.conf(rain.gev)
+
+### Profile log-likelihood for the GEV shape parameter xi ...
+
+pjn.gev.profxi(rain.gev,-0.15,0.4)                    ### PJN's version
+
+### Symmetric 100*conf% confidence intervals for return levels ...
+
+pjn.gev.conf.ret.levels(rain.gev)
+
+### Profile log-likelihood for the 100 year return level ...
+
+pjn.gev.prof(rain.gev,m=100,76,170)                 ### PJN's version
+
+#====================================================================================#
+#---------------------- Threshold modelling : bin-BP  -------------------------------#
[…]

### 2019-03-22 STAT0017_ICA1/SN17052480.Rmd
little change
finished the exploratory

@@
 setwd("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1")
-raw_wm <- load("wm.Rdata")
-raw_pot <- load("pot.Rdata")
+load("wm.Rdata")
+load("pot.Rdata")
 # You will also need to load any R libraries that you want to use.
@@
 # Add R code here (and similarly elsewhere)
+plot(wm$waterYear,wm$Hs,bty="l",pch=20,xlab="year",ylab="wave height (in metres)")
+#(wm$Hs~wm$meanNAO) 
+plot(wm$meanNAO,wm$Hs,bty="l",pch=20,xlab="year",ylab="the mean of NAO")
+abline(lm(wm$Hs~wm$meanNAO), col="red") # regression line (wm$Hs~wm$meanNAO) 
+lines(lowess(wm$Hs~wm$meanNAO), col="blue") # lowess line (wm$Hs~wm$meanNAO)
+#(wm$Hs~wm$maxNAO)
+plot(wm$maxNAO,wm$Hs,bty="l",pch=20,xlab="year",ylab="the max of NAO")
+abline(lm(wm$Hs~wm$maxNAO), col="red") # regression line (wm$Hs~wm$maxNAO)
+lines(lowess(wm$Hs~wm$maxNAO), col="blue") # lowess line (wm$Hs~wm$maxNAO)
+#(wm$Hs~wm$meanA0)
+plot(wm$meanA0,wm$Hs,bty="l",pch=20,xlab="year",ylab="the mean of AO")
+abline(lm(wm$Hs~wm$meanA0), col="red") # regression line (wm$Hs~wm$meanA0)
+lines(lowess(wm$Hs~wm$meanA0), col="blue") # lowess line (wm$Hs~wm$meanA0)
+#(wm$Hs~wm$maxAO)
+plot(wm$maxAO,wm$Hs,bty="l",pch=20,xlab="year",ylab="the max of AO")
+abline(lm(wm$Hs~wm$maxAO), col="red") # regression line (wm$Hs~wm$maxAO)
+lines(lowess(wm$Hs~wm$maxAO), col="blue") # lowess line (wm$Hs~wm$maxAO)
+
 ```
@@
 ## Build a GEV regression model
-test123
+
 ${}$\hspace*{\fill} [15]

### 2019-03-22 STAT0017_ICA1/dowjones.R

@@ -94,3 +94,4 @@ npars <- c(np1,np2,np3,np4)
 cbind(nllhs,npars)
 
 pp.diag(fit.mu) # diagnostic plots
+

### 2019-03-22 STAT0017_ICA1/fremantle.R

@@ -69,3 +69,4 @@ std.errors(evd_fit2)
 vcov(evd_fit2)
 confint(evd_fit2)
 plot(evd_fit2)
+

### 2019-03-22 STAT0017_ICA1/SN17052480.Rmd
plot pot
finished ICA1 selected topics

--- 2019-03-22 STAT0017_ICA1/SN17052480.Rmd
@@
 title: "STAT0017 ICA 1 2018-19"
-author: "Student number: xxxxxxxx"
+author: "Student number: 17052480"
 date: "`r Sys.Date()`"
@@
 
+## Question 1 (a)
+From the question we can see:
+$$ F(x)= P(X \leq x)= \begin{cases} 1-e^{1/x}, & \text {for $x < 0$ .} \\ 1, & \text{for $x \geq 0$ .} \end{cases} \tag {*}$$
+$$ M_n=max \lbrace x_1,...,x_n \rbrace $$ 
+Hazard Function:
+\begin{align}
+h(x) & =\frac{1-F(x)}{f(x)} \\
+  & = \frac{e^{1/x}}{e^{1/x} \times (-x^{-2})} \\
+  & =-x^{2}
+\end{align} 
+Derivative of h(x):
+$h^{'}= -2x$
+
+\begin{align}
+\lim_{x \to x^F} h^{'}(x) \to \xi \\
+Let\ \xi = -2M_n \\
+We\ can\ see:\  x \sim GEV(0,1,-2M_n)
+\end{align}
+
+From the slides we have:
+$$\begin{cases} 1-F(b_n)=1/n \\ a_n=h(b_n) \end{cases}$$
+solve it we have: 
+$$\begin{cases} b_n=- \frac{1}{log(n)} \\ a_n=- \frac{1}{{log^2(n)}} \end{cases}$$
+
+## Question 1 (b)
+When $\xi < 0$ the GEV distribution has light upper tail with the finite upper limit which is  $\mu - \sigma / \xi$.
+
+Let $\mu - \sigma / \xi = 0$ then this distribution with a finite upper end point of 0  has an upper end point of infinity.
+
+## Question 1 (c)
+We assume $A = \{ x: 0< F(x)<1 \}$ , and $x^*=sup_{x \in A} A$.
+
+Here F(x) can be any function including the function $(*)$.
+
+For $\forall x, x<x^*$, we have $Pr(M_n \leq x)=F^n(x) \to 0, as \  n \to \infty$.
+
+For $\forall x, x \geq x^*$, we have $Pr(M_n \leq x)=F^n(x) \to 1 , as \ n \to \infty$.
+
+This is mean whatever x or F(x), $M_n = 0 or 1$ when $n \to \infty$.
+
+The $M_n$ is Degenerate distribution, which is useless.
+
+That is why we need fit a GEV model.
+
+## Question 1 (d)
+The log-likelihood:
+$$\xi_n \approx h^{'}(x)|_x=u(n) \ where \ u(n)=F^{-1}(1-1/n)$$
+Thus $$\xi= h^{'}(x) = -2/ln(365) = -0.3400$$
+
 # Exploratory analysis
@@
 # Add R code here (and similarly elsewhere)
+plot(wm$waterYear,wm$Hs,bty="l",pch=20,xlab="year",ylab="wave height (in metres)")
+#(wm$Hs~wm$meanNAO) 
+plot(wm$meanNAO,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the mean of NAO")
+abline(lm(wm$Hs~wm$meanNAO), col="red") # regression line (wm$Hs~wm$meanNAO) 
+lines(lowess(wm$Hs~wm$meanNAO), col="blue") # lowess line (wm$Hs~wm$meanNAO)
+#(wm$Hs~wm$maxNAO)
+plot(wm$maxNAO,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the max of NAO")
+abline(lm(wm$Hs~wm$maxNAO), col="red") # regression line (wm$Hs~wm$maxNAO)
+lines(lowess(wm$Hs~wm$maxNAO), col="blue") # lowess line (wm$Hs~wm$maxNAO)
+#(wm$Hs~wm$meanA0)
+plot(wm$meanA0,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the mean of AO")
+abline(lm(wm$Hs~wm$meanA0), col="red") # regression line (wm$Hs~wm$meanA0)
+lines(lowess(wm$Hs~wm$meanA0), col="blue") # lowess line (wm$Hs~wm$meanA0)
+#(wm$Hs~wm$maxAO)
+plot(wm$maxAO,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the max of AO")
+abline(lm(wm$Hs~wm$maxAO), col="red") # regression line (wm$Hs~wm$maxAO)
+lines(lowess(wm$Hs~wm$maxAO), col="blue") # lowess line (wm$Hs~wm$maxAO)
+
 ```
@@
 ## Storm peaks (pot)
+```{r}
+plot(pot$date,pot$Hs,bty="l",pch=20,xlab="date",ylab="wave height (in metres)")
+```
 
 ## Comments
-
+The relationship between wave height and all of variables can be roughly seen through the scatter plot.
+As can be seen from the line graph, the more the red line coincides with the blue line, the better the linear regression model fits.
+As can be seen from the plot, the average of AO has a better fitting relationship with the height of the waves.
+Further analysis needs to be carried out, followed by analysis.
 ${}$\hspace*{\fill} [10]
@@
 ## GEV modelling of winter maxima
+```{r}
+wm.gev <- gev.fit(wm[,1])#fit GEV model
+wm.gev$mle#GEV MLEs
+wm.gev$se#standard errors of MLEs
+pjn.gev.diag(wm.gev) #PJN's GEV diagnostics
+```
 
 ### Maximum Likelihood-Based Inference
+```{r}
+pjn.gev.conf(wm.gev, conf = 0.95)
+pjn.gev.profxi(wm.gev, -1, 1, conf = 0.95)   
+pjn.gev.conf.ret.levels(wm.gev, m = 100, conf = 0.95)
+# Profile log-likelihood for the 100 year return level
+pjn.gev.prof(wm.gev,m=100,14,20)# PJN's version
+```
 
@@
 
+First, the model is fitted, and the three parameters of the model are 11.2726903,  1.2064985, -0.1534719 respectively.
+Their variances are 0.18140907, 0.12880447, 0.09956538 respectively.
+Through the diagnosis, we can see that the tail of data is basically appropriate, and it can be seen the model's trend.
+
 ### Bayesian Inference
+```{r}
+my.ylab <- c("mu","sigma","xi")
+# Set independent normal priors with large variances 
+prior.cov.mat <- diag(c(10000, 10000, 100))         
+pn <- prior.norm(mean = c(0, 0, 0), cov = prior.cov.mat)
+
+# Starting well away from the MLEs
+init <- c(11,1,0.1)                
+# SDs of the proposal distributions for (mu, ln(sigma), xi)
+prop.sd <- c(0.18,0.12,0.1)       
+prop.sd.auto <- ar.choice(init = init, prior = pn, lh = "gev", 
+                          data = wm$Hs, psd = prop.sd, 
+                          tol = rep(0.02, 3))$psd
+post <- posterior(3000, init = init, prior = pn, lh = "gev", 
+                  data = wm$Hs, psd = prop.sd.auto)
+for (i in 1:3) plot(post[,i],ylab=my.ylab[i]) 
+attr(post,"ar")        
+# Posterior dependence among parameters
+pairs(post)
+```
+
+### Comments
+Bayesian Inference
+
+## Binomial-GP modelling of storm peaks
+```{r}
+pot.gp <- gpd.fit(pot[,1], 10)
+```
+
+### Threshold selection
+```{r}
+mrl.plot(pot[,1])
+# PJN's GP diagnostics 
+pjn.gpd.diag(pot.gp)    
+```
+
+### Maximum Likelihood-Based Inference
+```{r}
+#Symmetric 100*conf% confidence intervals for p_u, sigma_u and xi 
+pjn.gpd.conf(pot.gp, conf = 0.95)
+#PJN's version of ismev::gpd.profxi 
+pjn.gpd.profxi(pot.gp, xlow = -0.3, xup = 0.2, conf = 0.95) 
+#Symmetric 100*conf% confidence intervals for the 100-year return level 
+pjn.gpd.conf.ret.levels(pot.gp, m = 100, npy = 10, conf = 0.95)
+#Profile log-likelihood for the 100-year return level 
+pjn.gpd.prof(pot.gp, m = 100, xlow = 14, xup = 20, npy = 10, conf = 0.95) 
+```
 
@@
 
-## Binomial-GP modelling of storm peaks
+The estimated of $\xi$ is -0.15, and the corresponding 95% confidence interval is [-0.33,0.07].
 
-### Threshold selection
+### Bayesian Inference
+```{r}
+fp <- set_prior(prior = "flat", model = "gp", min_xi = -1)
+bp <- set_bin_prior(prior = "jeffreys")
+u <- quantile(pot[,1], probs = 0.8)
+bgpg <- rpost(n = 10000, model = "bingp", prior = fp, thresh = u, data = pot[,1],
+              bin_prior = bp, npy = 10)
+plot(bgpg, pu_only = TRUE)
+plot(bgpg, add_pu = FALSE)
+plot(bgpg, add_pu = TRUE)
 
-### Maximum Likelihood-Based Inference
+```
 
@@
 
-### Bayesian Inference
-
-### Comments
-
+It can also be seen that the likelihood function of the 100 year return level.
+It takes a constant attempt to return the plot to find th likelihood function is asymmetrical, the confidence interval is also asymmetrical with respect to the maximum likelihood estimate.
 ${}$\hspace*{\fill} [25]
@@
 ## Reporting to your client
+
+From the plot we can see that the return period is 100. The estimated level of reconstruction for the year is 15.25, and the corresponding 95% confidence interval is [14.42,17.7].
 
@@
 ## Build a GEV regression model
-test123
+
 ${}$\hspace*{\fill} [15]
+```{r}
+
+evd_fit0 <- fgev(wm[,1])
+covaryear <- data.frame(scaled_year = (wm[,2]-1955)/(2010-1955))
+covar2 <- data.frame(scaled_year = (wm[,2]-1955)/(2010-1955), NOA = wm[, 3])
+evd_fit1 <- fgev(wm[,1], nsloc = covaryear)
+evd_fit2 <- fgev(wm[,1], nsloc = covar2)
+
+anova(evd_fit2, evd_fit1, evd_fit0)
+
+fitted(evd_fit2) # strictly speaking this should be coef() 
+std.errors(evd_fit2)
+vcov(evd_fit2)
+confint(evd_fit2)
+plot(evd_fit2)
+```
 

### 2019-03-22 STAT0017_ICA1/waves.R

@@ -85,7 +85,7 @@ pjn.gpd.conf.ret.levels(ns.gp, m = 100, npy = ns.npy, conf = 0.95)
 
 ### Profile log-likelihood for the m-year return level ...
 
-pjn.gpd.prof(ns.gp, m = 100, xlow = 10.2, xup = 12.5, npy = ns.npy, conf = 0.95) 
+pjn.gpd.prof(ns.gp, m = 100, xlow = 50, xup = 70, npy = ns.npy, conf = 0.95) 
 
 #=============================================================================#
 #                   A Bayesian approach, using revdbayes                      #

### 2019-04-27 STAT0017_ICA2/Practical 1.R
copula

@@ -1,0 +1,515 @@
+## Install CDVine package (and others)
+install.packages("CDVine")
+library("CDVine")
+
+install.packages("gridExtra","ggplot2")
+library("gridExtra")
+library("ggplot2")
+opar <- par("mfrow","mar")
+
+
+# simulate from a bivariate Gaussian copula, rho=0.3
+simdata1 = BiCopSim(1000,1,0.3,par2=0)
+plot(simdata1, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.3")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=0.7
+simdata2 = BiCopSim(1000,1,0.7,par2=0)
+plot(simdata2, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.7")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=0.9
+simdata3 = BiCopSim(1000,1,0.9,par2=0)
+plot(simdata3, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.9")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=0.99999
+simdata4 = BiCopSim(1000,1,0.99999,par2=0)
+plot(simdata4, pch=1, cex=0.8,xlab= "u1",col.lab="red",ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.99999")), font.main=1)
+
+# simulate from a bivariate Gaussian copula, rho=1, i.e. comonotonicity copula
+u = runif(1000)
+simdata5=cbind(u,u)
+plot(simdata5, pch=1, cex=0.8,xlab= "u",col.lab="red",ylab= "u",main=expression(paste("Gaussian copula, ",rho,"=1, (comonotonicity)")), font.main=1)
+
+
+par(mfrow=c(2,2))
+plot(simdata1, pch=1, cex=0.7,xlab= "u1", col.main="blue", col.lab="red", ylab= "u2",main=expression(paste("Gaussian copula, ",rho,"=0.3")), font.main=1,xaxs="i", yaxs="i", xlim=c(0, 1),ylim=c(0, 1))
[…]

### 2019-04-29 STAT0017_ICA2/17052480.R
copula

@@ -1,0 +1,1 @@
+load("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA2/ICA2_data.RData")

### 2019-04-29 STAT0017_ICA2/Practical 1_supplement 2.R

@@ -1,0 +1,109 @@
+## relevant package (and others)
+install.packages("fUnitRoots")
+library("fUnitRoots")
+library(CDVine)
+install.packages("fGarch")
+library(fGarch)
+install.packages("goftest")
+library(goftest)
+install.packages("KScorrect")
+library(KScorrect)
+library(stats)
+
+load("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA2/data.RData")
+
+opar <- par("mfrow","mar")
+
+plot(data$ftse100~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
+     xlab="",ylab="Price",col="blue",main="FTSE100 (prices)",xaxs="i", 
+     yaxs="i",ylim=c(3000,8000),cex.main=0.8,cex.lab=1)
+axis(2, at = seq(3000,8000,1000), tick=TRUE,cex.axis=0.9)
+axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))
+
+plot(data$sp500~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
+     xlab="",ylab="Price",col="blue",main="S&P500 (prices)",xaxs="i", 
+     yaxs="i",ylim=c(600,3000),cex.main=0.8,cex.lab=1)
+axis(2, at = seq(600,3000,500), tick=TRUE,cex.axis=0.9)
+axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))
+
+unitrootTest(data$ftse100)
+unitrootTest(data$sp500)
+
+ret1<-diff(log(data$ftse100), lag=1,na=remove)
+ret2<-diff(log(data$sp500), lag=1,na=remove)
+
+plot(ret1~as.Date(data$date[2:length(data$date)],"%d/%m/%y"),type="l",yaxt='n',xaxt='n',
+     xlab="",ylab="log-returns",main="FTSE100",xaxs="i", 
+     yaxs="i", col="blue",ylim=c(-0.15,0.15),cex.main=0.8,cex.lab=0.8)
+axis(2, at = seq(-0.15,0.15,0.1), tick=TRUE,cex.axis=0.7)
[…]

### 2019-04-29 STAT0017_ICA2/Practical 1_supplement.R

@@ -1,0 +1,38 @@
+install.packages("copula")
+library("copula")
+
+# normal Copula
+normal<-normalCopula(0.7)
+par(mfrow = c(1, 3))
+persp(normal, dCopula, main ="Normal copula density")
+persp(normal, pCopula, main = "Normal CDF")
+contour(normal, pCopula, xlim = c(0, 1), ylim=c(0, 1), main = " Normal CDF Contour plot")
+
+# t Copula
+t<-tCopula(param = 0.2, dim = 2, df = 3)
+par(mfrow = c(1, 3))
+persp(t, dCopula, main ="t copula density")
+persp(t, pCopula, main = "t CDF")
+contour(t, pCopula, xlim = c(0, 1), ylim=c(0, 1), main = " t CDF Contour plot")
+
+# Clayton Copula
+clayton <- claytonCopula(param = 3)
+par(mfrow = c(1, 3))
+persp(clayton, dCopula, main ="Clayton copula density")
+persp(clayton, pCopula, main = "Clayton CDF")
+contour(clayton, pCopula, xlim = c(0, 1), ylim=c(0, 1), main = " Clayton CDF Contour plot")
+
+# Gumbel Copula
+gumbel <- gumbelCopula(param = 3)
+par(mfrow = c(1, 3))
+persp(gumbel, dCopula, main ="Gumbel copula density")
+persp(gumbel, pCopula, main = "Gumbel CDF")
+contour(gumbel, pCopula, xlim = c(0, 1), ylim=c(0, 1), main = "Gumbel CDF Contour plot")
+
+
+# Frank Copula
+frank <- frankCopula(param = 3)
+par(mfrow = c(1, 3))
+persp(normal, dCopula, main ="Frank copula density")
+persp(normal, pCopula, main = "Frank CDF")
+contour(normal, pCopula, xlim = c(0, 1), ylim=c(0, 1), main = " Frank CDF Contour plot")

### 2019-04-29 STAT0017_ICA2/Practical 2.R

@@ -1,0 +1,31 @@
+# Load uniform data
+data(worldindices) 
+u=worldindices
+rm(worldindices)
+
+
+
+cor(u[,1:3],method = c("kendall"))
+
+u2u3u1=cbind(u[,2],u[,3],u[,1])
+vinemodel=CDVineCopSelect(u2u3u1,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel
+
+N=2000
+u2u3u1_sim=CDVineSim(N, family=vinemodel$family, vinemodel$par,  vinemodel$par2, type=2)
+cor(u2u3u1_sim,method = c("kendall"))
+cor(u2u3u1,method = c("kendall"))
+vinemodel_sim=CDVineCopSelect(u2u3u1_sim,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel_sim
+
+# Vine selection "manually"
+model_1 = BiCopSelect(u[,2],u[,3],familyset=c(1:10,13,14,16,23,24,26))
+model_1
+model_2 = BiCopSelect(u[,1],u[,3],familyset=c(1:10,13,14,16,23,24,26))
+model_2
+h1 = BiCopHfunc(u[,2],u[,3],model_1$family,model_1$par,model_1$par2)
+h2 = BiCopHfunc(u[,1],u[,3],model_2$family,model_2$par,model_2$par2)
+model_3 = BiCopSelect(h1$hfunc2,h2$hfunc2,familyset=c(1:10,13,14,16,23,24,26))
+
+
+###########

### 2019-04-29 STAT0017_ICA2/17052480.R
before Fit copula

@@ -1,1 +1,149 @@
 load("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA2/ICA2_data.RData")
+## relevant package (and others)
+install.packages("fUnitRoots")
+library("fUnitRoots")
+library(CDVine)
+install.packages("fGarch")
+library(fGarch)
+install.packages("goftest")
+library(goftest)
+install.packages("KScorrect")
+library(KScorrect)
+library(stats)
+
+#load("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA2/data.RData")
+
+opar <- par("mfrow","mar")
+
+plot(data$ftse100~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
+     xlab="",ylab="Price",col="blue",main="FTSE100 (prices)",xaxs="i", 
+     yaxs="i",ylim=c(3000,8000),cex.main=0.8,cex.lab=1)
+axis(2, at = seq(3000,8000,1000), tick=TRUE,cex.axis=0.9)
+axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))
+
+plot(data$sp500~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
+     xlab="",ylab="Price",col="blue",main="S&P500 (prices)",xaxs="i", 
+     yaxs="i",ylim=c(600,3000),cex.main=0.8,cex.lab=1)
+axis(2, at = seq(600,3000,500), tick=TRUE,cex.axis=0.9)
+axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))
+
+plot(data$sse~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
+     xlab="",ylab="Price",col="blue",main="FTSE100 (prices)",xaxs="i", 
+     yaxs="i",ylim=c(1000,6500),cex.main=0.8,cex.lab=1)
+axis(2, at = seq(1000,6500,500), tick=TRUE,cex.axis=0.9)
+axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))
+
[…]

### 2019-04-29 STAT0017_ICA2/17052480.R
I do not know

@@ -133,17 +133,110 @@ ADtest3$p.value
 
 
 
-# Fit copula
-u=cbind(u1,u2)
-plot(u)
-BiCopEst(u[,2],u[,1],family=1,method="mle",se=TRUE) 
-BiCopSelect(u[,1],u[,2],familyset=NA)
+u=cbind(u1,u2,u3)
+cor(u[,1:3],method = c("kendall"))
+
+u1u2u3=cbind(u[,1],u[,2],u[,3])
+vinemodel=CDVineCopSelect(u1u2u3,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel
+
+N=2000
+u1u2u3_sim=CDVineSim(N, family=vinemodel$family, vinemodel$par,  vinemodel$par2, type=2)
+cor(u1u2u3_sim,method = c("kendall"))
+cor(u1u2u3,method = c("kendall"))
+vinemodel_sim=CDVineCopSelect(u1u2u3_sim,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel_sim
+
+# Vine selection "manually"
+model_1 = BiCopSelect(u[,2],u[,1],familyset=c(1:10,13,14,16,23,24,26))
+model_1
+model_2 = BiCopSelect(u[,2],u[,3],familyset=c(1:10,13,14,16,23,24,26))
+model_2
+h1 = BiCopHfunc(u[,2],u[,3],model_1$family,model_1$par,model_1$par2)
+h2 = BiCopHfunc(u[,1],u[,3],model_2$family,model_2$par,model_2$par2)
+model_3 = BiCopSelect(h1$hfunc2,h2$hfunc2,familyset=c(1:10,13,14,16,23,24,26))
 
 
-# Gausian copula rho and tau
-f1 <- function (x) 2/pi*asin(x) -0.5
-f <- function (x) 2/pi*asin(x)
-c=uniroot(f1, c(0, 1), tol = 0.00001)
-ro=c$root
-f(ro)
+###########
 
+### Compute Value-at-Risk using MC method based on copulas
+u1=BiCopSim(2000, model_1$family, model_1$par, par2=model_1$par2)
+x <- qnorm(u1)
+u2=BiCopSim(2000, model_2$family, model_2$par, par2=model_2$par2)
+y <- qnorm(u2)
+u3=BiCopSim(2000, model_3$family, model_3$par, par2=model_3$par2)
[…]

### 2019-04-29 STAT0017_ICA2/Practical 2.R

@@ -29,3 +29,4 @@ model_3 = BiCopSelect(h1$hfunc2,h2$hfunc2,familyset=c(1:10,13,14,16,23,24,26))
 
 
 ###########
+

### 2019-04-29 STAT0017_ICA2/17052480.Rmd
trans to RMD

---
title: 'STAT0017 ICA2'
author: "Hongwei Peng"
date: "25/04/2019"
output: pdf_document
---

#(a)

```{r message = FALSE}
load("ICA2_data.RData")
library("fUnitRoots")
library(CDVine)
library(fGarch)
library(goftest)
library(KScorrect)
library(stats)
```
```{r}
plot(data$ftse100~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
     xlab="",ylab="Price",col="blue",main="FTSE100 (prices)",xaxs="i", 
     yaxs="i",ylim=c(3000,8000),cex.main=0.8,cex.lab=1)
axis(2, at = seq(3000,8000,1000), tick=TRUE,cex.axis=0.9)
axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))

plot(data$sp500~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
     xlab="",ylab="Price",col="blue",main="S&P500 (prices)",xaxs="i", 
     yaxs="i",ylim=c(600,3000),cex.main=0.8,cex.lab=1)
axis(2, at = seq(600,3000,500), tick=TRUE,cex.axis=0.9)
axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))

plot(data$sse~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
     xlab="",ylab="Price",col="blue",main="SSE (prices)",xaxs="i", 
     yaxs="i",ylim=c(1000,6500),cex.main=0.8,cex.lab=1)
axis(2, at = seq(1000,6500,500), tick=TRUE,cex.axis=0.9)
axis.Date(1, cex.axis=0.9,at=seq(as.Date("1999/02/25"), as.Date("2019/02/28"), "4 years"))

unitrootTest(data$ftse100)
unitrootTest(data$sp500)
unitrootTest(data$sse)

ret1<-diff(log(data$ftse100), lag=1,na=remove)
ret2<-diff(log(data$sp500), lag=1,na=remove)
ret3<-diff(log(data$sse), lag=1,na=remove)

plot(ret1~as.Date(data$date[2:length(data$date)],"%d/%m/%y"),type="l",yaxt='n',xaxt='n',
     xlab="",ylab="log-returns",main="FTSE100",xaxs="i", 
     yaxs="i", col="blue",ylim=c(-0.15,0.15),cex.main=0.8,cex.lab=0.8)
axis(2, at = seq(-0.15,0.15,0.1), tick=TRUE,cex.axis=0.7)
axis.Date(1, cex.axis=0.7, at=seq(as.Date("1998/01/04"), as.Date("2019/02/28"), "3 years"))

plot(ret2~as.Date(data$date[2:length(data$date)],"%d/%m/%y"),type="l",yaxt='n',xaxt='n',
     xlab="",ylab="log-returns",main="S&P500",xaxs="i", 
     yaxs="i", col="blue",ylim=c(-0.22,0.2),cex.main=0.8,cex.lab=0.8)
axis(2, at = seq(-0.15,0.15,0.1), tick=TRUE,cex.axis=0.7)
axis.Date(1, cex.axis=0.7, at=seq(as.Date("1998/01/04"), as.Date("2019/02/28"), "3 years"))

plot(ret3~as.Date(data$date[2:length(data$date)],"%d/%m/%y"),type="l",yaxt='n',xaxt='n',
     xlab="",ylab="log-returns",main="S&P500",xaxs="i", 
     yaxs="i", col="blue",ylim=c(-0.22,0.2),cex.main=0.8,cex.lab=0.8)
axis(2, at = seq(-0.15,0.15,0.1), tick=TRUE,cex.axis=0.7)
axis.Date(1, cex.axis=0.7, at=seq(as.Date("1998/01/04"), as.Date("2019/02/28"), "3 years"))

unitrootTest(ret1)
unitrootTest(ret2)
unitrootTest(ret3)

acf(ret1)
acf(ret1^2)

acf(ret2)
acf(ret2^2)

acf(ret3)
acf(ret3^2)

model1=garchFit(formula=~arma(3,0)+garch(1,1),data=ret1,trace=F,cond.dist="sstd")
res1 <- residuals(model1, standardize=TRUE)
acf(res1)
acf(res1^2)
Box.test(res1, lag = 10, type = c("Ljung-Box"), fitdf = 0)
Box.test(res1^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
shape1<-coef(model1)[9]
skew1<-coef(model1)[8]
u1<-psstd(res1, mean=0, sd=1, nu=shape1, xi=skew1)
hist(u1)

#Kolmogorov-Smirnov test
KStest1<-LcKS(u1, cdf = "punif")
KStest1$p.value
#Anderson-Darling test
ADtest1<-ad.test(u1, null="punif")
ADtest1$p.value

model2=garchFit(formula=~arma(7,0)+garch(1,1),data=ret2,trace=F,cond.dist="sstd")
res2 <- residuals(model2, standardize=TRUE)
acf(res2)
acf(res2^2)
Box.test(res2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
Box.test(res2^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
shape2<-coef(model2)[13]
skew2<-coef(model2)[12]
u2<-psstd(res2, mean=0, sd=1, nu=shape2, xi=skew2)
#u2<-pnorm(res2, mean=0, sd=1)
#u2<-pt(res2, df=3)
hist(u2)

#Kolmogorov-Smirnov test
KStest2<-LcKS(u2, cdf = "punif")
KStest2$p.value
#Anderson-Darling test
ADtest2<-ad.test(u2, null="punif")
ADtest2$p.value

model3=garchFit(formula=~arma(3,0)+garch(1,1),data=ret3,trace=F,cond.dist="sstd")
res3 <- residuals(model3, standardize=TRUE)
acf(res3)
acf(res3^2)
Box.test(res3, lag = 10, type = c("Ljung-Box"), fitdf = 0)
Box.test(res3^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
shape3<-coef(model3)[9]
skew3<-coef(model3)[8]
u3<-psstd(res3, mean=0, sd=1, nu=shape3, xi=skew3)
hist(u3)

#Kolmogorov-Smirnov test
KStest3<-LcKS(u3, cdf = "punif")
KStest3$p.value
#Anderson-Darling test
ADtest3<-ad.test(u3, null="punif")
ADtest3$p.value

```

#(b)

#(c)

#(d)

### 2019-04-29 STAT0017_ICA2/17052480.Rmd
.....

@@
 
-```{r message = FALSE}
+```{r echo = T, results = 'hide'}
 load("ICA2_data.RData")
@@
 library(stats)
+library(ggplot2)
+library("nloptr")
 ```
-```{r}
+```{r warning=FALSE}
+opar <- par("mfrow","mar")
 plot(data$ftse100~as.Date(data$date,"%d/%m/%y"),type="l",xaxt='n',yaxt='n',
@@
 
-acf(ret1)
-acf(ret1^2)
+#acf(ret1)
+#acf(ret1^2)
 
-acf(ret2)
-acf(ret2^2)
+#acf(ret2)
+#acf(ret2^2)
 
-acf(ret3)
-acf(ret3^2)
+#acf(ret3)
+#acf(ret3^2)
 
@@
 res1 <- residuals(model1, standardize=TRUE)
-acf(res1)
-acf(res1^2)
-Box.test(res1, lag = 10, type = c("Ljung-Box"), fitdf = 0)
-Box.test(res1^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
+Box.test(res1, lag = 10, type = c("Ljung-Box"), fitdf = 0)$p.value
+Box.test(res1^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)$p.value
 shape1<-coef(model1)[9]
@@
 u1<-psstd(res1, mean=0, sd=1, nu=shape1, xi=skew1)
-hist(u1)
+#hist(u1)
 
@@
 res2 <- residuals(model2, standardize=TRUE)
-acf(res2)
-acf(res2^2)
-Box.test(res2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
-Box.test(res2^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
+Box.test(res2, lag = 10, type = c("Ljung-Box"), fitdf = 0)$p.value
+Box.test(res2^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)$p.value
 shape2<-coef(model2)[13]
@@
 u2<-psstd(res2, mean=0, sd=1, nu=shape2, xi=skew2)
-#u2<-pnorm(res2, mean=0, sd=1)
-#u2<-pt(res2, df=3)
-hist(u2)
+#hist(u2)
 
@@
 res3 <- residuals(model3, standardize=TRUE)
-acf(res3)
-acf(res3^2)
-Box.test(res3, lag = 10, type = c("Ljung-Box"), fitdf = 0)
-Box.test(res3^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)
+Box.test(res3, lag = 10, type = c("Ljung-Box"), fitdf = 0)$p.value
+Box.test(res3^2, lag = 10, type = c("Ljung-Box"), fitdf = 0)$p.value
 shape3<-coef(model3)[9]
@@
 u3<-psstd(res3, mean=0, sd=1, nu=shape3, xi=skew3)
-hist(u3)
+#hist(u3)
 
@@
 ```
+```{r}
+u=cbind(u1,u2,u3)
+# Vine selection "manually"
+model_1 = BiCopSelect(u[,2],u[,1],familyset=c(1:10,13,14,16,23,24,26))
+model_2 = BiCopSelect(u[,2],u[,3],familyset=c(1:10,13,14,16,23,24,26))
+h1 = BiCopHfunc(u[,2],u[,3],model_1$family,model_1$par,model_1$par2)
+h2 = BiCopHfunc(u[,1],u[,3],model_2$family,model_2$par,model_2$par2)
+model_3 = BiCopSelect(h1$hfunc2,h2$hfunc2,familyset=c(1:10,13,14,16,23,24,26))
+
+### Compute Value-at-Risk of ftse100,sp500,sse using MC method based on copulas
+u1=BiCopSim(2000, model_1$family, model_1$par, par2=model_1$par2)
+x <- qnorm(u1)
+u2=BiCopSim(2000, model_2$family, model_2$par, par2=model_2$par2)
+y <- qnorm(u2)
+u3=BiCopSim(2000, model_3$family, model_3$par, par2=model_3$par2)
+z <- qnorm(u3)
+
+zz=data.frame(x)
+rownames(zz)<-NULL
+colnames(zz)<-c("x1", "y1")
+p1=ggplot(zz, aes(x1,  y1)) + geom_density2d(colour="blue")+
+  geom_point(size=0.4)+guides(alpha=FALSE)+
+  geom_point(data=subset(zz, !x1>-2 & !y1>-2), colour="red", size=3)+
+  theme_minimal()+
+  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.5),text=element_text(size=14))+ 
+  geom_vline(xintercept = -2, linetype="dashed", color = "#339933", size=1)+ 
+  geom_hline(yintercept = -2, linetype="dashed", color = "#339933", size=1)+  
+  scale_x_continuous(limits = c(-4,4), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-4,4), expand = c(0, 0)) +
+  annotate("rect", xmin = c(-4), xmax = c(-2),
+           ymin = -4, ymax = -2,
+           alpha = 0.2, fill = c("green")) 
+p1#MC method based on ftse100
+
+zz=data.frame(y)
+rownames(zz)<-NULL
+colnames(zz)<-c("x2", "y2")
+p2=ggplot(zz, aes(x2,  y2)) + geom_density2d(colour="blue")+
+  geom_point(size=0.4)+guides(alpha=FALSE)+
+  geom_point(data=subset(zz, !x2>-2 & !y2>-2), colour="red", size=3)+
+  theme_minimal()+
+  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.5),text=element_text(size=14))+ 
+  geom_vline(xintercept = -2, linetype="dashed", color = "#339933", size=1)+ 
+  geom_hline(yintercept = -2, linetype="dashed", color = "#339933", size=1)+  
+  scale_x_continuous(limits = c(-4,4), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-4,4), expand = c(0, 0)) +
+  annotate("rect", xmin = c(-4), xmax = c(-2),
+           ymin = -4, ymax = -2,
+           alpha = 0.2, fill = c("green")) 
+p2##MC method based on sp500 
+zz=data.frame(z)
+rownames(zz)<-NULL
+colnames(zz)<-c("x3", "y3")
+p3=ggplot(zz, aes(x3,  y3)) + geom_density2d(colour="blue")+
+  geom_point(size=0.4)+guides(alpha=FALSE)+
+  geom_point(data=subset(zz, !x3>-2 & !y3>-2), colour="red", size=3)+
+  theme_minimal()+
+  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.5),text=element_text(size=14))+ 
+  geom_vline(xintercept = -2, linetype="dashed", color = "#339933", size=1)+ 
+  geom_hline(yintercept = -2, linetype="dashed", color = "#339933", size=1)+  
+  scale_x_continuous(limits = c(-4,4), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-4,4), expand = c(0, 0)) +
+  annotate("rect", xmin = c(-4), xmax = c(-2),
+           ymin = -4, ymax = -2,
+           alpha = 0.2, fill = c("green")) 
+p3##MC method based on sse
+
+var=matrix(0,3,2)
+
+retport1=log(1+((exp(x[,1])-1)*0.5+(exp(x[,2])-1)*0.5))
+var[1,]=quantile(retport1,c(0.01,0.05))
+
+retport2=log(1+((exp(y[,1])-1)*0.5+(exp(y[,2])-1)*0.5))
+var[2,]=quantile(retport2,c(0.01,0.05))
+
+retport3=log(1+((exp(z[,1])-1)*0.5+(exp(z[,2])-1)*0.5))
+var[3,]=quantile(retport3,c(0.01,0.05))
+
+### VaR for portfolio returns generated using different coplas
+var  #the log diff VaR under 0.01 and 0.05
+
+```
 
@@
 
+```{r}
+
+#u=cbind(ret1,ret2,ret3)
+u=cbind(u1,u2,u3)
+cor(u[,1:3],method = c("kendall"))
+
+u1u2u3=cbind(u[,1],u[,2],u[,3])
+vinemodel=CDVineCopSelect(u1u2u3,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel
+
+N=2000
+u1u2u3_sim=CDVineSim(N, family=vinemodel$family, vinemodel$par,  vinemodel$par2, type=2)
+cor(u1u2u3_sim,method = c("kendall"))
+cor(u1u2u3,method = c("kendall"))
+vinemodel_sim=CDVineCopSelect(u1u2u3_sim,type=2,familyset=c(1:10,13,14,23,24))
+vinemodel_sim
+
+```
+
 #(c)
 
+```{r}
+
+loglike_fun <- function(x1, x2, mu1, mu2, sigma1, sigma2, rho) 
+{         
+  par1<-par[1]
+  par2<-par[2]
+
+  n=length(u1)
+  vec=matrix(data=0,nrow=n,ncol=1)
+
+  vec=dnorm(u1, mean = par1, sd = par2)
+
+  sumlik=-sum(dmvnorm(cbind(x1,x2), c(0,0), matrix(c(1, rho, rho, 1), ncol=2), log=T));
+
+  # Output
+  cat("Normal log-likelihood ->",sprintf("%4.4f",- sumlik),"\n")
+
+  return(sumlik)
+}
+
+```
+
+```{r}
+fit <- BiCopEst(u1,u2,family=1,method="mle",se=TRUE) 
+BiCopPDF(u1, u2, family=1,par = fit$par,par2 = fit$par2) 
+#the resulting estimate with the parameter value estimated using function BiCopEst.
+```
+
 #(d)

### 2019-04-29 STAT0017_ICA2/17052480.Rmd
final test

@@
   par2<-par[2]
-
+  rho <-par[3]
   n=length(u1)
-  vec=matrix(data=0,nrow=n,ncol=1)
-
-  vec=dnorm(u1, mean = par1, sd = par2)
-
-  sumlik=-sum(dmvnorm(cbind(x1,x2), c(0,0), matrix(c(1, rho, rho, 1), ncol=2), log=T));
+  sumlik=-sum(dmvnorm(cbind(u[,1],u[,2]), c(par1,par2), matrix(c(1, rho, rho, 1), ncol=2), log=T))
 
   # Output
-  cat("Normal log-likelihood ->",sprintf("%4.4f",- sumlik),"\n")
+  cat("log-likelihood ->",sprintf("%4.4f",- sumlik),"\n")
 
@@
 ```{r}
-fit <- BiCopEst(u1,u2,family=1,method="mle",se=TRUE) 
-BiCopPDF(u1, u2, family=1,par = fit$par,par2 = fit$par2) 
+library("CDVine")
+fit <- BiCopEst(u[,1],u[,2],family=1,method="mle",se=TRUE)
+#BiCopPDF(u1, u2, family=1,par = fit$par,par2 = fit$par2) 
 #the resulting estimate with the parameter value estimated using function BiCopEst.
 ```
-
-#(d)

### 2019-05-01 STAT0017_ICA2/17052480.R
Update 17052480.R

@@ -132,7 +132,7 @@ ADtest3$p.value
 
 
 
-
+#u=cbind(ret1,ret2,ret3)
 u=cbind(u1,u2,u3)
 cor(u[,1:3],method = c("kendall"))
 
@@ -240,3 +240,4 @@ var[3,]=quantile(retport3,c(0.01,0.05))
 
 ### VaR for portfolio returns generated using different coplas
 var
+

### 2019-06-24 MSc Project/PLSR for corn data.R
Create PLSR for corn data.R

@@ -1,0 +1,63 @@
+library("R.matlab")
+library(pls) 
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+propvals <- rawdata$propvals$data
+
+corn.pls <- plsr(m5data, propvals[,1], ncomp = 4, mode = "regression", tol = 1e-25)
+
+
+
+install.packages("pls")
+
+library(pls)
+
+n <- 50
+
+x1 <- rnorm(n); xx1 <- scale(x1)
+
+x2 <- rnorm(n); xx2 <- scale(x2)
+
+y <- x1 + x2 + rnorm(n,0,0.1); yy <- scale(y)
+
+p <- plsr(yy ~ xx1+xx2, ncomp=1)
+
+( w <- loading.weights(p) )#看这个主成分与原始xx1与xx2之间的回归系数
+
+a <- w["xx1",]
+
+b <- w["xx2",]
+
+a^2+b^2
+
+cor(y, a*xx1+b*xx2)#a,b是如何确定的，就是让这个回归系数最大，也就是带有主成分回归模型R方最大
+
+p$coef #这样就获取了yy跟xx1与xx2之间的回归系数的回归系数，如何获取的，请看下面的分析
+
+x <- a*xx1+b*xx2
+
+coef(lm(yy~0+x))
+
+coef(lm(yy~0+x))*a
+
+coef(lm(yy~0+x))*b
+
+#有了上面这个系数，可以顺利写出yy跟xx1与xx2之间的回归回归方程
+
+
+
+pls1<-plsr(propvals[,1]~m5data,validation="LOO",jackknife=TRUE,method="widekernelpls")
+summary(pls1,what="all")
+
+## 偏最小二乘回归
+library(lars)
+library(pls)
+
+ap = plsr(propvals[,1]~m5data, 64, validation = "CV")
+# CV准则下，不同评价指标
+validationplot(ap)
+# 不同准则
+RMSEP(ap)
+MSEP(ap)
+R2(ap)

### 2019-06-24 MSc Project/PLSR for corn data.R
Update PLSR for corn data.R

@@ -47,14 +47,14 @@ coef(lm(yy~0+x))*b
 
 
 
-pls1<-plsr(propvals[,1]~m5data,validation="LOO",jackknife=TRUE,method="widekernelpls")
+pls1<-plsr(propvals[,1]~m5data,10,validation="LOO",jackknife=TRUE,method="widekernelpls")
 summary(pls1,what="all")
 
 ## 偏最小二乘回归
 library(lars)
 library(pls)
 
-ap = plsr(propvals[,1]~m5data, 64, validation = "CV")
+ap = plsr(propvals[,1]~m5data, 10, validation = "CV")
 # CV准则下，不同评价指标
 validationplot(ap)
 # 不同准则

### 2019-06-25 MSc Project/PLSR for corn data.R
Update PLSR for corn data.R

@@ -8,45 +8,6 @@ propvals <- rawdata$propvals$data
 corn.pls <- plsr(m5data, propvals[,1], ncomp = 4, mode = "regression", tol = 1e-25)
 
 
-
-install.packages("pls")
-
-library(pls)
-
-n <- 50
-
-x1 <- rnorm(n); xx1 <- scale(x1)
-
-x2 <- rnorm(n); xx2 <- scale(x2)
-
-y <- x1 + x2 + rnorm(n,0,0.1); yy <- scale(y)
-
-p <- plsr(yy ~ xx1+xx2, ncomp=1)
-
-( w <- loading.weights(p) )#看这个主成分与原始xx1与xx2之间的回归系数
-
-a <- w["xx1",]
-
-b <- w["xx2",]
-
-a^2+b^2
-
-cor(y, a*xx1+b*xx2)#a,b是如何确定的，就是让这个回归系数最大，也就是带有主成分回归模型R方最大
-
-p$coef #这样就获取了yy跟xx1与xx2之间的回归系数的回归系数，如何获取的，请看下面的分析
-
-x <- a*xx1+b*xx2
-
-coef(lm(yy~0+x))
-
-coef(lm(yy~0+x))*a
-
-coef(lm(yy~0+x))*b
-
-#有了上面这个系数，可以顺利写出yy跟xx1与xx2之间的回归回归方程
-
-
-
 pls1<-plsr(propvals[,1]~m5data,10,validation="LOO",jackknife=TRUE,method="widekernelpls")
 summary(pls1,what="all")
 

### 2019-06-25 MSc Project/PLSR for corn data.R
Update PLSR for corn data.R

@@ -22,3 +22,19 @@ validationplot(ap)
 RMSEP(ap)
 MSEP(ap)
 R2(ap)
+
+
+
+# NOT RUN {
+data(yarn)
+nir.mvr <- mvr(density ~ NIR, ncomp = 5, data = yarn[yarn$train,])
+
+## Predicted responses for models with 1, 2, 3 and 4 components
+pred.resp <- predict(nir.mvr, ncomp = 1:4, newdata = yarn[!yarn$train,])
+
+## Predicted responses for a single model with components 1, 2, 3, 4
+predict(nir.mvr, comps = 1:4, newdata = yarn[!yarn$train,])
+
+## Predicted scores
+predict(nir.mvr, comps = 1:3, type = "scores", newdata = yarn[!yarn$train,])
+# }

### 2019-06-25 MSc Project/PLSR for corn data.R
Update PLSR for corn data.R

@@ -1,15 +1,23 @@
-library("R.matlab")
+library(R.matlab)
 library(pls) 
+library(lars)
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
 m5data <- rawdata$m5spec$data
 mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
 propvals <- rawdata$propvals$data
 
-corn.pls <- plsr(m5data, propvals[,1], ncomp = 4, mode = "regression", tol = 1e-25)
+n=60                             #the number of calibration
+sample <- sample(1:80)           #set random order; the begin of reset order
+calibration <- cbind(propvals[,1][sample[1:n] ],m5data[sample[1:n], ])#first nth rows for calibration
+prediction <- cbind(propvals[,1][sample[n+1:80] ],m5data[sample[n+1:80], ])#n+1th to the end sample for  prediction
+
+corn.pls <- plsr(calibration[,1]~calibration[,-1], ncomp = 10,data= calibration, validation="LOO",jackknife=TRUE,method="widekernelpls")
+summary(corn.pls,what="all")
+pred.resp <- predict(corn.pls, ncomp = 1:10,newdata = m5data[prediction])
 
 
-pls1<-plsr(propvals[,1]~m5data,10,validation="LOO",jackknife=TRUE,method="widekernelpls")
-summary(pls1,what="all")
+
 
 ## 偏最小二乘回归
 library(lars)

### 2019-06-25 MSc Project/PLSR for corn data.R
Update PLSR for corn data.R

@@ -11,38 +11,35 @@ n=60                             #the number of calibration
 sample <- sample(1:80)           #set random order; the begin of reset order
 calibration <- cbind(propvals[,1][sample[1:n] ],m5data[sample[1:n], ])#first nth rows for calibration
 prediction <- cbind(propvals[,1][sample[n+1:80] ],m5data[sample[n+1:80], ])#n+1th to the end sample for  prediction
-
-corn.pls <- plsr(calibration[,1]~calibration[,-1], ncomp = 10,data= calibration, validation="LOO",jackknife=TRUE,method="widekernelpls")
+corn.pls <- plsr(calibration[,1]~calibration[,-1], ncomp = 10, validation="LOO",jackknife=TRUE,method="widekernelpls")
 summary(corn.pls,what="all")
-pred.resp <- predict(corn.pls, ncomp = 1:10,newdata = m5data[prediction])
+pred.resp <- predict(corn.pls, comps = 1:10, newdata = prediction[,-1])
 
 
 
 
-## 偏最小二乘回归
-library(lars)
-library(pls)
-
-ap = plsr(propvals[,1]~m5data, 10, validation = "CV")
-# CV准则下，不同评价指标
-validationplot(ap)
-# 不同准则
-RMSEP(ap)
-MSEP(ap)
-R2(ap)
 
 
 
-# NOT RUN {
-data(yarn)
-nir.mvr <- mvr(density ~ NIR, ncomp = 5, data = yarn[yarn$train,])
 
-## Predicted responses for models with 1, 2, 3 and 4 components
-pred.resp <- predict(nir.mvr, ncomp = 1:4, newdata = yarn[!yarn$train,])
+library("pls")
+set.seed(123)
+bands=101
+spectra = matrix(runif(56*bands),ncol=bands)
+DF <- data.frame(spectra = I(spectra),
+                 height = rpois(56,10),
+                 fbm = rpois(56,10),
+                 nitrogen = rpois(56,10),
+                 carbon = rpois(56,10),
+                 chl = rpois(56,10),
+                 ID = 1:56)
+class(DF$spectra) <- "matrix" # just to be certain, it was "AsIs"
+str(DF)
 
-## Predicted responses for a single model with components 1, 2, 3, 4
-predict(nir.mvr, comps = 1:4, newdata = yarn[!yarn$train,])
+DF$train <- rep(FALSE, 56)
+DF$train[1:20] <- TRUE
 
[…]

### 2019-06-25 MSc Project/PLSR for corn V2.R
Create PLSR for corn V2.R

@@ -1,0 +1,26 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+n=60                             #the number of calibration
+sample <- sample(1:80)           #set random order; the begin of reset order
+calibration <- cbind(propvals[,1][sample[1:n] ],m5data[sample[1:n], ])#first nth rows for calibration
+prediction <- cbind(propvals[,1][sample[n+1:80] ],m5data[sample[n+1:80], ])#n+1th to the end sample for  prediction
+corn.pls <- plsr(calibration[,1]~calibration[,-1], ncomp = 10, validation="LOO",jackknife=TRUE,method="widekernelpls")
+summary(corn.pls,what="all")
+pred.resp <- predict(corn.pls, comps = 1:10, newdata = prediction[,-1])
+DF <- data.frame(NIR = I(m5data),
+                 y=propvals[,1])
+class(DF$NIR) <- "matrix" # just to be certain, it was "AsIs"
+str(DF)
+DF$train <- rep(FALSE, 20)
+DF$train[1:60] <- TRUE
+corn.pls <- plsr(y ~ NIR, data = DF, ncomp = 10, validation = 
+                   "LOO", jackknife = TRUE, subset = train)
+res <- predict(corn.pls, ncomp = 10, newdata = DF[!DF$train,])
+sum((res-DF[!DF$train,]$y)^2)

### 2019-06-25 MSc Project/PLSR for corn V2.R
Update PLSR for corn V2.R

@@ -7,20 +7,25 @@ mp5data <- rawdata$mp5spec$data
 mp6data <- rawdata$mp6spec$data
 propvals <- rawdata$propvals$data
 
-n=60                             #the number of calibration
-sample <- sample(1:80)           #set random order; the begin of reset order
-calibration <- cbind(propvals[,1][sample[1:n] ],m5data[sample[1:n], ])#first nth rows for calibration
-prediction <- cbind(propvals[,1][sample[n+1:80] ],m5data[sample[n+1:80], ])#n+1th to the end sample for  prediction
-corn.pls <- plsr(calibration[,1]~calibration[,-1], ncomp = 10, validation="LOO",jackknife=TRUE,method="widekernelpls")
-summary(corn.pls,what="all")
-pred.resp <- predict(corn.pls, comps = 1:10, newdata = prediction[,-1])
-DF <- data.frame(NIR = I(m5data),
-                 y=propvals[,1])
-class(DF$NIR) <- "matrix" # just to be certain, it was "AsIs"
-str(DF)
-DF$train <- rep(FALSE, 20)
-DF$train[1:60] <- TRUE
-corn.pls <- plsr(y ~ NIR, data = DF, ncomp = 10, validation = 
-                   "LOO", jackknife = TRUE, subset = train)
-res <- predict(corn.pls, ncomp = 10, newdata = DF[!DF$train,])
-sum((res-DF[!DF$train,]$y)^2)
+n=60                                                 #the number of calibration
+
+corn_PLS=function(n){                                #n is the number of calibration
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(m5data),                  #input data
+                   y=propvals[,1])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = 10, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,11]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = 10, newdata = DF[!DF$train,])
[…]

### 2019-06-25 MSc Project/PLSR for corn V2.R
Update PLSR for corn V2.R

@@ -27,5 +27,8 @@ corn_PLS=function(n){                                #n is the number of calibra
   #plot(R2(corn.pls))                                #check point
   return(cbind(RMSECV,RMSEP))
 }
- corn_PLS(n)
-repeat
+corn_PLS(n)
+PlotData <- data.frame(calibration <- rep(20:70,10)
+)
+test <- as.matrix(rep(20:70,10))
+apply(test,1,corn_PLS)

### 2019-06-25 MSc Project/PLSR for corn V2.R
Update PLSR for corn V2.R

@@ -1,15 +1,15 @@
 library(R.matlab)
 library(pls) 
 library(lars)
+library(ggplot2)
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
 m5data <- rawdata$m5spec$data
 mp5data <- rawdata$mp5spec$data
 mp6data <- rawdata$mp6spec$data
 propvals <- rawdata$propvals$data
 
-n=60                                                 #the number of calibration
-
 corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                                  #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,1])
@@ -17,18 +17,22 @@ corn_PLS=function(n){                                #n is the number of calibra
   #str(DF)                                           #check point
   DF$train <- rep(FALSE, 80)
   DF$train[sample<=n] <- TRUE                        #chose calibration
-  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = 10, validation="LOO", jackknife = TRUE, subset = train)
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
   #summary(corn.pls,what="all")                      #check point
-  RMSECV <- RMSEP(corn.pls)$val[1,1,11]
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
   #print(RMSECV)                                     #check point
-  predict <- predict(corn.pls, ncomp = 10, newdata = DF[!DF$train,])
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
   RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
   #print(RMSEP)                                      #check point
   #plot(R2(corn.pls))                                #check point
   return(cbind(RMSECV,RMSEP))
 }
-corn_PLS(n)
-PlotData <- data.frame(calibration <- rep(20:70,10)
-)
-test <- as.matrix(rep(20:70,10))
-apply(test,1,corn_PLS)
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,10))                         #the number of calibration
+PlsResult <- apply(n,1,corn_PLS)
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))
[…]

### 2019-06-25 MSc Project/PLSR for corn V2.Rmd
r markdown

---
title: "PLSR for corn V2 PDF Markdown"
author: "Hongwei Peng"
date: "25/06/2019"
output: pdf_document
---
```{r}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,1])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=10")
```

```{r}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,2])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=10")
```

```{r}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,3])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=10")
```

```{r}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,4])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=10")
```

### 2019-06-25 MSc Project/PLSR for corn V2.R

@@ -9,7 +9,7 @@ mp6data <- rawdata$mp6spec$data
 propvals <- rawdata$propvals$data
 
 corn_PLS=function(n){                                #n is the number of calibration
-  NV <- 10                                                  #number of variables 
+  NV <- 10                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,1])
@@ -25,14 +25,17 @@ corn_PLS=function(n){                                #n is the number of calibra
   RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
   #print(RMSEP)                                      #check point
   #plot(R2(corn.pls))                                #check point
-  return(cbind(RMSECV,RMSEP))
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
 }
 #corn_PLS(n)
-n <- as.matrix(rep(20:70,10))                         #the number of calibration
-PlsResult <- apply(n,1,corn_PLS)
-PlotData <- as.data.frame(cbind(n,t(PlsResult)))
+n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData)
-boxplot(V3~V1,data=PlotData)
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
 PlotData
 
+boxplot(V1~V2*V3, data=PlotData, notch=TRUE, 
+        col=(c("gold","darkgreen")),
+        main="PLS", xlab="Number of Calibration", ylab="RMSECV and RMSEP")

### 2019-06-25 MSc Project/PLSR_for_corn_V2.Rmd
times 3 and run

--- 2019-06-25 MSc Project/PLSR for corn V2.Rmd
@@
 ---
-```{r}
+```{r echo=FALSE}
 library(R.matlab)
@@
 
-```{r}
+```{r echo=FALSE}
 library(R.matlab)

### 2019-06-25 MSc Project/PLSR for corn V2.R

@@ -35,6 +35,7 @@ par(mfrow=c(1,2))
 boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
 PlotData
+apply(PlotData,2,mean)
 
 boxplot(V1~V2*V3, data=PlotData, notch=TRUE, 
         col=(c("gold","darkgreen")),

### 2019-06-25 MSc Project/Untitled.Rmd
finish 1 steps

---
title: "PLSR for corn V2 PDF Markdown"
author: "Hongwei Peng"
date: "25/06/2019"
output: pdf_document
---
```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,1])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,2])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,3])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(m5data),                  #input data
                   y=propvals[,4])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~m5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=10")
apply(PlotData,2,mean)
```

###############

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp5data),                  #input data
                   y=propvals[,1])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp5data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp5data),                  #input data
                   y=propvals[,2])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp5data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp5data),                  #input data
                   y=propvals[,3])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp5data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp5data),                  #input data
                   y=propvals[,4])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp5data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp5data Loop=10")
apply(PlotData,2,mean)
```

#################

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp6data),                  #input data
                   y=propvals[,1])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp6data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp6data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp6data),                  #input data
                   y=propvals[,2])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp6data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp6data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp6data),                  #input data
                   y=propvals[,3])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp6data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp6data Loop=10")
apply(PlotData,2,mean)
```

```{r echo=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
m5data <- rawdata$m5spec$data
mp5data <- rawdata$mp5spec$data
mp6data <- rawdata$mp6spec$data
propvals <- rawdata$propvals$data

corn_PLS=function(n){                                #n is the number of calibration
  NV <- 10                                           #number of variables 
  sample <- sample(1:80)                             #set random order; the begin of reset order
  DF <- data.frame(NIR = I(mp6data),                  #input data
                   y=propvals[,4])
  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
  #str(DF)                                           #check point
  DF$train <- rep(FALSE, 80)
  DF$train[sample<=n] <- TRUE                        #chose calibration
  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
  #summary(corn.pls,what="all")                      #check point
  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
  #print(RMSECV)                                     #check point
  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
  #print(RMSEP)                                      #check point
  #plot(R2(corn.pls))                                #check point
  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
}
#corn_PLS(n)
n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
PlsResult <- apply(n,1,corn_PLS)                     #loop
PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
par(mfrow=c(1,2))
boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp6data Loop=10")
boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp6data Loop=10")
apply(PlotData,2,mean)
```

### 2019-06-25 MSc Project/temp.Rmd
finish 1 steps

---
title: "Temp"
author: "Hongwei Peng"
date: "25/06/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-07-03 MSc Project/PLSR for corn V2.Rmd
test

@@
 #corn_PLS(n)
-n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
 PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=10")
+apply(PlotData,2,mean)
 ```
 
-```{r}
+```{r echo=FALSE}
 library(R.matlab)
@@
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=10")
+apply(PlotData,2,mean)
 ```
 
-```{r}
+```{r echo=FALSE}
 library(R.matlab)
@@
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=10")
+apply(PlotData,2,mean)
 ```
 
-```{r}
+```{r echo=FALSE}
 library(R.matlab)
@@
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=10")
+apply(PlotData,2,mean)
 ```
+
+###############
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp5data),                  #input data
+                   y=propvals[,1])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp5data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp5data Loop=10")
+apply(PlotData,2,mean)
+```
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp5data),                  #input data
+                   y=propvals[,2])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp5data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp5data Loop=10")
+apply(PlotData,2,mean)
+```
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp5data),                  #input data
+                   y=propvals[,3])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp5data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp5data Loop=10")
+apply(PlotData,2,mean)
+```
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp5data),                  #input data
+                   y=propvals[,4])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp5data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp5data Loop=10")
+apply(PlotData,2,mean)
+```
+
+#################
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp6data),                  #input data
+                   y=propvals[,1])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp6data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp6data Loop=10")
+apply(PlotData,2,mean)
+```
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp6data),                  #input data
+                   y=propvals[,2])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp6data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp6data Loop=10")
+apply(PlotData,2,mean)
+```
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp6data),                  #input data
+                   y=propvals[,3])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp6data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp6data Loop=10")
+apply(PlotData,2,mean)
+```
+
+```{r echo=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(mp6data),                  #input data
+                   y=propvals[,4])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,200))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp6data Loop=10")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp6data Loop=10")
+apply(PlotData,2,mean)
+```

### 2019-07-03 MSc Project/scaled PLS for corn data.R
scaled

@@ -1,0 +1,38 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- scale(rawdata$propvals$data)
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 6                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(m5data),                  #input data
+                   y=propvals[,1])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+apply(PlotData,2,mean)
+

### 2019-07-03 MSc Project/scaled PLS for corn data.R
Update scaled PLS for corn data.R

@@ -9,7 +9,7 @@ mp6data <- rawdata$mp6spec$data
 propvals <- scale(rawdata$propvals$data)
 
 corn_PLS=function(n){                                #n is the number of calibration
-  NV <- 6                                           #number of variables 
+  NV <- 10                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,1])

### 2019-07-03 MSc Project/scaled PLS for corn data.R
Update scaled PLS for corn data.R

@@ -3,7 +3,7 @@ library(pls)
 library(lars)
 library(ggplot2)
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-m5data <- rawdata$m5spec$data
+m5data <- scale(rawdata$m5spec$data)
 mp5data <- rawdata$mp5spec$data
 mp6data <- rawdata$mp6spec$data
 propvals <- scale(rawdata$propvals$data)

### 2019-07-03 MSc Project/scaled PLS for corn data.R
Update scaled PLS for corn data.R

@@ -3,10 +3,10 @@ library(pls)
 library(lars)
 library(ggplot2)
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-m5data <- scale(rawdata$m5spec$data)
-mp5data <- rawdata$mp5spec$data
-mp6data <- rawdata$mp6spec$data
-propvals <- scale(rawdata$propvals$data)
+m5data <-  apply(rawdata$m5spec$data,2,scale)
+mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+propvals <- apply(rawdata$propvals$data,2,scale)
 
 corn_PLS=function(n){                                #n is the number of calibration
   NV <- 10                                           #number of variables 

### 2019-07-04 MSc Project/scaled PLS for corn data.R
Update scaled PLS for corn data.R

@@ -36,3 +36,4 @@ boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PL
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
 apply(PlotData,2,mean)
 
+

### 2019-07-04 MSc Project/scaled PLS for corn data.R
Update scaled PLS for corn data.R

@@ -9,7 +9,7 @@ mp6data <-  apply(rawdata$mp6spec$data,2,scale)
 propvals <- apply(rawdata$propvals$data,2,scale)
 
 corn_PLS=function(n){                                #n is the number of calibration
-  NV <- 10                                           #number of variables 
+  NV <- 16                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,1])

### 2019-07-04 MSc Project/scaled PLS for corn data.R
run long pdf

@@ -9,7 +9,7 @@ mp6data <-  apply(rawdata$mp6spec$data,2,scale)
 propvals <- apply(rawdata$propvals$data,2,scale)
 
 corn_PLS=function(n){                                #n is the number of calibration
-  NV <- 16                                           #number of variables 
+  NV <- 5                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,1])

### 2019-07-04 MSc Project/scaled_PLSR_for_corn_data.Rmd
test

--- 2019-07-03 MSc Project/PLSR for corn V2.Rmd
@@
 ---
-title: "PLSR for corn V2 PDF Markdown"
+title: "Scaled PLSR for corn data"
 author: "Hongwei Peng"
-date: "25/06/2019"
+date: "04/07/2019"
 output: pdf_document
@@
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-m5data <- rawdata$m5spec$data
-mp5data <- rawdata$mp5spec$data
-mp6data <- rawdata$mp6spec$data
-propvals <- rawdata$propvals$data
+m5data <-  apply(rawdata$m5spec$data,2,scale)
+mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+propvals <- apply(rawdata$propvals$data,2,scale)
 
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~m5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~m5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~m5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~m5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp5data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp5data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp6data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp6data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp6data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp6data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp6data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp6data Loop=200 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp6data Loop=200 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp6data Loop=200 scaled")
 apply(PlotData,2,mean)

### 2019-07-04 MSc Project/scaled PLS for corn data.R

@@ -9,7 +9,7 @@ mp6data <-  apply(rawdata$mp6spec$data,2,scale)
 propvals <- apply(rawdata$propvals$data,2,scale)
 
 corn_PLS=function(n){                                #n is the number of calibration
-  NV <- 5                                           #number of variables 
+  NV <- 10                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,1])

### 2019-07-04 MSc Project/scaled PLS for corn data test.R
add test .R

@@ -1,0 +1,39 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <-  apply(rawdata$m5spec$data,2,scale)
+mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+propvals <- apply(rawdata$propvals$data,2,scale)
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 10                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(m5data),                  #input data
+                   y=propvals[,1])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
+PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+apply(PlotData,2,mean)
+
+

### 2019-07-04 MSc Project/scaled PLS for corn data test.R
finished

@@ -12,7 +12,7 @@ corn_PLS=function(n){                                #n is the number of calibra
   NV <- 10                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
-                   y=propvals[,1])
+                   y=propvals[,2])
   class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
   #str(DF)                                           #check point
   DF$train <- rep(FALSE, 80)
@@ -28,12 +28,12 @@ corn_PLS=function(n){                                #n is the number of calibra
   return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
 }
 #corn_PLS(n)
-n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
 PlsResult <- apply(n,1,corn_PLS)                     #loop
 PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
 par(mfrow=c(1,2))
 boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-apply(PlotData,2,mean)
-
-
+PlotDataMean <- apply(PlotData,2,mean)
+PlotDataSd <- apply(PlotData,2,sd)
+cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])

### 2019-07-04 MSc Project/SavitzkyGolay PLS for corn data.R
savitzkygolay

@@ -1,0 +1,42 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
+mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
+mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}) )
+propvals <- rawdata$propvals$data
+
+corn_PLS=function(n){                                #n is the number of calibration
+  NV <- 6                                           #number of variables 
+  sample <- sample(1:80)                             #set random order; the begin of reset order
+  DF <- data.frame(NIR = I(m5data),                  #input data
+                   y=propvals[,1])
+  class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+  #str(DF)                                           #check point
+  DF$train <- rep(FALSE, 80)
+  DF$train[sample<=n] <- TRUE                        #chose calibration
+  corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+  #summary(corn.pls,what="all")                      #check point
+  RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+  #print(RMSECV)                                     #check point
+  predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+  RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+  #print(RMSEP)                                      #check point
+  #plot(R2(corn.pls))                                #check point
+  return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+}
+#corn_PLS(n)
+n <- as.matrix(rep(60,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+PlsResult <- apply(n,1,corn_PLS)                     #loop
[…]

### 2019-07-04 MSc Project/SavitzkyGolay PLS for corn data.R
finish

@@ -4,7 +4,7 @@ library(lars)
 library(ggplot2)
 library("MALDIquant")
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
+m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=10, polynomialOrder=2)}))
 mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
 mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}) )
 propvals <- rawdata$propvals$data
@@ -13,7 +13,7 @@ corn_PLS=function(n){                                #n is the number of calibra
   NV <- 6                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
-                   y=propvals[,1])
+                   y=propvals[,4])
   class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
   #str(DF)                                           #check point
   DF$train <- rep(FALSE, 80)

### 2019-07-05 MSc Project/SavitzkyGolay PLS for corn data.R
finish

@@ -3,6 +3,7 @@ library(pls)
 library(lars)
 library(ggplot2)
 library("MALDIquant")
+library(prospectr)
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
 m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=10, polynomialOrder=2)}))
 mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
@@ -39,4 +40,17 @@ PlotDataMean <- apply(PlotData,2,mean)
 PlotDataSd <- apply(PlotData,2,sd)
 cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])
 
+
+
+data(NIRsoil)
+spc <- 1/10^NIRsoil$spc # conversion to reflectance
+opar <- par(no.readonly = TRUE)
+par(mfrow=c(2,1),mar=c(4,4,2,2))
+# plot of the 10 first spectra
+matplot(as.numeric(colnames(spc)),t(spc[1:10,]),type='l',xlab='',ylab='Reflectance')
+mtext('Raw spectra')
+sg <- savitzkyGolay(X = spc,1,3,11,delta.wav=2)
+matplot(as.numeric(colnames(sg)),t(sg[1:10,]),type='l',xlab='Wavelength /nm',ylab='1st derivative')
+mtext('1st derivative spectra')
+par(opar)
 

### 2019-07-05 MSc Project/SavitzkyGolay PLS for corn data.R
savitzkyGolay

@@ -5,13 +5,17 @@ library(ggplot2)
 library("MALDIquant")
 library(prospectr)
 rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=10, polynomialOrder=2)}))
-mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
-mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}) )
+#m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=10, polynomialOrder=2)}))
+#mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}))
+#mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {MALDIquant:::.savitzkyGolay(x,halfWindowSize=21, polynomialOrder=2)}) )
+m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {savitzkyGolay(x,1,2,21)}))
+mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {savitzkyGolay(x,1,2,21)}))
+mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {savitzkyGolay(x,1,2,21)}) )
+
 propvals <- rawdata$propvals$data
 
 corn_PLS=function(n){                                #n is the number of calibration
-  NV <- 6                                           #number of variables 
+  NV <- 5                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
                    y=propvals[,4])
@@ -40,17 +44,4 @@ PlotDataMean <- apply(PlotData,2,mean)
 PlotDataSd <- apply(PlotData,2,sd)
[…]

### 2019-07-07 MSc Project/pls-example.R
add example

@@ -1,0 +1,71 @@
+install.packages("pls")
+library(pls)
+#do a PLSR on the gasoline data to illustrate the use of pls
+data(gasoline)
+options(digits = 4)
+gasTrain <- gasoline[1:50,] #Row 1~50
+gasTest <- gasoline[51:60,] #Row 51~60
+
+#fit a PLSR model
+gas1 <- plsr(octane ~ NIR, ncomp = 10, data = gasTrain, validation = "LOO")
+#get an overview of the fit and validation results
+summary(gas1)  #The validation results here are Root Mean Squared Error of Prediction (RMSEP). 
+               #There are two cross-validation estimates: 
+               #CV is the ordinary CV estimate, and adjCV is a bias-corrected CV estimate 
+
+#Cross-validated RMSEP curves for the gasoline data
+#Figure 2(simpler)
+plot(RMSEP(gas1), legendpos = "topright")
+
+#Figure 3
+#the cross-validated predictions with two components versus measured values
+plot(gas1, ncomp = 2, asp = 1, line = TRUE)
+
+#Figure 4
+#a pairwise plot of the score values for the three first components
+plot(gas1, plottype = "scores", comps = 1:3)
+
+#extract the explained variances
+explvar(gas1)
+
+#Figure 5
+plot(gas1, "loadings", comps = 1:2, legendpos = "topleft",
+             labels = "numbers", xlab = "nm")
+abline(h = 0)
+
+#predict the response values of new observations
+predict(gas1, ncomp = 2, newdata = gasTest)
+#calculate the test set RMSEP
+RMSEP(gas1, newdata = gasTest)
+
+
+
+#5 Fitting models
+data(yarn)
+dens1 <- plsr(density ~ NIR, ncomp = 5, data = yarn)
+
+dim(oliveoil$sensory)
+plsr(sensory ~ chemical, data = oliveoil)
+trainind <- which(yarn$train == TRUE)
+dens2 <- update(dens1, subset = trainind)
+dens3 <- update(dens1, ncomp = 10)
+live1 <- plsr(sensory ~ chemical, scale = TRUE, data = oliveoil)
+gas2 <- plsr(octane ~ msc(NIR), ncomp = 10, data = gasTrain)
+predict(gas2, ncomp = 3, newdata = gasTest)
+
+
+#Choosing the number of components with cross-validation
[…]

### 2019-07-07 MSc Project/pls-example.R
add some books

@@ -1,71 +1,0 @@
-install.packages("pls")
-library(pls)
-#do a PLSR on the gasoline data to illustrate the use of pls
-data(gasoline)
-options(digits = 4)
-gasTrain <- gasoline[1:50,] #Row 1~50
-gasTest <- gasoline[51:60,] #Row 51~60
-
-#fit a PLSR model
-gas1 <- plsr(octane ~ NIR, ncomp = 10, data = gasTrain, validation = "LOO")
-#get an overview of the fit and validation results
-summary(gas1)  #The validation results here are Root Mean Squared Error of Prediction (RMSEP). 
-               #There are two cross-validation estimates: 
-               #CV is the ordinary CV estimate, and adjCV is a bias-corrected CV estimate 
-
-#Cross-validated RMSEP curves for the gasoline data
-#Figure 2(simpler)
-plot(RMSEP(gas1), legendpos = "topright")
-
-#Figure 3
-#the cross-validated predictions with two components versus measured values
-plot(gas1, ncomp = 2, asp = 1, line = TRUE)
-
-#Figure 4
-#a pairwise plot of the score values for the three first components
-plot(gas1, plottype = "scores", comps = 1:3)
-
-#extract the explained variances
-explvar(gas1)
-
-#Figure 5
-plot(gas1, "loadings", comps = 1:2, legendpos = "topleft",
-             labels = "numbers", xlab = "nm")
-abline(h = 0)
-
-#predict the response values of new observations
-predict(gas1, ncomp = 2, newdata = gasTest)
-#calculate the test set RMSEP
-RMSEP(gas1, newdata = gasTest)
-
-
-
-#5 Fitting models
-data(yarn)
-dens1 <- plsr(density ~ NIR, ncomp = 5, data = yarn)
-
-dim(oliveoil$sensory)
-plsr(sensory ~ chemical, data = oliveoil)
-trainind <- which(yarn$train == TRUE)
-dens2 <- update(dens1, subset = trainind)
-dens3 <- update(dens1, ncomp = 10)
-live1 <- plsr(sensory ~ chemical, scale = TRUE, data = oliveoil)
-gas2 <- plsr(octane ~ msc(NIR), ncomp = 10, data = gasTrain)
-predict(gas2, ncomp = 3, newdata = gasTest)
-
-
-#Choosing the number of components with cross-validation
[…]

### 2019-07-08 MSc Project/parallel PLS for corn data.R
add the parallel

@@ -1,0 +1,51 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+    
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
[…]

### 2019-07-08 MSc Project/parallel SavitzkyGlolay PLS for corn data.R

@@ -1,0 +1,57 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+    
+    NV <- 5                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
[…]

### 2019-07-08 MSc Project/parallel scaled PLS for corn data.R

@@ -1,0 +1,47 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
[…]

### 2019-07-09 MSc Project/Parallel all papers PLS for corn data.Rmd
finish

---
title: "Parallel all papers PLS for corn data"
author: "Hongwei Peng"
date: "09/07/2019"
output: pdf_document
---

#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples

##1~mp6 0.159

###60-20 10

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples

##2~mp6

###60-20 10

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

### 2019-07-09 MSc Project/parallel PLS for corn data.R

@@ -19,8 +19,8 @@ system.time({
     
     NV <- 10                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,3])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
     #str(DF)                                           #check point
     DF$train <- rep(FALSE, 80)
@@ -41,11 +41,11 @@ system.time({
   PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
   par(mfrow=c(1,2))
-  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
   PlotDataMean <- apply(PlotData,2,mean)
   PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2])
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
 })
 stopCluster(cl)

### 2019-07-09 MSc Project/parallel PLS for corn data.R
Update parallel PLS for corn data.R

@@ -19,8 +19,8 @@ system.time({
     
     NV <- 10                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp6data),                  #input data
-                     y=propvals[,3])
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
     #str(DF)                                           #check point
     DF$train <- rep(FALSE, 80)

### 2019-07-10 MSc Project/Parallel all papers PLS for corn data.Rmd
papers

@@
 
-##2~mp6
+##2~mp6 0.107
 
@@
 ```
+
+#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
+
+##3~mp6 0.150
+
+###60-20 10
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
+
+##4~mp6 0.370
+
+###60-20 10
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```

### 2019-07-10 MSc Project/PLSR for corn V2.R

@@ -28,7 +28,7 @@ corn_PLS=function(n){                                #n is the number of calibra
   return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
 }
 #corn_PLS(n)
-n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+n <- as.matrix(rep(40,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
 PlsResult <- apply(n,1,corn_PLS)                     #loop
 PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
 par(mfrow=c(1,2))
@@ -36,7 +36,3 @@ boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PL
 boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
 PlotData
 apply(PlotData,2,mean)
-
-boxplot(V1~V2*V3, data=PlotData, notch=TRUE, 
-        col=(c("gold","darkgreen")),
-        main="PLS", xlab="Number of Calibration", ylab="RMSECV and RMSEP")

### 2019-07-10 MSc Project/parallel SavitzkyGlolay PLS for corn data.R

@@ -27,7 +27,7 @@ system.time({
     NV <- 5                                            #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
     DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
+                     y=propvals[,1])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
     #str(DF)                                           #check point
     DF$train <- rep(FALSE, 80)
@@ -50,8 +50,8 @@ system.time({
   par(mfrow=c(1,2))
   boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
   boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
   cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
 })
 stopCluster(cl)

### 2019-07-10 MSc Project/scaled PLS for corn data test.R

@@ -12,7 +12,7 @@ corn_PLS=function(n){                                #n is the number of calibra
   NV <- 10                                           #number of variables 
   sample <- sample(1:80)                             #set random order; the begin of reset order
   DF <- data.frame(NIR = I(m5data),                  #input data
-                   y=propvals[,2])
+                   y=propvals[,1])
   class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
   #str(DF)                                           #check point
   DF$train <- rep(FALSE, 80)

### 2019-07-10 MSc Project/scaled PLS for corn data.R

@@ -28,7 +28,7 @@ corn_PLS=function(n){                                #n is the number of calibra
   return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
 }
 #corn_PLS(n)
-n <- as.matrix(rep(20:70,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+n <- as.matrix(rep(40,10))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
 PlsResult <- apply(n,1,corn_PLS)                     #loop
 PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
 par(mfrow=c(1,2))

### 2019-07-10 MSc Project/Parallel all papers PLS for corn data.Rmd
finished paper's data simulation

@@
 
-#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
+#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
 
-##1~mp6 0.159
+##60-20 10
 
-###60-20 10
+###1~mp6 0.159
 
@@
 
-#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
+#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
 
-##2~mp6 0.107
+##60-20 10
 
-###60-20 10
+###2~mp6 0.107
 
@@
 
-#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
+#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
 
-##3~mp6 0.150
+##60-20 10
 
-###60-20 10
+###3~mp6 0.150
 
@@
 
-#A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
+#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
 
-##4~mp6 0.370
+##60-20 10
 
-###60-20 10
+###4~mp6 0.370
 
@@
 ```
+
+#2 A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration
+
+##64-16 10
+
+###1~m5 RMSEC = 0.0149; RMSEP = 0.0201
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
+
+##60-20 SavitzkyGolay filler (in)
+
+###1~m5 0.040
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 6                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
+
+##60-20 SavitzkyGolay filler (in)
+
+###2~m5 0.029
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 12                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
+
+##60-20 SavitzkyGolay filler (in)
+
+###3~m5 0.119
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 6                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
+
+##60-20 SavitzkyGolay filler (in)
+
+###4~m5 0.196
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 6                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#4 Reduced PCR/PLSR models by subspace projections
+
+##40-40 Scale 4
+
+###1~m5 0.36
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 4                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#4 Reduced PCR/PLSR models by subspace projections
+
+##40-40 Scale 4
+
+###2~m5 0.97
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 4                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#4 Reduced PCR/PLSR models by subspace projections
+
+##40-40 Scale 4
+
+###3~m5 0.44
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 4                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#4 Reduced PCR/PLSR models by subspace projections
+
+##40-40 Scale 4
+
+###4~m5 0.49
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 4                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#5 Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra
+
+##40-40 Scale 10
+
+###1~mp5 0.357
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 None 10
+
+###2~m5 RMSECV=0.0363; RMSECP=0.04
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 None 10
+
+###4~m5 RMSECV=0.24; RMSECP=0.219
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###1~m5 0.045(06)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 6                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###2~m5 0.028(10)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 10                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###3~m5 0.110(07)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 7                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###4~m5 0.228(05)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 5                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+```
+
+#8 Using consensus interval partial least square in near infrared spectra analysis
+
+##52-26 Delete 75 , 77; 10
+
+###1~m5 RMSECV=0.0124; RMSEP=0.0157
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    m5data <- m5data[,c(-75,-77)]
+    propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#8 Using consensus interval partial least square in near infrared spectra analysis
+
+##52-26 Delete 75 , 77 10
+
+###2~m5 RMSECV=0.0613; RMSEP=0.0673
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    m5data <- m5data[,c(-75,-77)]
+    propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#8 Using consensus interval partial least square in near infrared spectra analysis
+
+##52-26 Delete 75 , 77 10
+
+###3~m5 RMSECV=0.1080; RMSEP=0.1353
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    m5data <- m5data[,c(-75,-77)]
+    propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```
+
+#8 Using consensus interval partial least square in near infrared spectra analysis
+
+##52-26 Delete 75 , 77 10
+
+###4~m5 RMSECV=0.2579; RMSEP=0.2356
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    m5data <- m5data[,c(-75,-77)]
+    propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+})
+stopCluster(cl)
+```

### 2019-07-10 MSc Project/Parallel all papers PLS for corn data.Rmd
fixed

@@
   par(mfrow=c(1,2))
-  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  #PlotDataMean <- apply(PlotData,2,mean)
-  #PlotDataSd <- apply(PlotData,2,sd)
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
   cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')

### 2019-07-11 MSc Project/2nd paper.R
xijie

@@ -1,0 +1,53 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+    
+    NV <- 9                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    #RMSECV <- RMSEP(corn.pls)$val[1,1,NV]             #change RMSECV to RMSEC
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[DF$train,])
+    RMSECV <- sqrt(sum((predict-DF[DF$train,]$y)^2)/(n))
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
[…]

### 2019-07-11 MSc Project/3rd paper.R

@@ -1,0 +1,57 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+    
+    NV <- 5                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
[…]

### 2019-07-11 MSc Project/Parallel all papers PLS for corn data.Rmd
xijie
fixing

@@
 date: "09/07/2019"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 ---
@@
 
-##64-16 10
+##64-16 9 CV=5
 
@@
 
-    NV <- 10                                           #number of variables 
+    NV <- 9                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
     DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    #RMSECV <- RMSEP(corn.pls)$val[1,1,NV]             #change RMSECV to RMSEC
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[DF$train,])
+    RMSECV <- sqrt(sum((predict-DF[DF$train,]$y)^2)/(n))
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
 
+##60-20 SavitzkyGolay filler (in) LOO
+
+###1~m5 0.040
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 5                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
+
+##60-20 SavitzkyGolay filler (in) LOO
+
+###2~m5 0.029
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 12                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
+
 ##60-20 SavitzkyGolay filler (in)
 
-###1~m5 0.040
+###3~m5 0.119
 
@@
     m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
     }))
     mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
     }))
     mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
     }))
@@
     DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,1])
+                     y=propvals[,3])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
@@
 
-###2~m5 0.029
+###4~m5 0.196
 
@@
     m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
     }))
     mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
     }))
     mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 12                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 6                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
 
-#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
-
-##60-20 SavitzkyGolay filler (in)
-
-###3~m5 0.119
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 6                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
-})
-stopCluster(cl)
-
-```
-
-#3 Cross-validation for the selection of spectral variables using the successive projections algorithm
-
-##60-20 SavitzkyGolay filler (in)
-
-###4~m5 0.196
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 6                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
-})
-stopCluster(cl)
-
-```
-
 #4 Reduced PCR/PLSR models by subspace projections
 
-##40-40 Scale 4
-
-###1~m5 0.36
+##40-40 Scale 12
+
+###1~m5 0.3506
 
@@
     propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 4                                           #number of variables 
+    NV <- 12                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
 
-##40-40 Scale 4
-
-###2~m5 0.97
+##40-40 Scale 14
+
+###2~m5 0.6912
 
@@
     propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 4                                           #number of variables 
+    NV <- 14                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
 
-##40-40 Scale 4
-
-###3~m5 0.44
+##40-40 Scale 8
+
+###3~m5 0.4466
 
@@
     propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 4                                           #number of variables 
+    NV <- 8                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
 
-##40-40 Scale 4
-
-###4~m5 0.49
+##40-40 Scale 9
+
+###4~m5 0.5010
 
@@
     propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 4                                           #number of variables 
+    NV <- 9                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
 
-##64-16 None 10
-
-###2~m5 RMSECV=0.0363; RMSECP=0.04
+##64-16 savitzkyGolay filler=(0,2,13) 7 5-fold
+
+###2~m5 RMSECV=0.0729; RMSECP=0.0855
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 7                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 savitzkyGolay filler=(1,2,13) 7 5-fold
+
+###2~m5 RMSECV=0.0577; RMSECP=0.0682
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 7                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 savitzkyGolay filler=(2,2,13) 7 5-fold
+
+###2~m5 RMSECV=0.0370; RMSECP=0.0397
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 7                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 savitzkyGolay filler=(0,2,7) 8 5-fold
+
+###4~m5 RMSECV=0.312; RMSECP=0.214
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 8                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 savitzkyGolay filler=(1,2,7) 8 5-fold
+
+###4~m5 RMSECV=0.248; RMSECP=0.221
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 8                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
+
+##64-16 savitzkyGolay filler=(2,2,7) 8 5-fold
+
+###4~m5 RMSECV=0.347; RMSECP=0.228
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 8                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###1~m5 0.045(06)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)  
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 6                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###2~m5 0.028(10)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 10                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###3~m5 0.110(07)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 7                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+```
+
+#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
+
+##60-20 None (in)
+
+###4~m5 0.228(05)
+
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 5                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  PlotDataMean <- apply(PlotData,2,mean)
+  PlotDataSd <- apply(PlotData,2,sd)
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+```
+
+#8 Using consensus interval partial least square in near infrared spectra analysis
+
+##52-26 Delete 75 , 77; 10
+
+###1~m5 RMSECV=0.0124; RMSEP=0.0157
 
@@
     propvals <- rawdata$propvals$data
-    #m5data <- m5data[,c(-75,-77)]
-    #propvals <- propvals[,c(-75,-77)]
+    m5data <- m5data[,c(-75,-77)]
+    propvals <- propvals[,c(-75,-77)]
 
@@
     DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
   PlotDataSd <- apply(PlotData,2,sd)
-  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
   cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
@@
 
-#6 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 None 10
-
-###4~m5 RMSECV=0.24; RMSECP=0.219
+#8 Using consensus interval partial least square in near infrared spectra analysis
+
+##52-26 Delete 75 , 77 10
+
+###2~m5 RMSECV=0.0613; RMSEP=0.0673
 
@@
     DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
 
-#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 None (in)
-
-###1~m5 0.045(06)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 6                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
-})
-stopCluster(cl)
-
-```
-
-#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 None (in)
-
-###2~m5 0.028(10)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 10                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
-})
-stopCluster(cl)
-
-```
-
-#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 None (in)
-
-###3~m5 0.110(07)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 7                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
-})
-stopCluster(cl)
-
-```
-
-#7 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 None (in)
-
-###4~m5 0.228(05)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 5                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
-})
-stopCluster(cl)
-```
-
 #8 Using consensus interval partial least square in near infrared spectra analysis
 
-##52-26 Delete 75 , 77; 10
-
-###1~m5 RMSECV=0.0124; RMSEP=0.0157
+##52-26 Delete 75 , 77 10
+
+###3~m5 RMSECV=0.1080; RMSEP=0.1353
 
@@
 
-###2~m5 RMSECV=0.0613; RMSEP=0.0673
+###4~m5 RMSECV=0.2579; RMSEP=0.2356
 
@@
     DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
+                     y=propvals[,4])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
@@
 ```
-
-#8 Using consensus interval partial least square in near infrared spectra analysis
-
-##52-26 Delete 75 , 77 10
-
-###3~m5 RMSECV=0.1080; RMSEP=0.1353
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    m5data <- m5data[,c(-75,-77)]
-    propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
-})
-stopCluster(cl)
-```
-
-#8 Using consensus interval partial least square in near infrared spectra analysis
-
-##52-26 Delete 75 , 77 10
-
-###4~m5 RMSECV=0.2579; RMSEP=0.2356
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    m5data <- m5data[,c(-75,-77)]
-    propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
-})
-stopCluster(cl)
-```

### 2019-07-11 MSc Project/5th paper.R

@@ -1,0 +1,47 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 12                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
[…]

### 2019-07-11 MSc Project/6th paper 1st part.R

@@ -1,0 +1,59 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+    
+    NV <- 7                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
[…]

### 2019-07-11 MSc Project/6th paper 2nd part.R

@@ -1,0 +1,59 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+    
+    NV <- 8                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
+    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
[…]

### 2019-07-11 MSc Project/Parallel all papers PLS for corn data.Rmd
finished

@@
 output:
+  pdf_document: default
   html_document:
@@
 
-##60-20 SavitzkyGolay filler (in) LOO
-
-###1~m5 0.040
+##60-20 SavitzkyGolay filler (in) 3-fold but Loo better
+
+###1~m5 0.040(5)
 
@@
   #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(60,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
 
-##60-20 SavitzkyGolay filler (in) LOO
-
-###2~m5 0.029
+##60-20 SavitzkyGolay filler (in) 3-fold
+
+###2~m5 0.029(12)
 
@@
     DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
     #summary(corn.pls,what="all")                      #check point
@@
 
-##60-20 SavitzkyGolay filler (in)
-
-###3~m5 0.119
+##60-20 SavitzkyGolay filler (in) 3-fold
+
+###3~m5 0.119(6)
 
@@
 
-##60-20 SavitzkyGolay filler (in)
-
-###4~m5 0.196
+##60-20 SavitzkyGolay filler (in) 3-fold but Loo better
+
+###4~m5 0.196(6)
 
@@
 
-##60-20 None (in)
+##60-20 savitzkyGolay filler=(1,2,21) (in)
 
@@
 
-##60-20 None (in)
+##60-20 savitzkyGolay=(1,2,21) (in)
 
@@
     DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
+    #plot(RMSEP(gas1), legendpos = "topright")         #check point
     #summary(corn.pls,what="all")                      #check point
@@
 
-##52-26 Delete 75 , 77 10
+##52-26 Delete 75 , 77; 13
 
@@
 
-    NV <- 10                                           #number of variables 
+    NV <- 13                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
     DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
+    #plot(RMSEP(corn.pls), legendpos = "topright")         #check point
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(52,30))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
 
-##52-26 Delete 75 , 77 10
+##52-26 Delete 75 , 77 13
 
@@
     DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
+    #plot(RMSEP(corn.pls), legendpos = "topright")         #check point
     #summary(corn.pls,what="all")                      #check point
@@
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
+  #par(mfrow=c(1,2))
   #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
@@
     DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
     #summary(corn.pls,what="all")                      #check point

### 2019-07-11 MSc Project/the basic value about corn data.R
finish

@@ -1,0 +1,28 @@
+#the basic value
+#none
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+plot(apply(m5data,2,mean))
+plot(apply(m5data,2,sd))
+plot(apply(mp5data,2,sd))
+plot(apply(mp6data,2,sd))
+apply(propvals,2,sd)
+
+#savitzkyGolay
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+  savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+}))
+mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+  savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+}))
+mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+  savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+}))
+propvals <- rawdata$propvals$data
+plot(apply(m5data,2,mean))
+plot(apply(m5data,2,sd))
+apply(propvals,2,sd)

### 2019-07-13 MSc Project/Parallel all papers PLS for corn data.Rmd
finish

@@
     mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
+    #propvals <- apply(rawdata$propvals$data,2,scale)
+    propvals <- rawdata$propvals$data
     NV <- 12                                           #number of variables 

### 2019-07-13 MSc Project/sd test.R

@@ -1,0 +1,81 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+    
+    NV <- 40                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    
+    
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
[…]

### 2019-07-13 MSc Project/the basic value about corn data.R

@@ -7,8 +7,16 @@ mp6data <- rawdata$mp6spec$data
 propvals <- rawdata$propvals$data
 plot(apply(m5data,2,mean))
 plot(apply(m5data,2,sd))
-plot(apply(mp5data,2,sd))
-plot(apply(mp6data,2,sd))
+apply(propvals,2,sd)
+
+#scaled
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <-  apply(rawdata$m5spec$data,2,scale)
+mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+propvals <- apply(rawdata$propvals$data,2,scale)
+plot(apply(m5data,2,mean))
+plot(apply(m5data,2,sd))
 apply(propvals,2,sd)
 
 #savitzkyGolay

### 2019-07-19 MSc Project/number_of_components_test.Rmd
number of conponent test

---
title: "number_of_component"
author: "Hongwei Peng"
date: "19/07/2019"
output: pdf_document
---

#1~m5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #1~m5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #1~m5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#2~m5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #2~m5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #2~m5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#3~m5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #3~m5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #3~m5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#4~m5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #4~m5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #4~m5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#1~mp5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #1~mp5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #1~mp5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#2~mp5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #2~mp5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #2~mp5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#3~mp5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #3~mp5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #3~mp5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#4~mp5 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #4~mp5 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #4~mp5 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#1~mp6 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #1~mp6 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #1~mp6 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#2~mp6 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #2~mp6 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #2~mp6 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#3~mp6 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #3~mp6 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #3~mp6 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

#4~mp6 60-20
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Component", ylab="RMSECV",main="PLS #4~mp6 60-20")
  boxplot(V3~V1,data=PlotData,xlab="Number of Component", ylab="RMSEP",main="PLS #4~mp6 60-20")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

### 2019-07-21 MSc Project/number_of_components_test.Rmd
test component

@@
 date: "19/07/2019"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 ---
@@
   #corn_PLS(n)
-  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(6:50,20))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
   #corn_PLS(n)
-  n <- as.matrix(rep(6:50,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(1:50,20))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop

### 2019-07-24 MSc Project/run.R
myriad R

@@ -1,0 +1,53 @@
+library(R.matlab)
+library(pls)
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   #Myriad dir
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")#PC dir
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+    n=40
+    #NV <- 40                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
[…]

### 2019-07-25 MSc Project/paper_writing/MSc dissertation.tex
myriad

\documentclass[a4paper,12pt,titlepage]{article} % [papersize,fontsize,add title page]{document type}

% This LaTeX file can be turned straight into a pdf by "PDFTeXify" in WinEdit, or
% by any LaTeX --> PDF command in another LaTeX editor
%
% Because figure files are PDF, LaTeX --> DVI does not work

% usepackage{.} reads in additional LaTeX packages
\usepackage[pdftex]{graphicx}       % to include graphs
\usepackage{natbib}                 % A BibTeX style file for references.
\usepackage{amssymb,amsmath}        % for maths symbols and equation numbering

% set up title page
\title{Title}
\author{Hongwei PENG \vspace{2cm} \\
Supervisor : Prof Tom Fearn \vspace{2cm} \\
Department of Statistical Science \\
University College London}
\date{\today} % \today gives today's date. ... or put in the date you want

% set page size and margins
\setlength{\textwidth}{17cm}
\setlength{\textheight}{26cm}
\setlength{\oddsidemargin}{-0.5cm}
\setlength{\evensidemargin}{-0.5cm}
\setlength{\topmargin}{-25mm}
\setlength{\parindent}{0cm}
\setlength{\parskip}{0.3cm}

\let\leq=\leqslant   % for nice-looking inequality signs
\let\geq=\geqslant

\numberwithin{equation}{section}  % equation numbers like (section#.equation#)

\linespread{1}     % 1: single-spacing, 2: double-spacing, 1.5: 1.5-spacing etc

\begin{document}   % start of document
\maketitle         % create title etc
\tableofcontents   % create table of contents
\newpage           % start a new page

\section{Introduction}             % start a new section called `Introduction'
\label{sec:intro}                  % create label for this section
Write the introduction in here.    % content of the introduction

Second paragraph of the introduction \ldots  % New paragraph by leaving a blank line

%\subsection{Structure of the report}         % start a new subsection
\label{sec:structure}                        % section label
In Section \ref{sec:section2} we see how to do various useful things.
In Section \ref{sec:graphs} we import pdf files.
In Section \ref{sec:tables} we create a table. %\ref{label} gives number of section called label.
In Section \ref{sec:maths} we produce some mathematics.
In Section \ref{sec:lists} we produce lists.
In Section \ref{sec:refs} we consider citing books, papers etc..

\section{Name of section 2}                      % start another new section
How to do important things like importing graphs, create tables and produce beautiful mathematics.
\label{sec:section2}                             % label for this section
\subsection{Including a pdf file as a figure}    % create a subsection
\label{sec:graphs}
Figure \ref{fig:space_dep} shows that, even for pairs of sites situated at opposite points of the network, there is strong spatial association in the storm peak values.

\begin{figure}[h]    % start of figure environment
\centering           % put the graph(s) in the centre of the page (horizontally)
\includegraphics[width=7.5cm, angle=0]{Number of loop times mp5~1.pdf}  % width changes size
\includegraphics[width=7.5cm, angle=0]{Rplots.pdf} % angle changes orientation
\vspace*{-0.25cm}    % manual adjustment of vertical spacing
\caption{Scatter plots of contemporaneous $H^{sp}_s$ values at pairs of sites.  Left: contiguous sites (site 30: latitude=3, longitude=6 and site 31: latitude=3 and longitude=7). Right: distant sites (site 1: latitude=1, longitude=1 and site 72: latitude=6, longitude=12)}          % a meaningful caption
\label{fig:space_dep}               % label for the figure
\end{figure}                        % end of figure environment

\subsection{Tables}
\label{sec:tables}
Table \ref{tab:simple} is an example of a fairly simple table.

\renewcommand{\arraystretch}{1.1} % increase the spacing factor value in {}
                                  % to increase the vertical spacing locally for the table
\begin{table}[h]                  % begin table environment (h asks LaTeX to try to put table here)
\centering
\begin{tabular}{lrcrc}            % column alignment  l (left), r (right), c (centre).
\\ \hline                         % \hline for  horizontal line
model   &  neg. log-lik & d.f. & ALRS        & $p$-value \\ \hline           % & separates columns
constant &  22763.20    &       &                &   \\                      % \\ end the current row
linear     &  22742.59    &  2   & 34.23       & $3.7 \times 10^{-8}$ \\     % $$ for maths
quadratic & 22737.09     &  3   & 20.50       & $1.3 \times 10^{-4}$ \\
cubic       & 22737.02     &  4   & 2.09         & 0.72 \\ \hline
\end{tabular}                     % end tabular environment
\caption{Summary of point process modelling in which the location parameter $\mu$ is modelled as a polynomial function of longitude and latitude and $\sigma$ and $\xi$ are constant.  The likelihood ratio tests compare the model with the model in the row above. neg. log-lik = negated maximised log-likelihood; d.f. = degrees of freedom; ALRS = adjusted likelihood ratio statistic.}
\label{tab:simple}
\end{table}
\renewcommand{\arraystretch}{1}  % set spacing factor back to 1

Table \ref{tab:more_complicated} is an example of the use of the \verb!\multicolumn! command to produce column headings that span more than one column.             %\verb!text! quotes text verbatim

\renewcommand{\arraystretch}{1.1}
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|cc|cc|} \hline
                     & \multicolumn{2}{c}{wave height (m)} \vline & \multicolumn{2}{c|}{windpseed (m/s)} \\
return period  & estimate & 95\% CI & estimate & 95\% CI \\ \hline
10 years    &   \,\,\,8.7          &     (\,\,\,8.0, 10.7)  & 10.2 & (\,\,\,5.7, 14.4)  \\
100 years     &   22.1          &    (20.6, 25.6)     & 34.9 & (30.1, 42.4)  \\
1,000 years    &   35.5          &    (32.4, 42.5)    & 63.5 & (67.3, 76.9)  \\
10,000 years    &    40.3         &     (35.2, 52.8)    & 78.6 & (70.9, 98.0)  \\ \hline
\end{tabular}
\caption{Estimates and 95\% confidence intervals of return levels of $H_s$.}
\label{tab:more_complicated}
\end{center}
\end{table}
\renewcommand{\arraystretch}{1}

\subsection{Mathematics}
\label{sec:maths}
\subsubsection*{Maths in text} % subsubsection* produces no subsubsection number
Maths in text needs to be enclosed between dollar signs, e.g. \verb!$x$! gives $x$ (rather than x) and \verb!$f$! gives maths font $f$ (rather than f).

We get Greek symbols like this: $\lambda,\alpha,\beta,\gamma,\delta,\phi,\theta,\ldots$.
\ldots and mathematical operators like this: $1/x, x^{-1}, x_2,xy, \log x, 1+x, -2,x^2, \exp(x), \sin x$.

\subsubsection*{Displayed equations}

\newcommand{\e}{ {\rm e} } % a useful way to produce your own LaTeX commands

Using the \verb!equation! environment: \verb!\begin{equation}! \ldots \verb!\end{equation}!.
An exponential distribution, with mean $1/\lambda$, has probability density function (p.d.f.)
\begin{equation}
f_X(x) = \lambda \, \e^{-\lambda x}, \quad x > 0.  % \,  small space, \quad : bigger space
\label{eqn:one} % label for equation
\end{equation}
This comment refers to equation (\ref{eqn:one}).

An alternative way to produce this displayed equation is to enclose it between \verb!\[! and \verb!\]! \ldots
\[ f_X(x) = \lambda \, \e^{-\lambda x}, \quad x > 0.  \]
\ldots but no equation number is produced.

\subsubsection*{Multi-line displayed equations}
Using the \verb!align! environment (produces equation numbers) \ldots

Suppose that we have a random sample $X_1,\ldots,X_n$ from an exponential distribution with mean $1/\lambda$.
The likelihood function for $\lambda$ is given by
\begin{align}                                                                % align is part of the amsmath package
 L(\lambda) &= \prod_{i=1}^n \lambda \e^{-\lambda x_i} \notag \\             % use \notag for no equation number
 &= \lambda^n \,\e^{-\lambda \sum_{i=1}^n x_i}  \\                           % \, gives a small horizontal space
 &= \lambda^n \e^{-\lambda \displaystyle\sum_{i=1}^n x_i}  \label{eqn:two}\\ % displaystyle gives a big summation sign
 &= \lambda^n \exp \left\{-\lambda \displaystyle\sum_{i=1}^n x_i \right\}.   % \left\{ ... \right\} sizes brackets
\end{align}
Which of the above expressions do you think looks best?  Equation \eqref{eqn:two} is rather ugly...
% \eqref produces (number) (\ref would just produce number).

Using the \verb!align*! environment (produces no equation numbers) \ldots
\begin{align*}                         % align* produces no equation numbers
P(M_n \leq z)&=P(X_1 \leq z,X_2 \leq z,...,X_n \leq z)  \\
    &=P(X_1 \leq z) \times P(X_2 \leq z) \times \cdots \times P(X_n \leq z) \\
    &={F(z)}^n.
\end{align*}

Some more examples \ldots
The cumulative distribution function (c.d.f.) of a Generalized Extreme Value (GEV) distribution is given by
\[ P(X \le x) = \exp\left\{ - \left[ 1+\xi\left(\frac{x-\mu}{\sigma}\right) \right]^{-1/\xi} \right\}, \quad \mbox{for~} 1+\xi\left(\frac{x-\mu}{\sigma}\right) > 0. \]

\newcommand{\disp}{\displaystyle}   % create a shorthand for \displaystyle
\let\hat=\widehat                   % make all hats wide ones
We estimate $\theta$ using the estimator
\[ \widehat{\theta} = \disp\frac1n \frac{\disp\frac1M \disp\sum_{i=1}^M \hat{H}(Y_i)}{\disp\frac1N \disp\sum_{j=1}^N \hat{G}(Z_j)}, \]
where
\[ \hat{G}(y) = \frac1M \sum_{i=1}^M I(Y_i \leq y) \quad \mbox{and} \quad  \hat{H}(z) = \frac1N \sum_{j=1}^N I(Z_j \leq z). \]

Two examples of defining a quantity conditional on the value of another quantity. First using the cases environment \ldots
\begin{equation*}
|x|=
\begin{cases} x & \text{if $x \geq 0$,} \\      % left bracket is put in automatically
-x &\text{if $x \leq 0$.}
\end{cases}
\end{equation*}
\ldots and now using the array environment \ldots
\begin{equation*}
|x|= \left\{                                    % put in left bracket by hand
\begin{array}{rc} x & \text{if $x \geq 0$,} \\  % columns are right justified and centred respectively
-x &\text{if $x \leq 0$.}
\end{array} \right.                             % balance left bracket by a null right bracket
\end{equation*}
{\bf Note: Mathematics should read just like sentences of text, with punctuation, i.e. commas, full stops etc.}

\subsection{Lists}
\label{sec:lists}
% Some more user-defined commands ...
\newcommand{\simiid}{\,\stackrel{{\rm\tiny i.i.d.}}{\sim}\,}  % i.i.d. r.v.s
\newcommand{\simindep}{\,\stackrel{{\rm\tiny indep}}{\sim}\,} % indep r.v.s
\newcommand{\dist}{\,\stackrel{{\rm\tiny d}}{=\!=}\,}         % equality in distn

\def\approxd{\setbox0=\hbox{$\sim$}                           % approximately distributed as
\setbox1=\hbox to \wd0{\hss.\hss}%
\kern 4 pt\raise0.1ex\copy0\kern-\wd0\raise1.2ex%
\copy1\kern-\wd0\copy1\kern 4 pt}

\def\dperp{ \mathrel{\kern0pt\vbox{\hbox to 0.8em{\hss
\setbox0=\hbox{$\shortparallel$}\dp0=0pt\box0\hss}\hrule width 0.8em}}}

%\newcommand{\dist}{\,\stackrel{{\rm\tiny d}}{=}\,}
Some useful symbols presented as  bullet/numbered/lettered points using the \verb!itemize! environment \ldots
\begin{itemize}
\item $\simiid$; as in $X_1,\ldots,X_n \simiid N(\mu,\sigma^2)$.
\item [2.] $\simindep$; as in $X_i \simindep N(\mu_i,\sigma^2)$, for $i=1,\ldots,n$.
\item [(d)] $\dist$; as in $X_1 \dist X_2$, i.e. $X_1$ has the same distribution as $X_2$.
\item [(i)] $W \approxd \chi^2_p$, i.e. $W$ is approximately chi-squared with $p$ degrees of freedom.
\item $X_1 \dperp X_2$, i.e. $X_1$ is independent of $X_2$.
\end{itemize}
The \verb!enumerate! environment can be used to number items automatically using 1., 2., etc.

\subsection{Citing books, papers etc.}
\label{sec:refs}
Remember to read the guidelines on the STATG099 Moodle page.

\citet{Coles2001} is a good introduction to extreme value theory.
%citet when citation is part of a sentence

Many papers \citep{BCT2000} have also been written about exteme value theory.
% \citep when citation is in brackets.

\section{Conclusion}

\addcontentsline{toc}{section}{References} % to add references to table of contents
\bibliography{example}                     % read references from example.bib
\bibliographystyle{Chicago}                % file to determine the style of references

\end{document}

### 2019-07-25 MSc Project/He_chengling/run.R

@@ -1,0 +1,217 @@
+# ______multivariate normal  EFF(GW)/EFF(RW) VS. dimensions_______
+library(coda)
+library(mvtnorm)
+set.seed(8)
+
+# function
+## RW
+MN_RW_MwGibbs <- function(num,start,scale){
+  x.store <- matrix(NA,nrow=dim,ncol=num)
+  x.store[,1] <- start
+  x.old <- start
+  # judge whether dimension=1
+  if (dim == 1){
+    for(i in 2:num){
+      z <- scale*rnorm(1)
+      x1d <- x.old[1] + z
+      log_accept1d <- min(0,dnorm(x1d, mu, cov,log=T)-
+                            dnorm(x.old, mu, cov,log=T))
+      if (log(runif(1)) < log_accept1d){
+        x.store[,i] <- x1d
+        x.old <- x1d
+      }else {
+        x.store[,i] <- x.old
+      }
+    }
+  }else{
+    for (i in 2:num){
+      # update the first variable
+      z <- scale*rnorm(1)
+      x.new1 <- x.old[1] + z
+      mu.new1 <- mu[1] + cov[1,-1]%*%solve(cov[-1,-1])%*%
+        (x.store[-1,i-1] - mu[-1])
+      cov.new1 <- cov[1,1]-cov[1,-1]%*%solve(cov[-1,-1])%*%cov[-1,1]
+      log_accept1 <- min(0,dnorm(x.new1, mu.new1, cov.new1,log=T)-
+                           dnorm(x.old[1], mu.new1, cov.new1,log=T))
+      if (log(runif(1)) < log_accept1){
+        x.store[1,i] <- x.new1
+        x.old[1] <- x.new1
+      }else {
+        x.store[1,i] <- x.old[1]
+      }
+      # judge whether dimension=2
+      if (dim==2){
+        z <- scale*rnorm(1)
+        x.newd <- x.old[dim] + z
+        mu.newd <- mu[dim] + cov[dim,-dim]%*%solve(cov[-dim,-dim])%*%
+          (x.store[-dim,i] - mu[-dim])
+        cov.newd <- cov[dim,dim]-cov[dim,-dim]%*%solve(cov[-dim,-dim])%*%cov[-dim,dim]
+        log_acceptd <- min(0,dnorm(x.newd, mu.newd, cov.newd,log=T)-
+                             dnorm(x.old[dim], mu.newd, cov.newd,log=T))
[…]

### 2019-07-25 MSc Project/He_chengling/run2.R

@@ -1,0 +1,216 @@
+# ______multivariate normal  EFF(DBPS)/EFF(GW) VS. dimensions_______
+library(coda)
+library(mvtnorm)
+set.seed(8)
+
+## function
+# dbps
+mn_dbps <- function(num,start,scale){
+  x.store <- matrix(NA,nrow=dim,ncol=num)
+  x.store[,1] <- start
+  x.old <- start
+  # sample u which follows unifrom distribution on the unit d-sphere
+  v <- rnorm(dim)
+  u <- v/sqrt(sum(v^2))
+  # set the count of acceptance for the 1st stage 
+  count <- 0
+  if( dim==1 ){
+    for(i in 2:num){
+      z <- abs(scale*rnorm(dim)) # generate a vector of delta 
+      # first proposal
+      x_1p <- x.old + z*u
+      u.new1 <- -u
+      accep1 <- min(1,dnorm(x_1p,mean=mu,sd=sqrt(cov))/
+                      dnorm(x.old,mean=mu,sd=sqrt(cov)))
+      if (log(runif(1)) < log(accep1)){ # first judgement
+        x.store[,i] <- x_1p
+        x.old <- x_1p
+        u <- -u.new1 
+        count <- count+1 # acceptance rate for the 1st stage
+      }else{
+        # second proposal
+        nabla <- as.vector(-solve(cov)%*%(x_1p-mu))
+        nabla_hat <- nabla/sqrt(sum(nabla^2))
+        u.new2 <- 2*sum(u*nabla_hat)*nabla_hat - u # new u
+        x_2p <- x_1p - z*u.new2 # new x
+        alpha2 <- min(1,dnorm(x_1p,mean=mu,sd=sqrt(cov))/
+                        dnorm(x_2p,mean=mu,sd=sqrt(cov)))
+        pi.ratio <- dnorm(x_2p,mean=mu,sd=sqrt(cov))/
+          dnorm(x.old,mean=mu,sd=sqrt(cov))
+        accep2 <- min(1, (1-alpha2)/(1-accep1)*pi.ratio)
+        if (log(runif(1)) < log(accep2)){
+          x.store[,i] <- x_2p
+          x.old <- x_2p
+          u <- -u.new2
+        }else{
+          x.store[,i] <- x.old
+          u <- -u
+        }
+      }
+    }
+  }else{
+    for (i in 2:num){
[…]

### 2019-07-25 MSc Project/parallel scaled PLS for corn data.R

@@ -14,10 +14,10 @@ system.time({
     mp5data <-  apply(rawdata$mp5spec$data,2,scale)
     mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
     propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 10                                           #number of variables 
+    NV <- 8                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
+    DF <- data.frame(NIR = I(mp5data),                  #input data
+                     y=propvals[,3])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
     #str(DF)                                           #check point
     DF$train <- rep(FALSE, 80)

### 2019-08-02 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
test

\documentclass[a4paper,12pt,titlepage]{article} % [papersize,fontsize,add title page]{document type}

% This LaTeX file can be turned straight into a pdf by "PDFTeXify" in WinEdit, or
% by any LaTeX --> PDF command in another LaTeX editor
%
% Because figure files are PDF, LaTeX --> DVI does not work

% usepackage{.} reads in additional LaTeX packages
\usepackage[pdftex]{graphicx}       % to include graphs
\usepackage{natbib}                % A BibTeX style file for references.
\usepackage{amssymb,amsmath}        % for maths symbols and equation numbering
\usepackage{array,tabularx,calc}

\newenvironment{conditions}[1][where:]
{%
	#1\tabularx{\textwidth-\widthof{#1}}[t]{
		>{$}l<{$} @{${}={}$} X@{}
	}%
}
{\endtabularx\\[\belowdisplayskip]}

% set up title page
\title{The NIR Corn Data Set}
\author{Hongwei PENG \vspace{2cm} \\
	Supervisor : Prof Tom Fearn \vspace{2cm} \\
	Department of Statistical Science \\
	University College London}
\date{\today} % \today gives today's date. ... or put in the date you want

% set page size and margins
\setlength{\textwidth}{17cm}
\setlength{\textheight}{26cm}
\setlength{\oddsidemargin}{-0.5cm}
\setlength{\evensidemargin}{-0.5cm}
\setlength{\topmargin}{-25mm}
\setlength{\parindent}{0cm}
\setlength{\parskip}{0.3cm}

\let\leq=\leqslant   % for nice-looking inequality signs
\let\geq=\geqslant

\numberwithin{equation}{section}  % equation numbers like (section#.equation#)

\linespread{1}     % 1: single-spacing, 2: double-spacing, 1.5: 1.5-spacing etc

\begin{document}   % start of document
	\maketitle         % create title etc
	\tableofcontents   % create table of contents
	\newpage           % start a new page

	The most readily available high-dimensional NIR spectroscopic data is called corn data. There are many algorithms for analysing corn data in many publications. These algorithms will often claim that their new algorithm has a better performs. So the purpose of this dissertation is to search for as many different papers as possible, and write a critical overall to find the most efficient measure that can evaluate whether the model performs well and quantify the improvements mentioned in the paper.

	\section{Introduction}             % start a new section called `Introduction'
	\label{sec:intro}                  % create label for this section

	\section{Literature reviews}
	\label{sec:liter}

	\section{Datasets}
	\label{sec:data}

	\section{Methodology}
	\label{sec:method}

	\subsection{Model Evaluation}
	\label{sec:eva}
	According to the corn data literature, there are several measures that can be used to evaluate the performance of the model.

	1, Root Mean Square Error for Calibration samples (RMSEC) is proposed by \citet{2yun2014strategy}.

	2, RMSECV is mentioned by many papers \citep{8ji2015using}. And there are two cross-validation methods. One is leave one out cross-validation (LOOCV), mentioned by \citet{6zheng2015pretreating}. The other is K-fold cross-validation, there are the 3-fold cross-validation \citep{3galvao2007cross}, 10-fold cross-validation \citep{8ji2015using} and so on. The calculation method of RMSECV is as follows:
	\begin{equation}
		RMSECV=\sqrt{\frac{1}{n}\sum_{i=1}^{n} (y_i-\hat y_i)^2} 
	\end{equation}
	\begin{conditions}
		n     &  the number of samples\\
		y_i     &   the experimental value of the i-th sample\\   
		\hat y_i &  the predicted value of the i-th sample by cross-validation which  includes removing the set of i-th sample from the calibration set, building a model with the remaining samples, and applying the model to i-th sample
	\end{conditions}

	3, The Root Mean Square Error of Prediction (RMSEP) is mentioned by \citet{1su2006partial}. This is a generally accepted method of evaluating models. This approach requires the determination of appropriate cross-validation sets and prediction sets before building PLS model. For example, 60 samples of corn data are used for a cross-validation and the remaining 20 samples are used as predictions \citep{1su2006partial}. Then the cross-validation data is used for modelling, determining the parameters for regression model, such as PLS. After that, the model is applied to the predictive data to calculate the Root Mean Square Error of Prediction (RMSEP). The RMSEP calculation formula is:

	\begin{equation}
RMSEP=\sqrt{\frac{1}{m}\sum_{i=1}^{m} (y_i-\hat y_i)^2}
	\end{equation}

	\begin{conditions}
		m     &  the number of prediction sets\\
		y_i     &  the experimental value of the i-th sample in the prediction set \\   
		\hat y_i &  the prediction value of model for the i-th sample
	\end{conditions}

	4, There are few papers mentioned that $R^2$ is used to measure the model \citep{tatavarti2005assessment}. But this method is also flawed. In some situations, not enough calculation accuracy of the computer will cause the value of $R^2$ to be equal to 1. For example, \citet{deng2016bootstrapping} has this problem and the $R^2$ in PLS model fitting  moisture is equl to 0.9959, but for the CARS, GA-PLS and BOSS model, $R^2$ are all equal to $1.0000 \pm 0.0000$. Hence we can see it hard to distinguish the different between models. So this will not be a good indicator of evaluation.

	\subsection{Pre-treatment}
	\label{sec:treat}
	The papers use different pre-treatments of the data, and the results of the model will be very different. For example, 7th paper and 8th paper also use M5 to predict the first constituent, and the results are very different. Through the different literatures, the common pretreatment of corn data has the following four types:

	1. Nothing to deal with, such as 1st paper.

	2. Scale the data, such as 4th paper.

	3. SavitzkyGolay filter processing on the data, such as 3rd paper.

	4. Delete the outliers, such as 8th paper.

	\subsection{Sample splitting}
	\label{splitting}
	The number of samples selected and the method of sample selection will also have an impact on the results of models. The methods of selecting samples are as follows:

	1. A completely random sample \citep{1su2006partial}.

	2. Choosing the samples by the SPXY method \citep{3galvao2007cross}.

	3. Use the Kennard-Stone (K-S) algorithm, such as 8th paper  in the third form.

	4. Directly divide the raw data into the first half and the second half, the first half is cross-validation sets, and the second half is prediction set. For example 4th paper.

	The second and third methods will result in the prediction level data being very close to the data of the cross-check set, which may increase the accuracy of the prediction and reduce the prediction difficulty, so these two methods are not used here. Because in the actual problem, the performance of the algorithm looks better when the two sample sets are too similar, which is not what we want. The last method relies on the sorting of the original data, so the next step is to take a random sampling method to simulate the sample. The selection of the quantity refers to the 5th and 6th documents, so the sample size of 20~70 will be selected to build the model, and the rest will be predicted.

	\subsection{Cross-validation}
	\label{cross-validation}

	\subsection{PLS algorithm}
	\label{PLS_al}

	\subsection{Parallel computing}
	\label{parallel}

	\subsection{Myriad}
	\label{myriad}

	\section{Result and discussion}
	\label{sec:result}

	\subsection{Loop times}

	\subsection{Number of Samples}

	\subsection{Number of Components}

	\subsection{Pre-treatment}

	\subsection{Cross-Validation}

	\subsection{Compare with papers}

	\section{Conclusions}
	\label{sec:conclution}

	\section{Conclusion}

	\addcontentsline{toc}{section}{References} % to add references to table of contents
	\bibliography{hongwei_pls_MSc}                     % read references from example.bib
	\bibliographystyle{chicago}            % file to determine the style of references

\end{document}

### 2019-08-11 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
latex change methodology

@@
 The calculation method of RMSECV is as follows:
+
 	\begin{equation}
@@
 	The papers use different pre-treatments of the data, and the results of the model will be very different.
-For example, 7th paper and 8th paper also use M5 to predict the first constituent, and the results are very different.
+For example, \citet{7galvao2008variable} and \citet{8ji2015using} both use M5 to predict the first constituent, and the results are very different.
 Through the different literatures, the common pretreatment of corn data has the following four types:
 
-	1. Nothing to deal with, such as 1st paper.
+	1. Nothing to deal with \citep{1su2006partial}.
 
-	2. Scale the data, such as 4th paper.
+	2. Scale the data \citep{4ergon2006reduced}.
 
-	3. SavitzkyGolay filter processing on the data, such as 3rd paper.
+	3. SavitzkyGolay filter processing on the data \citep{3galvao2007cross}.
 
-	4. Delete the outliers, such as 8th paper.
+	4. Delete the outliers \citep{8ji2015using}.
 
@@
 
-	2. Choosing the samples by the SPXY method \citep{3galvao2007cross}.
+	2. Choosing the samples by SPXY method \citep{3galvao2007cross}.
 
-	3. Use the Kennard-Stone (K-S) algorithm, such as 8th paper  in the third form.
+	3. Use the Kennard-Stone (K-S) algorithm \citep{zhao2015optimization}.
 
-	4. Directly divide the raw data into the first half and the second half, the first half is cross-validation sets, and the second half is prediction set. For example 4th paper.
+	4. Directly divide the raw data into the first half and the second half, the first half is cross-validation sets, and the second half is prediction set \citep{4ergon2006reduced}.
 
-	The second and third methods will result in the prediction level data being very close to the data of the cross-check set, which may increase the accuracy of the prediction and reduce the prediction difficulty, so these two methods are not used here.
+	The second and third methods will result in the prediction level data being very close to the data of the cross-validation set, which may increase the accuracy of the prediction and reduce the prediction difficulty, so these two methods are not used here.
 Because in the actual problem, the performance of the algorithm looks better when the two sample sets are too similar, which is not what we want.
 The last method relies on the sorting of the original data, so the next step is to take a random sampling method to simulate the sample.
-The selection of the quantity refers to the 5th and 6th documents, so the sample size of 20~70 will be selected to build the model, and the rest will be predicted.
+The selection of samples refers to \citet{5zheng2012stability} and \citet{6zheng2015pretreating}, so the sample size of 20 $\sim$ 70 will be selected as calibration to build the model, and the rest will selected as prediction.
 
@@
 	\label{cross-validation}
+	The cross-validation is to divide the data into n groups.
+One of group is selected as the prediction set, and the remaining n-1 groups are used as the training set, and testing n times.
+Finally, the average of results of all tests was taken as the cross-validation result.
+If the selected n is the same as the size of sample, then this method is called leave one out method (LOO), otherwise it is called the k-fold cross-validation.
+Cross-validation not only improves the reliability of models, but also allows the model to avoid falling into local optimal solutions.
+Figure \ref{fig:cross-validation} shows the flow of the cross-validation.
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=8.5cm, angle=0]{cross-validation.png}  % width changes size
+	    \vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The flow of the cross-validation}          % a meaningful caption
+		\label{fig:cross-validation}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	The choice between LOO and k-fold cross-validation is determined according to the number of samples.
+When the sample size is small, the LOO is preferred.
+When the sample size is too large, the k-fold cross-test is preferred.
+There is an additional reminder here that the difference between LOO and the k-fold cross-validation is not just a difference in computing time.
+More, when the sample size is too large, LOO may cause over-fitting problems, and the k-fold cross-validation can not only save computational power, but also avoid the over-fitting problem in here.
+Chapter \ref{sec:Cross-Validation} will discuss the difference.
 
@@
 	\label{PLS_al}
+	The partial least squares regression (PLS) is a multi-regression technique proposed by \citet{wold1984collinearity}, and it is also the most common statistical method in the research of near-infrared spectroscopy.
+Partial least squares regression is similar to principal components analysis (PCA) and is also a factor analysis method.
+In the modelling  process, it is first necessary to decompose the matrix of spectrum and then extract a few principal components (these variables are called latent variables in PLS) to represent most of the information of original spectrum.
+Because the spectral data is high-dimensional, the number of independent variables is more than the number of samples, thus it cannot meet the basic assumption of least squares method.
+Therefore, it is necessary to extracting the data to some components, and then make the regression.
+Compared with PCA, PLS not only considers the dimensionality reduction of the independent variables, but also maximizes the covariance between the components and target variables.
+In this way, the covariance between the extracted components and the target vector will be the maximum.
+From this point, PLS is the improvement and further development of PCA, and the results in many applications also prove that PLS has better performance than PCA.
+
+	The process of partial least squares regression is as follows:
+
+	The PLS model needs to perform principal component decomposition on the spectral data matrix and the target vector when it is established.
+
+	\begin{equation}
+	X=TP^T+E 
+	\end{equation}
+	\begin{equation}
+	Y=UQ^T+F
+	\end{equation}
+	Where T and P are the scoring matrix and the load matrix of the spectral matrix X, respectively.
+U and Q are the scoring matrix and the load matrix of the detection target vector Y, respectively.
+E and F are residual matrices of the spectral matrix X and the detection target vector Y, respectively, and T and U can perform linear regression as follows:
 
@@
 
-	\subsection{Myriad}
+	\subsection{High performance computing system}
 	\label{myriad}
@@
 	\subsection{Loop times}
-
+	\label{sec:Loop times}
 	\subsection{Number of Samples}
-
+	\label{sec:Number of Samples}
 	\subsection{Number of Components}
-
+	\label{sec:Number of Components}
 	\subsection{Pre-treatment}
-
+	\label{sec:Pre-treatment}
 	\subsection{Cross-Validation}
-
+	\label{sec:Cross-Validation}
 	\subsection{Compare with papers}
-
+	\label{sec:Compare with papers}
 	\section{Conclusions}

### 2019-08-15 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
dissertation add papers table

@@
 \usepackage{array,tabularx,calc}
+\usepackage{multirow} % create the tables
+\usepackage{lscape} %put table lscape
+\usepackage{pdflscape} %put pages lscape
 
@@
 E and F are residual matrices of the spectral matrix X and the detection target vector Y, respectively, and T and U can perform linear regression as follows:
+	......
 
@@
 	\label{sec:Loop times}
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=15.5cm, angle=0]{no_loop_time500.pdf}  % width changes size
+		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{RMSECV and RMSEP under different loop times}          % a meaningful caption
+		\label{fig:looptimes}               % label for the figure
+	\end{figure}                        % end of figure environment
+
 	\subsection{Number of Samples}
 	\label{sec:Number of Samples}
+
 	\subsection{Number of Components}
 	\label{sec:Number of Components}
+
 	\subsection{Pre-treatment}
 	\label{sec:Pre-treatment}
+
 	\subsection{Cross-Validation}
 	\label{sec:Cross-Validation}
+
 	\subsection{Compare with papers}
 	\label{sec:Compare with papers}
+
+	\begin{landscape}
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllll}
+		\hline
+		\multirow{2}{*}{Paper} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{Pre-treatment}                                           & \multicolumn{2}{c}{Moisture}    & \multicolumn{2}{c}{Oil}         & \multicolumn{2}{c}{Protein}   & \multicolumn{2}{c}{Starch}    \\ \cline{5-12}
+		&                                                                     &                                                                            &                                                                          & RMSECV         & RMSEP          & RMSECV         & RMSEP          & RMSECV        & RMSEP         & RMSECV        & RMSEP         \\ \hline
+		1                      & mp6                                                                 & 60                                                                         & None                                                                     &                & 0.1446034(10)  &                & 0.09225961(10) &               & 0.1400926(10) &               & 0.3436289(10) \\
+		2                      & m5                                                                  & 64 5-fold                                                                  & None                                                                     & 0.01488358(10) & 0.02113168(10) &                &                &               &               &               &               \\
+		3                      & m5                                                                  & 60                                                                         & SavitzkyGolay                                                            &                & 0.05628462(5)  &                & 0.03163213(12) &               & 0.1085697(6)  &               & 0.2371506(6)  \\
+		4                      & m5                                                                  & 40                                                                         & Scale                                                                    &                & 0.05862355(12) &                & 0.3891674(14)  &               & 0.3554446(8)  &               & 0.3878001(9)  \\
+		4                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4194983(12)  &                & 0.7190886(17)  &               & 0.3731878(8)  &               & 0.4980389(9)  \\
+		5                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4023674(10)  &                &                &               &               &               &               \\
+		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  &                &                & 0.08331678(7)  & 0.07401861(7)  &               &               & 0.3322749(7)  & 0.2890035(7)  \\
+		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  &                &                & 0.06403154(7)  & 0.05660701(7)  &               &               & 0.2426438(7)  & 0.2287837(7)  \\
+		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} &                &                & 0.04751603(7)  & 0.03468245(7)  &               &               & 0.3216974(7)  & 0.3037632(7)  \\
+		7                      & m5                                                                  & 60                                                                         & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} &                & 0.04043771(6)  &                & 0.04937681(10) &               & 0.1021954(7)  &               & 0.2630782(5)  \\
+		8                      & m5                                                                  & 52                                                                         & Delete 75 , 77                                                           & 0.02177367(10) & 0.0197695(10)  & 0.06621319(10) & 0.05955603(10) & 0.1194857(10) & 0.1123115(10) & 0.2937006(10) & 0.2723313(10)
+	\end{tabular}
+\end{table}
+\end{landscape}
+
+	\begin{landscape}
+\begin{table}[]
+	\begin{tabular}{lllllllll}
+		\hline
+		Paper & \begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & Pre-treatment                                                            & \begin{tabular}[c]{@{}l@{}}RMSECV/\\ RMSEP\end{tabular} & Moisture       & Oil            & Protein       & Starch        \\ \hline
+		1     & mp6                                                & 60                                                        & None                                                                     & RMSEP                                                   & 0.1446034(10)  & 0.09225961(10) & 0.1400926(10) & 0.3436289(10) \\
+		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSECV                                                  & 0.01488358(10) &                &               &               \\
+		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSEP                                                   & 0.02113168(10) &                &               &               \\
+		3     & m5                                                 & 60                                                        & SavitzkyGolay                                                            & RMSEP                                                   & 0.05628462(5)  & 0.03163213(12) & 0.1085697(6)  & 0.2371506(6)  \\
+		4     & m5                                                 & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.05862355(12) & 0.3891674(14)  & 0.3554446(8)  & 0.3878001(9)  \\
+		4     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4194983(12)  & 0.7190886(17)  & 0.3731878(8)  & 0.4980389(9)  \\
+		5     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4023674(10)  &                &               &               \\
+		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSECV                                                  &                & 0.08331678(7)  &               & 0.3322749(7)  \\
+		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSEP                                                   &                & 0.07401861(7)  &               & 0.2890035(7)  \\
+		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSECV                                                  &                & 0.06403154(7)  &               & 0.2426438(7)  \\
+		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSEP                                                   &                & 0.05660701(7)  &               & 0.2287837(7)  \\
+		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} & RMSECV                                                  &                & 0.04751603(7)  &               & 0.3216974(7)  \\
+		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(2,2,13)\end{tabular}  & RMSEP                                                   &                & 0.03468245(7)  &               & 0.3037632(7)  \\
+		7     & m5                                                 & 60                                                        & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} & RMSECV                                                  & 0.04043771(6)  & 0.04937681(10) & 0.1021954(7)  & 0.2630782(5)  \\
+		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSECV                                                  & 0.02177367(10) & 0.06621319(10) & 0.1194857(10) & 0.2937006(10) \\
+		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSEP                                                   & 0.0197695(10)  & 0.05955603(10) & 0.1123115(10) & 0.2723313(10)
+	\end{tabular}
+\end{table}
+\end{landscape}
+
 	\section{Conclusions}
 	\label{sec:conclution}
-
-	\section{Conclusion}
 

### 2019-08-20 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
add tables!

--- 2019-08-11 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
@@
 	\label{sec:Loop times}
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=15.5cm, angle=0]{no_loop_time500.pdf}  % width changes size
+		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{RMSECV and RMSEP under different loop times}          % a meaningful caption
+		\label{fig:looptimes}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=8.5cm, angle=0]{Number_of_loop_times_mp5-1.pdf}  % width changes size
+	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{SD under different loop times}          % a meaningful caption
+	\label{fig:looptimes}               % label for the figure
+\end{figure}                        % end of figure environment
+
 	\subsection{Number of Samples}
 	\label{sec:Number of Samples}
+
 	\subsection{Number of Components}
 	\label{sec:Number of Components}
+
 	\subsection{Pre-treatment}
 	\label{sec:Pre-treatment}
+
 	\subsection{Cross-Validation}
 	\label{sec:Cross-Validation}
+
 	\subsection{Compare with papers}
 	\label{sec:Compare with papers}
+
+	\begin{landscape}
+
+\begin{table}[]
+	\begin{tabular}{lll}
+		\hline
+		Number & Paper's title & Publication date \\ \hline
+		1 & A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples & 2007 \\
+		2 & A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration & 2014 \\
+		3 & Reduced PCR/PLSR models by subspace projections & 2006 \\
+		4 & Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra & 2012 \\
+		5 & Cross-validation for the selection of spectral variables using the successive projections algorithm & 2007 \\
+		6 & A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm & 2008 \\
+		7 & Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD) & 2015 \\
+		8 & Using consensus interval partial least square in near infrared spectra analysis & 2015
+	\end{tabular}
+
+\label{tab:papers}
+\end{table}
+
+Table \ref{tab:moisture} is the regression for moisture.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Moisture} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.148(0.0213) &  & 0.159 &  & 0.139 &  &  &  \\
+		2 & m5 & None & 64(5-fold) & 10 & 0.0152(0.000739) & 0.0202(0.00319) & 0.0149 & 0.0201 & 0.00026 & 0.00035 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 12 &  & 0.0231(0.00443) &  & 0.3506 &  & 0.3485 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 12 &  & 0.159(0.0178) &  & 0.3506 &  & 0.3485 &  &  &  \\
+		4 & mp5 & Scale & 40(LOO) & 10 &  & 0.405(0.0467) &  & 0.357 &  & 0.265 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 5 &  & 0.0547(0.00942) &  & 0.040 &  & 0.012 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 6 &  & 0.0396(0.00625) &  & 0.045 &  & 0.019 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0221(0.0018) & 0.0194(0.00298) & 0.0124 & 0.0157 & 0.0047 & 0.0056 &  &  & 
+	\end{tabular}
+
+\caption{regression of moisture}
+\label{tab:moisture}
+\end{table}
+
+Table \ref{tab:oil} is the regression for Oil.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Oil} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.0991(0.0161) &  & 0.107 &  & 0.0948 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 14 &  & 0.396(0.0665) &  & 0.6912 &  & 0.6902 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 14 &  & 0.694(0.095) &  & 0.6912 &  & 0.6902 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 12 &  & 0.0329(0.00672) &  & 0.029 &  & 0.022 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 10 &  & 0.0505(0.0103) &  & 0.028 &  & 0.030 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) & 7 & 0.0827(0.00419) & 0.0716(0.0116) & 0.0729 & 0.0855 & 0.0363 & 0.0400 &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) & 7 & 0.0639(0.00357) & 0.0548(0.012) & 0.0577 & 0.0682 & 0.0363 & 0.0400 &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) & 7 & 0.0480(0.00312) & 0.0368 (0.0088) & 0.0370 & 0.0397 & 0.0363 & 0.0400 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0651(0.00662) & 0.0604(0.00876) & 0.0613 & 0.0673 & 0.0483 & 0.0546 &  &  & 
+	\end{tabular}
+
+\caption{regression of oil}
+\label{tab:oil}
+\end{table}
+    \end{landscape}
+
+	\begin{landscape}
+Table \ref{tab:protein} is the regression for protein.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Protein} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.141(0.0203) &  & 0.150 &  & 0.145 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 8 &  & 0.349(0.051) &  & 0.4466 &  & 0.4349 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 8 &  & 0.37(0.0485) &  & 0.4466 &  & 0.4349 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.107(0.0195) &  & 0.119 &  & 0.040 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 7 &  & 0.102(0.0186) &  & 0.110 &  & 0.033 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 13 & 0.119(0.0155) & 0.11(0.0169) & 0.1080 & 0.1353 & 0.0429 & 0.0846 &  &  & 
+	\end{tabular}
+\caption{regression of protein}
+\label{tab:protein}
+\end{table}
+
+Table \ref{tab:starch} is the regression for starch.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Starch} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.35(0.056) &  & 0.370 &  & 0.358 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 9 &  & 0.393(0.0736) &  & 0.5010 &  & 0.4443 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 9 &  & 0.513(0.0779) &  & 0.5010 &  & 0.4443 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.239(0.0449) &  & 0.196 &  & 0.100 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 5 &  & 0.258(0.0453) &  & 0.228 &  & 0.101 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) & 8 & 0.333(0.0226) & 0.283(0.0624) & 0.312 & 0.214 & 0.240 & 0.219 &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) & 8 & 0.2412(0.0171) & 0.221(0.049) & 0.248 & 0.221 & 0.240 & 0.219 &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) & 8 & 0.318(0.0252) & 0.302(0.061) & 0.347 & 0.228 & 0.240 & 0.219 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.292(0.0312) & 0.282(0.043) & 0.2579 & 0.2356 & 0.1137 & 0.1188 &  &  & 
+	\end{tabular}
+\caption{regression of starch}
+\label{tab:starch}
+\end{table}
+    \end{landscape}
+
 	\section{Conclusions}
 	\label{sec:conclution}
-
-	\section{Conclusion}
 

### 2019-08-20 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
after final tables

--- 2019-08-11 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
@@
 	\label{sec:Loop times}
-	\subsection{Number of Samples}
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=15.5cm, angle=0]{no_loop_time500.pdf}  % width changes size
+		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{RMSECV and RMSEP under different loop times}          % a meaningful caption
+		\label{fig:looptimes}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=8.5cm, angle=0]{Number_of_loop_times_mp5-1.pdf}  % width changes size
+	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{SD under different loop times}          % a meaningful caption
+	\label{fig:looptimes}               % label for the figure
+\end{figure}                        % end of figure environment
+
+	\subsection{Number of samples}
 	\label{sec:Number of Samples}
-	\subsection{Number of Components}
+
+	\subsection{Number of components}
 	\label{sec:Number of Components}
+
 	\subsection{Pre-treatment}
 	\label{sec:Pre-treatment}
-	\subsection{Cross-Validation}
+
+	\subsection{Cross-validation}
 	\label{sec:Cross-Validation}
+
 	\subsection{Compare with papers}
 	\label{sec:Compare with papers}
+
+	\begin{landscape}
+
+\begin{table}[]
+	\begin{tabular}{ll}
+		\hline
+		Number & Paper's title \\ \hline
+		1 & A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples \\
+		2 & A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration \\
+		3 & Reduced PCR/PLSR models by subspace projections \\
+		4 & Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra \\
+		5 & Cross-validation for the selection of spectral variables using the successive projections algorithm \\
+		6 & A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm \\
+		7 & Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD) \\
+		8 & Using consensus interval partial least square in near infrared spectra analysis
+	\end{tabular}
+
+\label{tab:papers}
+\end{table}
+
+    \end{landscape}
+
+\begin{landscape}
+
+Table \ref{tab:moisture} is the regression for moisture.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ components\end{tabular}} & \multicolumn{2}{c}{Moisture} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.148(0.0213) &  & 0.159 &  & 0.139 &  &  &  \\
+		2 & m5 & None & 64(5-fold) & 10 & 0.0152(0.000739) & 0.0202(0.00319) & 0.0149 & 0.0201 & 0.00026 & 0.00035 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 12 &  & 0.0231(0.00443) &  & 0.3506 &  & 0.3485 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 12 &  & 0.159(0.0178) &  & 0.3506 &  & 0.3485 &  &  &  \\
+		4 & mp5 & Scale & 40(LOO) & 10 &  & 0.405(0.0467) &  & 0.357 &  & 0.265 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 5 &  & 0.0547(0.00942) &  & 0.040 &  & 0.012 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 6 &  & 0.0396(0.00625) &  & 0.045 &  & 0.019 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0221(0.0018) & 0.0194(0.00298) & 0.0124 & 0.0157 & 0.0047 & 0.0056 &  &  & 
+	\end{tabular}
+
+\caption{regression of moisture.The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:moisture}
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllllll}
+		\cline{1-13}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Moisture} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.148(0.0213) &  &  & 0.159 &  &  & 0.139 &  &  &  \\
+		2 & m5 & None & 64(5-fold) & 10 & 0.0152(0.000739) & 0.0202(0.00319) &  & 0.0149 & 0.0201 &  & 0.00026 & 0.00035 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 12 &  & 0.0231(0.00443) &  &  & 0.3506 &  &  & 0.3485 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 12 &  & 0.159(0.0178) &  &  & 0.3506 &  &  & 0.3485 &  &  &  \\
+		4 & mp5 & Scale & 40(LOO) & 10 &  & 0.405(0.0467) &  &  & 0.357 &  &  & 0.265 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 5 &  & 0.0547(0.00942) &  &  & 0.040 &  &  & 0.012 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 6 &  & 0.0396(0.00625) &  &  & 0.045 &  &  & 0.019 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) &  &  &  &  &  &  &  &  &  &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) &  &  &  &  &  &  &  &  &  &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) &  &  &  &  &  &  &  &  &  &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0221(0.0018) & 0.0194(0.00298) &  & 0.0124 & 0.0157 &  & 0.0047 & 0.0056 &  &  & 
+	\end{tabular}
+\end{table}
+
+    \end{landscape}
+
+\begin{landscape}
+
+Table \ref{tab:oil} is the regression for Oil.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ components\end{tabular}} & \multicolumn{2}{c}{Oil} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.0991(0.0161) &  & 0.107 &  & 0.0948 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 14 &  & 0.396(0.0665) &  & 0.6912 &  & 0.6902 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 14 &  & 0.694(0.095) &  & 0.6912 &  & 0.6902 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 12 &  & 0.0329(0.00672) &  & 0.029 &  & 0.022 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 10 &  & 0.0505(0.0103) &  & 0.028 &  & 0.030 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) & 7 & 0.0827(0.00419) & 0.0716(0.0116) & 0.0729 & 0.0855 & 0.0363 & 0.0400 &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) & 7 & 0.0639(0.00357) & 0.0548(0.012) & 0.0577 & 0.0682 & 0.0363 & 0.0400 &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) & 7 & 0.0480(0.00312) & 0.0368 (0.0088) & 0.0370 & 0.0397 & 0.0363 & 0.0400 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0651(0.00662) & 0.0604(0.00876) & 0.0613 & 0.0673 & 0.0483 & 0.0546 &  &  & 
+	\end{tabular}
+
+\caption{regression of oil. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:oil}
+\end{table}
+    \end{landscape}
+
+	\begin{landscape}
+Table \ref{tab:protein} is the regression for protein.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ components\end{tabular}} & \multicolumn{2}{c}{Protein} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.141(0.0203) &  & 0.150 &  & 0.145 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 8 &  & 0.349(0.051) &  & 0.4466 &  & 0.4349 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 8 &  & 0.37(0.0485) &  & 0.4466 &  & 0.4349 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.107(0.0195) &  & 0.119 &  & 0.040 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 7 &  & 0.102(0.0186) &  & 0.110 &  & 0.033 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 13 & 0.119(0.0155) & 0.11(0.0169) & 0.1080 & 0.1353 & 0.0429 & 0.0846 &  &  & 
+	\end{tabular}
+\caption{regression of protein. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:protein}
+\end{table}
+
+    \end{landscape}
+
+\begin{landscape}
+Table \ref{tab:starch} is the regression for starch.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllll}
+		\cline{1-11}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ components\end{tabular}} & \multicolumn{2}{c}{Starch} & \multicolumn{2}{c}{PLS in papers} & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-11}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP & RMSECV & RMSEP & RMSECV & RMSEP &  &  &  \\ \cline{1-11}
+%		1 & mp6 & None & 60(LOO) & 10 &  & 0.35(0.056) &  & 0.370 &  & 0.358 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 9 &  & 0.393(0.0736) &  & 0.5010 &  & 0.4443 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 9 &  & 0.513(0.0779) &  & 0.5010 &  & 0.4443 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.239(0.0449) &  & 0.196 &  & 0.100 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 5 &  & 0.258(0.0453) &  & 0.228 &  & 0.101 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) & 8 & 0.333(0.0226) & 0.283(0.0624) & 0.312 & 0.214 & 0.240 & 0.219 &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) & 8 & 0.2412(0.0171) & 0.221(0.049) & 0.248 & 0.221 & 0.240 & 0.219 &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) & 8 & 0.318(0.0252) & 0.302(0.061) & 0.347 & 0.228 & 0.240 & 0.219 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.292(0.0312) & 0.282(0.043) & 0.2579 & 0.2356 & 0.1137 & 0.1188 &  &  & 
+	\end{tabular}
+\caption{regression of starch. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:starch}
+\end{table}
+    \end{landscape}
+
+	\subsection{Developed method significant test}
+\label{sec: test}
+
 	\section{Conclusions}
 	\label{sec:conclution}
-
-	\section{Conclusion}
 

### 2019-08-20 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
fix the table

--- 2019-08-15 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
@@
 
-	\subsection{Number of Samples}
+	\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=8.5cm, angle=0]{Number_of_loop_times_mp5-1.pdf}  % width changes size
+	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{SD under different loop times}          % a meaningful caption
+	\label{fig:looptimes}               % label for the figure
+\end{figure}                        % end of figure environment
+
+	\subsection{Number of samples}
 	\label{sec:Number of Samples}
 
-	\subsection{Number of Components}
+	\subsection{Number of components}
 	\label{sec:Number of Components}
@@
 
-	\subsection{Cross-Validation}
+	\subsection{Cross-validation}
 	\label{sec:Cross-Validation}
@@
 	\begin{landscape}
+
+\begin{table}[]
+	\begin{tabular}{ll}
+		\hline
+		Number & Paper's title \\ \hline
+		1 & A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples \\
+		2 & A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration \\
+		3 & Reduced PCR/PLSR models by subspace projections \\
+		4 & Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra \\
+		5 & Cross-validation for the selection of spectral variables using the successive projections algorithm \\
+		6 & A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm \\
+		7 & Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD) \\
+		8 & Using consensus interval partial least square in near infrared spectra analysis
+	\end{tabular}
+
+\label{tab:papers}
+\end{table}
+
+    \end{landscape}
+
+\begin{landscape}
+
+Table \ref{tab:moisture} is the regression for moisture.
 % Please add the following required packages to your document preamble:
@@
 \begin{table}[]
-	\begin{tabular}{llllllllllll}
-		\hline
-		\multirow{2}{*}{Paper} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{Pre-treatment}                                           & \multicolumn{2}{c}{Moisture}    & \multicolumn{2}{c}{Oil}         & \multicolumn{2}{c}{Protein}   & \multicolumn{2}{c}{Starch}    \\ \cline{5-12}
-		&                                                                     &                                                                            &                                                                          & RMSECV         & RMSEP          & RMSECV         & RMSEP          & RMSECV        & RMSEP         & RMSECV        & RMSEP         \\ \hline
-		1                      & mp6                                                                 & 60                                                                         & None                                                                     &                & 0.1446034(10)  &                & 0.09225961(10) &               & 0.1400926(10) &               & 0.3436289(10) \\
-		2                      & m5                                                                  & 64 5-fold                                                                  & None                                                                     & 0.01488358(10) & 0.02113168(10) &                &                &               &               &               &               \\
-		3                      & m5                                                                  & 60                                                                         & SavitzkyGolay                                                            &                & 0.05628462(5)  &                & 0.03163213(12) &               & 0.1085697(6)  &               & 0.2371506(6)  \\
-		4                      & m5                                                                  & 40                                                                         & Scale                                                                    &                & 0.05862355(12) &                & 0.3891674(14)  &               & 0.3554446(8)  &               & 0.3878001(9)  \\
-		4                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4194983(12)  &                & 0.7190886(17)  &               & 0.3731878(8)  &               & 0.4980389(9)  \\
-		5                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4023674(10)  &                &                &               &               &               &               \\
-		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  &                &                & 0.08331678(7)  & 0.07401861(7)  &               &               & 0.3322749(7)  & 0.2890035(7)  \\
-		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  &                &                & 0.06403154(7)  & 0.05660701(7)  &               &               & 0.2426438(7)  & 0.2287837(7)  \\
-		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} &                &                & 0.04751603(7)  & 0.03468245(7)  &               &               & 0.3216974(7)  & 0.3037632(7)  \\
-		7                      & m5                                                                  & 60                                                                         & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} &                & 0.04043771(6)  &                & 0.04937681(10) &               & 0.1021954(7)  &               & 0.2630782(5)  \\
-		8                      & m5                                                                  & 52                                                                         & Delete 75 , 77                                                           & 0.02177367(10) & 0.0197695(10)  & 0.06621319(10) & 0.05955603(10) & 0.1194857(10) & 0.1123115(10) & 0.2937006(10) & 0.2723313(10)
+	\begin{tabular}{llllllllllllllll}
+	\cline{1-13}
+	\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Moisture} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
+	\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
+	1 & mp6 & None & 60(LOO) & 10 &  & 0.148(0.0213) &  &  & 0.159 &  &  & 0.139 &  &  &  \\
+	2 & m5 & None & 64(5-fold) & 10 & 0.0152(0.000739) & 0.0202(0.00319) &  & 0.0149 & 0.0201 &  & 0.00026 & 0.00035 &  &  &  \\
+	3 & m5 & Scale & 40(LOO) & 12 &  & 0.0231(0.00443) &  &  & 0.3506 &  &  & 0.3485 &  &  &  \\
+	3 & mp5 & Scale & 40(LOO) & 12 &  & 0.159(0.0178) &  &  & 0.3506 &  &  & 0.3485 &  &  &  \\
+	4 & mp5 & Scale & 40(LOO) & 10 &  & 0.405(0.0467) &  &  & 0.357 &  &  & 0.265 &  &  &  \\
+	5 & m5 & SG(1,2,13) & 60(3-fold) & 5 &  & 0.0547(0.00942) &  &  & 0.040 &  &  & 0.012 &  &  &  \\
+	6 & m5 & SG(1,2,21) & 60(LOO) & 6 &  & 0.0396(0.00625) &  &  & 0.045 &  &  & 0.019 &  &  &  \\
+	8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0221(0.0018) & 0.0194(0.00298) &  & 0.0124 & 0.0157 &  & 0.0047 & 0.0056 &  &  & 
 \end{tabular}
+
+\caption{regression of moisture.The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:moisture}
+\end{table}
+
+    \end{landscape}
+
+\begin{landscape}
+
+Table \ref{tab:oil} is the regression for Oil.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+
+	\begin{tabular}{llllllllllllllll}
+		\cline{1-13}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Oil} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.0991(0.0161) &  &  & 0.107 &  &  & 0.0948 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 14 &  & 0.396(0.0665) &  &  & 0.6912 &  &  & 0.6902 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 14 &  & 0.694(0.095) &  &  & 0.6912 &  &  & 0.6902 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 12 &  & 0.0329(0.00672) &  &  & 0.029 &  &  & 0.022 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 10 &  & 0.0505(0.0103) &  &  & 0.028 &  &  & 0.030 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) & 7 & 0.0827(0.00419) & 0.0716(0.0116) &  & 0.0729 & 0.0855 &  &  & 0.0400 &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) & 7 & 0.0639(0.00357) & 0.0548(0.012) &  & 0.0577 & 0.0682 &  & 0.0363 & 0.0400 &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) & 7 & 0.0480(0.00312) & 0.0368 (0.0088) &  & 0.0370 & 0.0397 &  & 0.0363 & 0.0400 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0651(0.00662) & 0.0604(0.00876) &  & 0.0613 & 0.0673 &  & 0.0483 & 0.0546 &  &  & 
+	\end{tabular}
+
+\caption{regression of oil. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:oil}
 \end{table}
@@
 	\begin{landscape}
+Table \ref{tab:protein} is the regression for protein.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
 \begin{table}[]
-	\begin{tabular}{lllllllll}
-		\hline
-		Paper & \begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & Pre-treatment                                                            & \begin{tabular}[c]{@{}l@{}}RMSECV/\\ RMSEP\end{tabular} & Moisture       & Oil            & Protein       & Starch        \\ \hline
-		1     & mp6                                                & 60                                                        & None                                                                     & RMSEP                                                   & 0.1446034(10)  & 0.09225961(10) & 0.1400926(10) & 0.3436289(10) \\
-		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSECV                                                  & 0.01488358(10) &                &               &               \\
-		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSEP                                                   & 0.02113168(10) &                &               &               \\
-		3     & m5                                                 & 60                                                        & SavitzkyGolay                                                            & RMSEP                                                   & 0.05628462(5)  & 0.03163213(12) & 0.1085697(6)  & 0.2371506(6)  \\
-		4     & m5                                                 & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.05862355(12) & 0.3891674(14)  & 0.3554446(8)  & 0.3878001(9)  \\
-		4     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4194983(12)  & 0.7190886(17)  & 0.3731878(8)  & 0.4980389(9)  \\
-		5     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4023674(10)  &                &               &               \\
-		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSECV                                                  &                & 0.08331678(7)  &               & 0.3322749(7)  \\
-		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSEP                                                   &                & 0.07401861(7)  &               & 0.2890035(7)  \\
-		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSECV                                                  &                & 0.06403154(7)  &               & 0.2426438(7)  \\
-		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSEP                                                   &                & 0.05660701(7)  &               & 0.2287837(7)  \\
-		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} & RMSECV                                                  &                & 0.04751603(7)  &               & 0.3216974(7)  \\
-		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(2,2,13)\end{tabular}  & RMSEP                                                   &                & 0.03468245(7)  &               & 0.3037632(7)  \\
-		7     & m5                                                 & 60                                                        & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} & RMSECV                                                  & 0.04043771(6)  & 0.04937681(10) & 0.1021954(7)  & 0.2630782(5)  \\
-		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSECV                                                  & 0.02177367(10) & 0.06621319(10) & 0.1194857(10) & 0.2937006(10) \\
-		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSEP                                                   & 0.0197695(10)  & 0.05955603(10) & 0.1123115(10) & 0.2723313(10)
+	\begin{tabular}{llllllllllllllll}
+		\cline{1-13}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Protein} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.141(0.0203) &  &  & 0.150 &  &  & 0.145 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 8 &  & 0.349(0.051) &  &  & 0.4466 &  &  & 0.4349 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 8 &  & 0.37(0.0485) &  &  & 0.4466 &  &  & 0.4349 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.107(0.0195) &  &  & 0.119 &  &  & 0.040 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 7 &  & 0.102(0.0186) &  &  & 0.110 &  &  & 0.033 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 13 & 0.119 ( 0.0155 ) & 0.11(0.0169) &  & 0.1080 & 0.1353 &  & 0.0429 & 0.0846 &  &  & 
 	\end{tabular}
+
+\caption{regression of protein. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:protein}
+\end{table}
+
+    \end{landscape}
+
+\begin{landscape}
+Table \ref{tab:starch} is the regression for starch.
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+	\begin{tabular}{llllllllllllllll}
+		\cline{1-13}
+		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Starch} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
+		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
+		1 & mp6 & None & 60(LOO) & 10 &  & 0.35(0.056) &  &  & 0.370 &  &  & 0.358 &  &  &  \\
+		3 & m5 & Scale & 40(LOO) & 9 &  & 0.393(0.0736) &  &  & 0.5010 &  &  & 0.4443 &  &  &  \\
+		3 & mp5 & Scale & 40(LOO) & 9 &  & 0.513(0.0779) &  &  & 0.5010 &  &  & 0.4443 &  &  &  \\
+		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.239(0.0449) &  &  & 0.196 &  &  & 0.100 &  &  &  \\
+		6 & m5 & SG(1,2,21) & 60(LOO) & 5 &  & 0.258(0.0453) &  &  & 0.228 &  &  & 0.101 &  &  &  \\
+		7 & m5 & SG(0,2,13) & 64(5-fold) & 8 & 0.333(0.0226) & 0.283(0.0624) &  & 0.312 & 0.214 &  & 0.240 & 0.219 &  &  &  \\
+		7 & m5 & SG(1,2,13) & 64(5-fold) & 8 & 0.2412(0.0171) & 0.221(0.049) &  & 0.248 & 0.221 &  & 0.240 & 0.219 &  &  &  \\
+		7 & m5 & SG(2,2,13) & 64(5-fold) & 8 & 0.318(0.0252) & 0.302(0.061) &  & 0.347 & 0.228 &  & 0.240 & 0.219 &  &  &  \\
+		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.292(0.0312) & 0.282(0.043) &  & 0.2579 & 0.2356 &  & 0.1137 & 0.1188 &  &  & 
+	\end{tabular}
+
+\caption{regression of starch. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+\label{tab:starch}
 \end{table}
     \end{landscape}
+
+	\subsection{Developed method significant test}
+\label{sec: test}
 

### 2019-08-21 MSc Project/Scratch/My_Analysis.Rmd
add the exchange area with remote servers

---
title: "Parallel all papers PLS for corn data"
author: "Hongwei Peng"
date: "09/07/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples

##60-20 10

###1~mp6 0.159

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples

##60-20 10

###2~mp6 0.107

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples

##60-20 10

###3~mp6 0.150

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples

##60-20 10

###4~mp6 0.370

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#2 A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration

##64-16 9 CV=5

###1~m5 RMSEC = 0.0149; RMSEP = 0.0201

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 9                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    #RMSECV <- RMSEP(corn.pls)$val[1,1,NV]             #change RMSECV to RMSEC
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[DF$train,])
    RMSECV <- sqrt(sum((predict-DF[DF$train,]$y)^2)/(n))
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 12

###1~m5 0.3506

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    #propvals <- apply(rawdata$propvals$data,2,scale)
    propvals <- rawdata$propvals$data
    NV <- 12                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 14

###2~m5 0.6912

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 14                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 8

###3~m5 0.4466

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 8                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 9

###4~m5 0.5010

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 9                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 12

###1~mp5 0.3506

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    #propvals <- apply(rawdata$propvals$data,2,scale)
    propvals <- rawdata$propvals$data
    NV <- 12                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 14

###2~mp5 0.6912

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 14                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 8

###3~mp5 0.4466

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 8                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#3 Reduced PCR/PLSR models by subspace projections

##40-40 Scale 9

###4~mp5 0.5010

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 9                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#4 Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra

##40-40 Scale 10

###1~mp5 0.357

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls) 
    m5data <-  apply(rawdata$m5spec$data,2,scale)
    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
    propvals <- apply(rawdata$propvals$data,2,scale)
    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#5 Cross-validation for the selection of spectral variables using the successive projections algorithm

##60-20 SavitzkyGolay filler (in) 3-fold but Loo better

###1~m5 0.040(5)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 5                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#5 Cross-validation for the selection of spectral variables using the successive projections algorithm

##60-20 SavitzkyGolay filler (in) 3-fold

###2~m5 0.029(12)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 12                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#5 Cross-validation for the selection of spectral variables using the successive projections algorithm

##60-20 SavitzkyGolay filler (in) 3-fold

###3~m5 0.119(6)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 6                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#5 Cross-validation for the selection of spectral variables using the successive projections algorithm

##60-20 SavitzkyGolay filler (in) 3-fold but Loo better

###4~m5 0.196(6)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 6                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm

##60-20 savitzkyGolay filler=(1,2,21) (in)

###1~m5 0.045(06)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)  
library("MALDIquant")
library(prospectr)  
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 6                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm

##60-20 savitzkyGolay=(1,2,21) (in)

###2~m5 0.028(10)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 10                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm

##60-20 savitzkyGolay=(1,2,21) (in)

###3~m5 0.110(07)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 7                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm

##60-20 savitzkyGolay=(1,2,21) (in)

###4~m5 0.228(05)

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 5                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)

##64-16 savitzkyGolay filler=(0,2,13) 7 5-fold

###2~m5 RMSECV=0.0729; RMSECP=0.0855

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 7                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)

##64-16 savitzkyGolay filler=(1,2,13) 7 5-fold

###2~m5 RMSECV=0.0577; RMSECP=0.0682

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 7                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)

##64-16 savitzkyGolay filler=(2,2,13) 7 5-fold

###2~m5 RMSECV=0.0370; RMSECP=0.0397

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 7                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)

##64-16 savitzkyGolay filler=(0,2,7) 8 5-fold

###4~m5 RMSECV=0.312; RMSECP=0.214

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 8                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)

##64-16 savitzkyGolay filler=(1,2,7) 8 5-fold

###4~m5 RMSECV=0.248; RMSECP=0.221

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 8                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)

##64-16 savitzkyGolay filler=(2,2,7) 8 5-fold

###4~m5 RMSECV=0.347; RMSECP=0.228

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library("MALDIquant")
library(prospectr)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(prospectr)
    library(pls)
    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
    }))
    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
    }))
    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
    }))
    propvals <- rawdata$propvals$data

    NV <- 8                                            #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)

```

#8 Using consensus interval partial least square in near infrared spectra analysis

##52-26 Delete 75 , 77; 10

###1~m5 RMSECV=0.0124; RMSEP=0.0157

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    m5data <- m5data[,c(-75,-77)]
    propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
    #plot(RMSEP(gas1), legendpos = "topright")         #check point
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#8 Using consensus interval partial least square in near infrared spectra analysis

##52-26 Delete 75 , 77; 13

###2~m5 RMSECV=0.0613; RMSEP=0.0673

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    m5data <- m5data[,c(-75,-77)]
    propvals <- propvals[,c(-75,-77)]

    NV <- 13                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
    #plot(RMSEP(corn.pls), legendpos = "topright")         #check point
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#8 Using consensus interval partial least square in near infrared spectra analysis

##52-26 Delete 75 , 77 13

###3~m5 RMSECV=0.1080; RMSEP=0.1353

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    m5data <- m5data[,c(-75,-77)]
    propvals <- propvals[,c(-75,-77)]

    NV <- 13                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
    #plot(RMSEP(corn.pls), legendpos = "topright")         #check point
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

#8 Using consensus interval partial least square in near infrared spectra analysis

##52-26 Delete 75 , 77 10

###4~m5 RMSECV=0.2579; RMSEP=0.2356

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    m5data <- m5data[,c(-75,-77)]
    propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
})
stopCluster(cl)
```

### 2019-08-21 MSc Project/Scratch/Scratch/run.Rmd
add the exchange area with remote servers

--- 2019-06-25 MSc Project/Untitled.Rmd
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~m5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~m5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~m5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~m5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~m5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~m5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~m5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~m5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~m5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp5data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp5data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp5data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp5data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 1~mp6data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 1~mp6data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 2~mp6data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 2~mp6data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 3~mp6data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 3~mp6data Loop=10 scaled")
 apply(PlotData,2,mean)
@@
 par(mfrow=c(1,2))
-boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp6data Loop=10")
-boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp6data Loop=10")
+boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS 4~mp6data Loop=10 scaled")
+boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS 4~mp6data Loop=10 scaled")
 apply(PlotData,2,mean)

### 2019-08-21 MSc Project/Scratch/Scratch/R_run.sh

@@ -1,0 +1,19 @@
+#!/bin/bash -l
+
+#$ -S /bin/bash
+#$ -pe mpi 32
+#$ -l tmpfs=30G 
+#$ -N clonealign 
+#$ -l h_rt=48:0:0
+
+
+#$ -wd /home/uczlhpe/Scratch/
+
+#$ -m eas
+#$ -M h.peng@ucl.ac.uk
+
+module unload compilers
+module unload mpi
+module load r/recommended
+
+R CMD BATCH /home/uczlhpe/Scratch/run.R

### 2019-08-21 MSc Project/Scratch/Scratch/Rmd_run.R

@@ -1,0 +1,2 @@
+library(rmarkdown)
+rmarkdown::render(input="/home/uczlhpe/Scratch/run.rmd")

### 2019-08-21 MSc Project/Scratch/Scratch/Rmd_run.sh

@@ -1,0 +1,16 @@
+#!/bin/bash -l
+
+#$ -S /bin/bash
+#$ -l h_rt=72:0:0
+#$ -l mem=500G
+
+#$ -pe smp 1
+
+#$ -N clonealign
+#$ -wd /home/uczlhpe/Scratch/
+
+module unload compilers
+module unload mpi
+module load r/recommended
+
+R CMD BATCH /home/uczlhpe/Scratch/Rmd_run.R

### 2019-08-21 MSc Project/Scratch/Scratch/run-R.sh

@@ -1,0 +1,39 @@
+# software stack under SGE. This version works with the modules
+# environment upgraded in 2015.
+
+# R Version 3.4.2
+
+# 1. Request ten minutes of wallclock time (format hours:minutes:seconds).
+#    Change this to suit your requirements.
+#$ -l h_rt=72:0:0
+
+# 2. Request 1 gigabyte of RAM. Change this to suit your requirements.
+#$ -l mem=500G
+
+# 3. Set the name of the job. You can change this if you wish.
+#$ -N R_job_1
+
+# 4. Set the working directory to somewhere in your scratch space.  This is
+# a necessary step with the upgraded software stack as compute nodes cannot
+# write to your $HOME.
+#
+# NOTE: this directory must exist.
+#
+# Replace "<your_UCL_id>" with your UCL user ID :)
+#$ -wd /home/uczlhpe/Scratch/R_output
+ 
+# 5. Your work *must* be done in $TMPDIR 
+cd $TMPDIR
+
+# 6. Run your R program.
+module unload compilers
+module unload mpi
+module load r/recommended
+
+R --no-save < /home/uczlhpe/Scratch/myR_job.R > myR_job.out
+
+# 7. Preferably, tar-up (archive) all output files onto the shared scratch area
+#    this will include the R_output file above.
+tar zcvf $HOME/Scratch/R_output/files_from_job_$JOB_ID.tgz $TMPDIR
+
+# Make sure you have given enough time for the copy to complete!

### 2019-08-21 MSc Project/Scratch/Scratch/run.R

@@ -1,0 +1,69 @@
+library(R.matlab)
+library(pls)
+library(lars)
+library(ggplot2)
+library(parallel)                                        # load the parallel package
+clnum<-detectCores()-1                                   # Calculate and set the number of available cores
+cl <- makeCluster(getOption("cl.cores", clnum))          # Initialization parallel
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                 # n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+    n=40
+    NV <- 15                                            # number of variables 
+    sample <- sample(1:80)                               # set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                    # input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                            # just to be certain, it was "AsIs"
+    #str(DF)                                             # check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                          # chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                        # check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                       # check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
[…]

### 2019-08-22 MSc Project/Scratch/run.R
added something auto

@@ -1,0 +1,70 @@
+library(R.matlab)
+library(pls)
+library(lars)
+library(ggplot2)
+library(parallel)                                        # load the parallel package
+clnum<-detectCores()                                   # Calculate and set the number of available cores
+cl <- makeCluster(getOption("cl.cores", clnum))          # Initialization parallel
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                 # n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+    n=40
+    NV <- 15                                            # number of variables 
+    sample <- sample(1:80)                               # set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                    # input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                            # just to be certain, it was "AsIs"
+    #str(DF)                                             # check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                          # chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                        # check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                       # check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
[…]

### 2019-08-22 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
sample numbers

@@
 	\label{sec:Loop times}
+
 	\begin{figure}[h]    % start of figure environment
 		\centering           % put the graph(s) in the centre of the page (horizontally)
-		\includegraphics[width=15.5cm, angle=0]{no_loop_time500.pdf}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{boxplot_RMSECV_loop_times_500.pdf}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{boxplot_RMSEP_loop_times_500.pdf} % angle changes orientation
 		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-		\caption{RMSECV and RMSEP under different loop times}          % a meaningful caption
-		\label{fig:looptimes}               % label for the figure
+		\caption{The boxplot of RMSECV and RMSEP from PLSR of oil on m5 under different loop times}          % a meaningful caption
+		\label{fig:sd_RMSECV_RMSEP}               % label for the figure
 	\end{figure}                        % end of figure environment
@@
 	\centering           % put the graph(s) in the centre of the page (horizontally)
-	\includegraphics[width=8.5cm, angle=0]{Number_of_loop_times_mp5-1.pdf}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{sd_RMSECV_loop_times_500.pdf}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{sd_RMSEP_loop_times_500.pdf} % angle changes orientation
 	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{SD under different loop times}          % a meaningful caption
-	\label{fig:looptimes}               % label for the figure
+	\caption{The standard deviation of RMSECV and RMSEP from PLSR of oil on m5 under different loop times}          % a meaningful caption
+	\label{fig:sd_RMSECV_RMSEP}               % label for the figure
 \end{figure}                        % end of figure environment

### 2019-08-23 MSc Project/Scratch/My_Analysis.Rmd
add sample number

@@
 ---
-#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
-
-##60-20 10
-
-###1~mp6 0.159
 
@@
 library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
 cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
 clusterExport(cl, "rawdata")                           # 额外加载变量
@@
     NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp6data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
-
-##60-20 10
-
-###2~mp6 0.107
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    #m5data <- m5data[,c(-75,-77)]
-    #propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp6data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
-
-##60-20 10
-
-###3~mp6 0.150
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    #m5data <- m5data[,c(-75,-77)]
-    #propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp6data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#1 A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples
-
-##60-20 10
-
-###4~mp6 0.370
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    #m5data <- m5data[,c(-75,-77)]
-    #propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp6data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  #cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#2 A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration
-
-##64-16 9 CV=5
-
-###1~m5 RMSEC = 0.0149; RMSEP = 0.0201
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    #m5data <- m5data[,c(-75,-77)]
-    #propvals <- propvals[,c(-75,-77)]
-
-    NV <- 9                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    #RMSECV <- RMSEP(corn.pls)$val[1,1,NV]             #change RMSECV to RMSEC
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[DF$train,])
-    RMSECV <- sqrt(sum((predict-DF[DF$train,]$y)^2)/(n))
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 12
-
-###1~m5 0.3506
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    #propvals <- apply(rawdata$propvals$data,2,scale)
-    propvals <- rawdata$propvals$data
-    NV <- 12                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
   #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(20:70,300))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
   par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
+  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
   PlotDataMean <- apply(PlotData,2,mean)
   PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 14
-
-###2~m5 0.6912
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 14                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 8
-
-###3~m5 0.4466
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 8                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 9
-
-###4~m5 0.5010
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 9                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 12
-
-###1~mp5 0.3506
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    #propvals <- apply(rawdata$propvals$data,2,scale)
-    propvals <- rawdata$propvals$data
-    NV <- 12                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 14
-
-###2~mp5 0.6912
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 14                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 8
-
-###3~mp5 0.4466
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 8                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#3 Reduced PCR/PLSR models by subspace projections
-
-##40-40 Scale 9
-
-###4~mp5 0.5010
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 9                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#4 Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra
-
-##40-40 Scale 10
-
-###1~mp5 0.357
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls) 
-    m5data <-  apply(rawdata$m5spec$data,2,scale)
-    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
-    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
-    propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(40,300))                         #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#5 Cross-validation for the selection of spectral variables using the successive projections algorithm
-
-##60-20 SavitzkyGolay filler (in) 3-fold but Loo better
-
-###1~m5 0.040(5)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 5                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
 })
@@
 ```
-
-#5 Cross-validation for the selection of spectral variables using the successive projections algorithm
-
-##60-20 SavitzkyGolay filler (in) 3-fold
-
-###2~m5 0.029(12)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 12                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#5 Cross-validation for the selection of spectral variables using the successive projections algorithm
-
-##60-20 SavitzkyGolay filler (in) 3-fold
-
-###3~m5 0.119(6)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 6                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#5 Cross-validation for the selection of spectral variables using the successive projections algorithm
-
-##60-20 SavitzkyGolay filler (in) 3-fold but Loo better
-
-###4~m5 0.196(6)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 6                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 savitzkyGolay filler=(1,2,21) (in)
-
-###1~m5 0.045(06)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)  
-library("MALDIquant")
-library(prospectr)  
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 6                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 savitzkyGolay=(1,2,21) (in)
-
-###2~m5 0.028(10)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 10                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 savitzkyGolay=(1,2,21) (in)
-
-###3~m5 0.110(07)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 7                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#6 A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm
-
-##60-20 savitzkyGolay=(1,2,21) (in)
-
-###4~m5 0.228(05)
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 5                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(60,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 savitzkyGolay filler=(0,2,13) 7 5-fold
-
-###2~m5 RMSECV=0.0729; RMSECP=0.0855
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,0,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 7                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 savitzkyGolay filler=(1,2,13) 7 5-fold
-
-###2~m5 RMSECV=0.0577; RMSECP=0.0682
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 7                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 savitzkyGolay filler=(2,2,13) 7 5-fold
-
-###2~m5 RMSECV=0.0370; RMSECP=0.0397
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,2,2,13)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 7                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 savitzkyGolay filler=(0,2,7) 8 5-fold
-
-###4~m5 RMSECV=0.312; RMSECP=0.214
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,0,2,7)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 8                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 savitzkyGolay filler=(1,2,7) 8 5-fold
-
-###4~m5 RMSECV=0.248; RMSECP=0.221
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,1,2,7)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 8                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#7 Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)
-
-##64-16 savitzkyGolay filler=(2,2,7) 8 5-fold
-
-###4~m5 RMSECV=0.347; RMSECP=0.228
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library("MALDIquant")
-library(prospectr)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(prospectr)
-    library(pls)
-    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
-      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
-    }))
-    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
-      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
-    }))
-    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
-      savitzkyGolay(x,2,2,7)                          #SavitzkyGolay filler
-    }))
-    propvals <- rawdata$propvals$data
-
-    NV <- 8                                            #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=5, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    #plot(RMSEP(corn.pls), legendpos = "topright")     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(64,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],'\n')
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-
-```
-
-#8 Using consensus interval partial least square in near infrared spectra analysis
-
-##52-26 Delete 75 , 77; 10
-
-###1~m5 RMSECV=0.0124; RMSEP=0.0157
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    m5data <- m5data[,c(-75,-77)]
-    propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,1])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
-    #plot(RMSEP(gas1), legendpos = "topright")         #check point
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#8 Using consensus interval partial least square in near infrared spectra analysis
-
-##52-26 Delete 75 , 77; 13
-
-###2~m5 RMSECV=0.0613; RMSEP=0.0673
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    m5data <- m5data[,c(-75,-77)]
-    propvals <- propvals[,c(-75,-77)]
-
-    NV <- 13                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,2])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
-    #plot(RMSEP(corn.pls), legendpos = "topright")         #check point
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#8 Using consensus interval partial least square in near infrared spectra analysis
-
-##52-26 Delete 75 , 77 13
-
-###3~m5 RMSECV=0.1080; RMSEP=0.1353
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    m5data <- m5data[,c(-75,-77)]
-    propvals <- propvals[,c(-75,-77)]
-
-    NV <- 13                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,3])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
-    #plot(RMSEP(corn.pls), legendpos = "topright")         #check point
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  #par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```
-
-#8 Using consensus interval partial least square in near infrared spectra analysis
-
-##52-26 Delete 75 , 77 10
-
-###4~m5 RMSECV=0.2579; RMSEP=0.2356
-
-```{r echo=FALSE,warning=FALSE,message=FALSE}
-library(R.matlab)
-library(pls) 
-library(lars)
-library(ggplot2)
-library(parallel)                                      # 载入parallel包
-clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
-cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
-system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
-    library(pls)
-    m5data <- rawdata$m5spec$data
-    mp5data <- rawdata$mp5spec$data
-    mp6data <- rawdata$mp6spec$data
-    propvals <- rawdata$propvals$data
-    m5data <- m5data[,c(-75,-77)]
-    propvals <- propvals[,c(-75,-77)]
-
-    NV <- 10                                           #number of variables 
-    sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
-                     y=propvals[,4])
-    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
-    #str(DF)                                           #check point
-    DF$train <- rep(FALSE, 80)
-    DF$train[sample<=n] <- TRUE                        #chose calibration
-    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=10, jackknife = TRUE, subset = train)
-    #summary(corn.pls,what="all")                      #check point
-    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
-    #print(RMSECV)                                     #check point
-    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
-    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
-    #print(RMSEP)                                      #check point
-    #plot(R2(corn.pls))                                #check point
-    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
-  }
-  #corn_PLS(n)
-  n <- as.matrix(rep(52,300))                            #the number of calibration, rep(a:b,c): from a to b and repeat c. 
-  #PlsResult <- apply(n,1,corn_PLS)                     #loop
-  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
-  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
-  cat(signif(PlotDataMean[2],3),"(",signif(PlotDataSd[2],3),")","\n")
-  cat(signif(PlotDataMean[3],3),"(",signif(PlotDataSd[3],3),")","\n")
-})
-stopCluster(cl)
-```

### 2019-08-23 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
add sample number

@@
 	\label{PLS_al}
-	The partial least squares regression (PLS) is a multi-regression technique proposed by \citet{wold1984collinearity}, and it is also the most common statistical method in the research of near-infrared spectroscopy.
+	The partial least squares regression (PLS) is a multi-regression technique proposed by \citet{wold1984collinearity}, and it is also the most common statistical method in the research of near-infrared spectroscopy (NIR).
 Partial least squares regression is similar to principal components analysis (PCA) and is also a factor analysis method.
 In the modelling  process, it is first necessary to decompose the matrix of spectrum and then extract a few principal components (these variables are called latent variables in PLS) to represent most of the information of original spectrum.
-Because the spectral data is high-dimensional, the number of independent variables is more than the number of samples, thus it cannot meet the basic assumption of least squares method.
+Because the spectral data is high-dimensional, the number of independent variables is more than the number of samples, thus it cannot meet the basic assumption of least squares method (OLS).
 Therefore, it is necessary to extracting the data to some components, and then make the regression.
-Compared with PCA, PLS not only considers the dimensionality reduction of the independent variables, but also maximizes the covariance between the components and target variables.
+Compared with PCA, PLS not only considers the dimensionality reduction of the independent variables, but also maximizes the covariance between principal components and target variables.
 In this way, the covariance between the extracted components and the target vector will be the maximum.
-From this point, PLS is the improvement and further development of PCA, and the results in many applications also prove that PLS has better performance than PCA.
+According to this point, PLS is the improvement and further development of PCA, and the results in many applications also prove that PLS has better performance than PCA.
 
@@
 	\end{equation}
-	Where T and P are the scoring matrix and the load matrix of the spectral matrix X, respectively.
-U and Q are the scoring matrix and the load matrix of the detection target vector Y, respectively.
-E and F are residual matrices of the spectral matrix X and the detection target vector Y, respectively, and T and U can perform linear regression as follows:
-	......
+
+	Where $T$ and $P$ are the scoring matrices and the loading matrices of the spectral matrix $X$, respectively.
+$U$ and $Q$ are the scoring matrices and the loading matrices of target vector $Y$.
+$E$ and $F$ are residual matrices of the spectral matrix $X$ and target vector $Y$, respectively, and $T$ and $U$ can perform linear regression as follows:
+
+	\begin{equation}
+u_i=t_ib_i
+	\label{equ:ui} 
+\end{equation}
+
+	Here $t_i$ and $u_i$ are the first column data of $T$ and $U$, respectively.
+
+	In the process of establishing partial least squares regression models, the spectral matrix $X$ and the target vector $Y$ are decomposed in an iterative manner.
+In each iteration, the principal components $t_i$ and $u_i$ of $T$ and $U$ can be obtained separately.
+Linear regression is performed on t and u by Equation (\ref{equ:ui}), and then the information explained by t and u is subtracted from the spectral matrix and the target vector, respectively, to obtain a residual matrix of the spectral matrix and the target vector.
+Finally, the residual matrix is brought into the previous iterative process again, which is the spectral matrix and the target vector in the next iteration matrix.
+This iterative process is terminated by constant iteration until the pre-variable of the specified target is obtained.
+The specific operation flow, pseudo code is as follows
+	1, initialize the score vector u=y
+	2, calculate the weight vector by formula:
+
+	3,
+
+	4. Calculate the spectral score vector.
+
+	5. Calculate the load vector of the spectral matrix.
+
+	6, calculate the detection target vector according to the spectral matrix score vector
+
+	7,
+
+	8. If the number of extracted money variables reaches the number required by the algorithm, the iteration is terminated, otherwise it returns to step 1 to continue the next iteration.
+
+	When the above is the end of the code iteration process, the regression coefficients of the partial least squares regression model are calculated according to the equation.
+	Finally, the prediction model of its partial least squares regression model is as follows
 

### 2019-08-29 MSc Project/Scratch/My_Analysis.Rmd
add the datasets and intro and loop time and sample number

@@
 author: "Hongwei Peng"
-date: "09/07/2019"
-output:
-  pdf_document: default
-  html_document:
-    df_print: paged
+date: "28/08/2019"
+output: html_document
 ---
 
+#1~m5
 ```{r echo=FALSE,warning=FALSE,message=FALSE}
@@
 library(parallel)                                      # 载入parallel包
-clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
 cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
 system.time({
-  corn_PLS=function(n){                                #n is the number of calibration
+  corn_PLS=function(NV){                                #n is the number of calibration
     library(pls)
@@
 
-    NV <- 10                                           #number of variables 
+    n <- 60                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
@@
   #corn_PLS(n)
-  n <- as.matrix(rep(20:70,300))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of moisture on m5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of moisture on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
   #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="1~m5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
 })
 stopCluster(cl)
+```
 
+#2~m5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of oil on m5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of oil on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="2~m5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
 ```
+
+#3~m5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of protein on m5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of protein on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="3~m5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#4~m5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of starch on m5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of starch on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="4~m5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#1~mp5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of moisture on mp5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of moisture on mp5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="1~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#2~mp5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of oil on mp5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of oil on mp5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="2~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#3~mp5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of protein on mp5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of protein on mp5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="3~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#4~mp5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of starch on mp5")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of starch on mp5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="4~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#1~mp6
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of moisture on mp6")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of moisture on mp6")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="1~mp6_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#2~mp6
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of oil on mp6")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of oil on mp6")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="2~mp6_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#3~mp6
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of protein on mp6")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of protein on mp6")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="3~mp6_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```
+
+#4~mp6
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(NV){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    n <- 60                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(mp6data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of starch on mp6")
+  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of starch on mp6")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  if (Myriad_flag==TRUE) {
+    save(PlotData,file="4~mp6_Number_of_components_PlotData.RData")                  # save results in myriad
+  }
+  clnum
+})
+stopCluster(cl)
+```

### 2019-08-29 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
add the datasets and intro and loop time and sample number

@@
 \usepackage{pdflscape} %put pages lscape
+\usepackage{listings}
+\usepackage[T1]{fontenc}   %for the ""
+\usepackage[title]{appendix} %for appendix
 
@@
 	\maketitle         % create title etc
+
+	\section{Abstruct} 
+	These algorithms will often claim that their new algorithm has a better performs.
+So the purpose of this dissertation is to search for as many different papers as possible, and write a critical overall to find the most efficient measure that can evaluate whether the model performs well and quantify the improvements mentioned in the paper.
+	\newpage           % start a new page
+
+	\section{Acknowledgements} 
+ 	I would thank
+	\newpage           % start a new page
+
 	\tableofcontents   % create table of contents
@@
 
-	The most readily available high-dimensional NIR spectroscopic data is called corn data.
-There are many algorithms for analysing corn data in many publications.
-These algorithms will often claim that their new algorithm has a better performs.
-So the purpose of this dissertation is to search for as many different papers as possible, and write a critical overall to find the most efficient measure that can evaluate whether the model performs well and quantify the improvements mentioned in the paper.
-
 	\section{Introduction}             % start a new section called `Introduction'
 	\label{sec:intro}                  % create label for this section
+
+	Introduction
+	The near-infrared spectroscopy mainly reflects the frequency of the vibration of the hydrogen-containing group and the absorption of the frequency doubling at each level.
+Infrared spectroscopy combined with chemometric methods have been widely used for the detection of various plant samples.
+When the samples of plants are tested by near-infrared spectroscopy, this method is cheaper and faster than the traditional chemical method.
+
+	However, although the spectroscopy technique is more convenient, for some samples with similar properties, it is impossible to draw an identification conclusion through an intuitive method.
+Because the detected high-dimensional data can not be read directly.
+Therefore, a stoichiometric method is needed to establish a prediction model in which spectral information is associated with sample features.
+Because spectral information belongs to high latitude data and has strong collinearity, choosing the appropriate regression method is very important for predictive models.
+Among them, common spectral data modeling methods include partial least squares and principal component regression.
+Among them, partial minimization multiplication has many applications in spectral analysis, and it is a very effective chemometric method.
+The partial least squares method can not only comprehensively screen out significant spectral data but also eliminate spectral collinearity problems.
+The main idea of the algorithm is to simplify the data structure and highlight the main contradictory multivariate statistical methods.
+
+	The infrared spectral data of corn is the most easily obtained high-dimensional infrared spectrum data on the network.
+In recent years, many papers have analyzed corn data as an example.
+The most common algorithm for analyzing corn infrared spectral data is the partial least squares method.
+The partial least squares method can effectively reduce the dimensionality of the infrared spectrum.
+This is one of the best ways at the moment.
+Therefore, a large part of the paper is based on the partial least squares method to improve the accuracy of the prediction.
+And this type of paper also claims that its method has better performance than partial least squares.
+E.g:
+
+	Although this type of algorithm does show better performance from the results of the data, even if you choose the same corn data for analysis, the method of selection, the number of principal components selected, and so on, some related variables will result in the results.
+Make an impact.
+Most papers usually show that the new algorithm has smaller rmsep and rmsep than partial least squares in a regression result.
+So the main research work of this paper is to write a rough critical document by reading as much literature as possible related to corn data.
+Then study how each variable affects the partial least squares regression based on corn data.
+Finally, compare the results in the paper and evaluate whether the new method has more outstanding performance.
 
@@
 	\label{sec:data}
+
+	Corn data is the most readily available high-dimensional Near-infrared spectral data.
+This data was published on the Internet (http://www.eigenvector.com/data/Corn/index.html) by Eigenvector Research, Inc.
+in 2005.
+The data consisted of 80 corn samples measured on three different NIR spectrometers named m5, mp5 and mp6.
+The spectral wavelength range is 1100$\sim$2498nm with an interval of 2nm.
+Hence there are 700 channels for each spectrum in each sample.
+Figure \ref{fig:Spectra_on_instrument_m5} is the plot of spectra on m5 and mp5.
+
+		\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{Spectra_on_instrument_m5.pdf}  % width changes size
+				\includegraphics[width=7.5cm, angle=0]{Spectra_on_instrument_mp5.pdf}  % width changes size
+		\caption{Spectra on instrument m5 and mp5}          % a meaningful caption
+		\label{fig:Spectra_on_instrument_m5}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	 Each of these samples also gives the corresponding moisture, oil, protein and starch values.
+In this dissertation, the spectrum data measured by m5 spectrometers calls as m5.
+So the same as mp5 and mp6.
+And one of m5, mp5 and mp6 NIR data will be selected as $X$ in each regression.
+The value related to the moisture, oil, protein and starch values was considered as the dependent variable $Y$.
+So $X$ should be one of three 80$\times$700 matrices and $Y$ should be one of four 80$\times$1 vectors.
+	  In addition, corn data set will be divided into a calibration set and a prediction set using a random sampling method.
+Model the calibration set and then predict prediction set.
+Finally, RMSECV and RMSEP are calculated as the criterion.
+
+	Firstly, the effect of each conditions on partial least squares regression (PLSR) is observed by different performance of PLSR based on corn data under different conditions.
+Then find out as much papers using corn data as possible to compare the results in papers with the results in dissertation.
+In this way, we can observe whether the new algorithm has a significant improvement compared to PLSR.
+Finally, the F-test is used to test whether the new method is significantly different from PLS.
 
@@
 
-	1, Root Mean Square Error for Calibration samples (RMSEC) is proposed by \citet{2yun2014strategy}.
+	1. Root Mean Square Error for Calibration samples (RMSEC) is proposed by \citet{2yun2014strategy}.
 
-	2, RMSECV is mentioned by many papers \citep{8ji2015using}.
+	2.
+RMSECV is mentioned by many papers \citep{8ji2015using}.
 And there are two cross-validation methods.
@@
 
-	3, The Root Mean Square Error of Prediction (RMSEP) is mentioned by \citet{1su2006partial}.
+	3.
+The Root Mean Square Error of Prediction (RMSEP) is mentioned by \citet{1su2006partial}.
 This is a generally accepted method of evaluating models.
@@
 
-	4, There are few papers mentioned that $R^2$ is used to measure the model \citep{tatavarti2005assessment}.
+	4.
+There are few papers mentioned that $R^2$ is used to measure the model \citep{tatavarti2005assessment}.
 But this method is also flawed.
@@
 
-	1. Nothing to deal with \citep{1su2006partial}.
+	\begin{enumerate}
 
-	2. Scale the data \citep{4ergon2006reduced}.
+	\item Nothing to deal with \citep{1su2006partial}.
 
-	3. SavitzkyGolay filter processing on the data \citep{3galvao2007cross}.
+	\item Scale the data \citep{4ergon2006reduced}.
 
-	4. Delete the outliers \citep{8ji2015using}.
+	\item SavitzkyGolay filter processing on the data \citep{3galvao2007cross}.
+
+	\item Delete the outliers. For example \citet{8ji2015using} take out the 75th and 77th corn 
+	spectrum from dataset as outliers.
+
+	\end{enumerate}
 
@@
 
-	1. A completely random sample \citep{1su2006partial}.
+	\begin{enumerate}
 
-	2. Choosing the samples by SPXY method \citep{3galvao2007cross}.
+	\item A completely random sample \citep{1su2006partial}.
 
-	3. Use the Kennard-Stone (K-S) algorithm \citep{zhao2015optimization}.
+	\item Choosing the samples by SPXY method \citep{3galvao2007cross}.
 
-	4. Directly divide the raw data into the first half and the second half, the first half is cross-validation sets, and the second half is prediction set \citep{4ergon2006reduced}.
+	\item Use the Kennard-Stone (K-S) algorithm \citep{zhao2015optimization}.
+
+	\item Directly divide the raw data into the first half and the second half, the first half is cross-validation sets, and the second half is prediction set \citep{4ergon2006reduced}.
+
+	\end{enumerate}
 
@@
 	The cross-validation is to divide the data into n groups.
-One of group is selected as the prediction set, and the remaining n-1 groups are used as the training set, and testing n times.
+One of group is selected as the prediction set, and the remaining n-1 groups are used as calibration sets, and testing n times.
 Finally, the average of results of all tests was taken as the cross-validation result.
@@
 
-	Where $T$ and $P$ are the scoring matrices and the loading matrices of the spectral matrix $X$, respectively.
-$U$ and $Q$ are the scoring matrices and the loading matrices of target vector $Y$.
+	Where $T$ and $P$ are the score matrices and the loading matrices of the spectral matrix $X$, respectively.
+$U$ and $Q$ are the score matrices and the loading matrices of target vector $Y$.
 $E$ and $F$ are residual matrices of the spectral matrix $X$ and target vector $Y$, respectively, and $T$ and $U$ can perform linear regression as follows:
@@
 In each iteration, the principal components $t_i$ and $u_i$ of $T$ and $U$ can be obtained separately.
-Linear regression is performed on t and u by Equation (\ref{equ:ui}), and then the information explained by t and u is subtracted from the spectral matrix and the target vector, respectively, to obtain a residual matrix of the spectral matrix and the target vector.
-Finally, the residual matrix is brought into the previous iterative process again, which is the spectral matrix and the target vector in the next iteration matrix.
-This iterative process is terminated by constant iteration until the pre-variable of the specified target is obtained.
-The specific operation flow, pseudo code is as follows
-	1, initialize the score vector u=y
-	2, calculate the weight vector by formula:
+Linear regression is performed on $t_i$ and $u_i$ by Equation (\ref{equ:ui}), and then the information explained by $t_i$ and $u_i$ is subtracted from spectral matrices and target vectors, respectively, to obtain the residual matrices.
+Finally, the residual matrices is brought into the previous iterative process again, which are the spectral matrices and the target vectors in next iteration.
+This iterative process is terminated by constant iteration until the latent variable of the specified target is obtained.
+The specific operation flow, pseudocode as follows:
 
-	3,
+	\begin{enumerate}
 
-	4. Calculate the spectral score vector.
+	\item Initialize the score vector $u=Y$.
 
-	5. Calculate the load vector of the spectral matrix.
+	\item Calculate the weight vector $\omega$ by formula \ref{equ:omega}:
 
-	6, calculate the detection target vector according to the spectral matrix score vector
+	\begin{equation}
+	\omega=X'u/(u'u)
+	\label{equ:omega} 
+	\end{equation}
 
-	7,
+	\item Let $\omega=\omega/\left\|\omega\right\|$.
 
-	8. If the number of extracted money variables reaches the number required by the algorithm, the iteration is terminated, otherwise it returns to step 1 to continue the next iteration.
+	\item Calculate the spectral score vector $t=X\omega$.
 
-	When the above is the end of the code iteration process, the regression coefficients of the partial least squares regression model are calculated according to the equation.
-	Finally, the prediction model of its partial least squares regression model is as follows
+	\item Calculate the spectral matrices' loading vector $p=X't/(t't)$.
+
+	\item According to the spectral matrix score vector, calculate target vector $q=Y't(t't)$.
+
+	\item Let $X=X-tp'$ and $Y=Y-tq$.
+
+	\item If the number of extracted latent variables reaches number required by the algorithm, the iteration is terminated, otherwise go back to step 1 and continue the next iteration.
+
+	\end{enumerate}
+
+	After the iteration process finish, the regression coefficients of the partial least squares regression model (PLSR) are calculated according to the equation \ref{equ:B}.
+	\begin{equation}
+	B=W(P'W)^{-1}Q
+	\label{equ:B} 
+	\end{equation}
+
+	Finally, the prediction model of the partial least squares regression model is as equation \ref{equ:y_unknow}.
+	\begin{equation}
+	Y_{unknow}=X_{unknow}B
+	\label{equ:y_unknow} 
+	\end{equation}
 
@@
 
-	\subsection{High performance computing system}
+	Parallel computing is the simultaneous calculation of tasks that are broken down into subtasks into multiple cores.
+There are two computer calculation ways: serial calculations, such as iterative algorithms, and parallel calculations, such as repeated experiments.
+When an algorithm calculations are all serial tasks, it is completely impossible to use parallel computing.
+When all the calculations from an algorithm are parallel tasks, then full parallel computing can be used.
+So, how much parallel computing can improve algorithm, it depends on the proportion of the algorithm's serial computing part and parallel computing part respectively.
+When there are less serial calculations in algorithm, the more time can be saved by parallel computing.
+In this dissertation, each partial least square regression process is a serial calculation and cannot be optimized by  parallel computing.
+However, repeated experiments with partial least squares regression can be optimized using parallel computing.
+
+	Because this dissertation is computationally heavy, parallel computing is considered to improve the efficiency of algorithm.
+Through the analysis of a small amount of experimental data, it is estimated that if a single-core calculation is used, the computation required to complete the whole paper will take about three months to end the calculation.
+In terms of time, if  dissertation doesn't optimize the algorithm, this is an impossible task to finish dissertation in time.
+
+	Parallel computing in R language is divided into two categories, one is implicit parallel computing and the other is explicit parallel computing.
+Implicit parallel computing hides most of the parallel computing details from the user, and the user does not need to know the specific calculation process.
+After library the implicit parallel computing related R packages, the system automatically enables parallel computing based on the current resources.
+The related R package includes "OpenBLAS", "Intel MKL" and "NVIDIA cuBLAS".
+But the disadvantage of this kind of parallel computing is that the efficiency of the upgrade is extremely limited.
+The other is explicit parallel computing.
+Explicit parallel computing requires the user to actively run parallel computing, and actively divide the data and assign tasks.
+This type of parallel computing can effectively improve the efficiency of the algorithm, but not as friendly as the former.
+The associated R language explicit parallel package includes "parallel", "foreach", "SupR" and "gpuR".
+Whether it is implicit parallel computing or parallel computing, parallel computing consumes a lot of memory, and the lazy evaluation programming strategy used by R exacerbates this problem.
+Therefore, when using parallel computing, you need to allocate enough memory space in advance to the program.
+This dissertation implements parallel computing through the family of "apply" functions optimized by "parallel" package in R.
+
+	The main steps of complete parallel computing process are as follows:
+	\begin{enumerate}
+	\item  Load the parallel package and calculate the number of available cores. R code is as follows:
+	\begin{lstlisting}[language=R]
+	library(parallel) 
+	clnum <- detectCores()
+	\end{lstlisting}
+
+	\item Initialize and set up a clustered parallel computing environment.
+
+	\begin{lstlisting}[language=R]
+	cl <- makeCluster(getOption("cl.cores", clnum))
+	\end{lstlisting}
+
+	\item Assign copies of packages and variables that need to be used in parallel computing to each core.
+
+	\begin{lstlisting}[language=R]
+	clusterExport(cl, "RawData")
+	\end{lstlisting}
+
+	\item Run the algorithm optimized for parallel computing.
+Here is the optimized code sample as following:
+
+	\begin{lstlisting}[language=R]
+	Result <- parSapply(cl, x, my_function)
+	\end{lstlisting}
+
+	\item Shut down the cluster.
+
+	\begin{lstlisting}[language=R]
+	stopCluster(cl)
+	\end{lstlisting}
+
+	\end{enumerate}
+
+	Enable different number of cores and running times as shown in Table \ref{parallel_time}.
+
+		\begin{table}[h]
+		\centering
+		\begin{tabular}{llllll}
+			\hline
+			Number of core & 1     & 9     & 18    & 27    & 36    \\ \hline
+			Running time (s)  & 97.42 & 68.84 & 58.56 & 55.77 & 54.97 \\ \hline
+		\end{tabular}
+		\caption{Different number of cores vs. running time of parallel computing and one core means no parallel computing.}
+		\label{parallel_time}
+	\end{table}
+
+	Table \ref{parallel_time} shows running time required for the corn data m5 spectrum to perform 5000 partial least squares regression on moisture data.
+As can be seen from the table, as the number of cores increases, the running time shows a significant downward trend.
+But when the number of cores exceeds a certain limit, the algorithm improvement through parallel computing is getting smaller and smaller.
+This is because, when the number of cores is too large, it will take a lot of time to allocate subtasks to the initialization process of each core.
+But when the amount of calculation becomes larger, parallel computing will show its superiority.
+
+	\subsection{High performance computing (HPC)}
 	\label{myriad}
+
+	High-performance computers are also often referred to as supercomputers.
+It is a cluster that is connected by a network of many servers called nodes.
+A cluster can simultaneously use multiple cores or multiple nodes to run multi-core tasks through a special network.
+And the reason why use high-performance computers for calculation in this dissertation is as follows.
+
+	\begin{enumerate}
+	\item Dissertation needs to run large parallel jobs.
+Usually, a single-core program needs to run continuously for 6$\sim$12 hours on personal computers every times.
+The personal computers cannot do anything  while running large parallel jobs, and you need to make sure computers do not encounter any unexpected situations, such as sleep, power outages, and accidental touches on the keyboard.
+So such a task is an unrealistic job to run locally.
+
+	\item Dissertation needs large quantities of RAM.
+Because this thesis uses parallel computing so many times, it consumes a lot of computer memory than a single core compute.
+While personal computers usually have only 16 GB, less than half of the available memory can be allocated to programming.
+So in terms of memory requirements, personal computers are not good enough.
+
+	\end{enumerate}
+
+	This dissertation uses two high-performance computing systems ,named "Myriad" and "Grace", provided by University College London.
+"Grace" consists of 684 compute nodes, 10,944 processor cores and over 1 Petabyte high-performance memory, which is the largest and fastest high-performance computing system in the UK university sector.
+And there are two ways to run r code through a cluster.
+
+	\begin{enumerate}
+
+	\item Load directly through commands in terminal and then use the R interactively. The codes for starting the R module are as follows.
+
+	\begin{lstlisting}[language=sh]
+	module unload compilers mpi
+	module load r/recommended
+	R
+	\end{lstlisting}
+
+	After setting anaconda environment, the interactive operation interface under tmux shell is as figure \ref{fig:R_cluster}.
+
+	\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=14.5cm, angle=0]{R_cluster.png} % angle changes orientation
+	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{R interactive operation interface under tmux shell}          % a meaningful caption
+	\label{fig:R_cluster}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\item Submit the task to the cluster through a batch job.
+These functions can be implemented through a runscript.
+Among this R runscript, the following variables need to be set in script:  required max wallclock time, required max memory, and required number of cores when run.
+There are also other additional functions, such as output path, or sending a message to mailbox when the code finishes running.
+These functions can be implemented through scripts.
+Finally, enter the command, start R module, and run the specified R file.
+
+	Simplified runscript is shown below.
+
+	\begin{lstlisting}[language=sh]
+#!/bin/bash -l
+#$ -S /bin/bash                          #Set type of shell
+#$ -pe mpi 36                            #Set number of cores
+#$ -l tmpfs=30G                          #Set max memory
+#$ -l h_rt=48:0:0                        #Set max wallclock time
+#$ -wd /lustre/scratch/scratch/uczlhpe/output
+                                         #Set working path
+#$ -m eas                                #Set email notification
+#$ -M xxx@ucl.ac.uk                      #Set email address
+
+module unload compilers
+module unload mpi
+module load r/recommended
+R CMD BATCH run.R                        #Run R code
+	\end{lstlisting}
+
+After completing the runscript, it can use "qsub" to submit this script into remote server queue and wait for it to run.
+
+	\end{enumerate}
+
+	Both methods have advantages and disadvantages.
+	The first method requires online wait, but the submitted task can be run immediately, and is suitable for use in program testing or when running a single program.
+In the second method, although it takes a while to run the code, when running a large number of serial programs and large parallel programs, it is a more sensible choice to submit the script to the cluster for calculation.
+In contrast, the advantage of clustering can be found not only in a more stable and better configuration than PC.
+Using a cluster also allows you to run multiple files at once, and a cluster can have multiple nodes running on multiple files at the same time.
+By disassembling the computing tasks and submitting them to the cluster in batches, the single-core calculation that takes up to three months to complete can be completed in just one week.
 
@@
 
-	\begin{figure}[h]    % start of figure environment
+	Set different loop times and repeat PLSR to calculate how many loop times are needed to get stable results.
+Too small a number of cycles will result in very unstable results and large standard deviations.
+However, because of the limitations of computer, there are also upper limits on the number of loop times.
+If the program loops too many times, it will require a unimaginable long runtime.
+
+	First, 40 samples were randomly selected as calibration set 40 samples as prediction set.
+Then make 10 as the number of component.
+Calculate the corresponding RMSECV and RMSEP.
+Then continue to cycle this process, get the figure of RMSECV and RMSEP based on different loop times.
+Through above steps, the  figure \ref{fig:sd_RMSECV_RMSEP} based on the partial least squares result under different cycle times can be obtained.
+Left graph of figure \ref{fig:sd_RMSECV_RMSEP} is RMSECV and the right boxplot is RMSEP.
+
+	\begin{figure}[]    % start of figure environment
 		\centering           % put the graph(s) in the centre of the page (horizontally)
-		\includegraphics[width=7.5cm, angle=0]{boxplot_RMSECV_loop_times_500.pdf}  % width changes size
-		\includegraphics[width=7.5cm, angle=0]{boxplot_RMSEP_loop_times_500.pdf} % angle changes orientation
-		\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\includegraphics[width=5.5cm, angle=0]{boxplot_RMSECV_loop_times_500.pdf}  % width changes size
+		\includegraphics[width=5.5cm, angle=0]{boxplot_RMSEP_loop_times_500.pdf} % angle changes orientation
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
 		\caption{The boxplot of RMSECV and RMSEP from PLSR of oil on m5 under different loop times}          % a meaningful caption
@@
 
-\begin{figure}[h]    % start of figure environment
+	 Figure \ref{fig:sd_RMSECV_RMSEP} shows that when the number of loops is too small, the results are not stable enough.
+When the number of cycles is less than 40, the result shows a significant deviation.
+But this table does not show how much the number of loops is appropriate.
+Therefore, the standard deviation plots based on loop times is made for before PLSR result.
+Figure \ref{fig:sd_RMSECV_loop_times_500} shows the standard deviations of RMSECV and RMSEP from PLSR of oil on m5 spectrum under different loop times.
+
+	\begin{figure}[]    % start of figure environment
 		\centering           % put the graph(s) in the centre of the page (horizontally)
-	\includegraphics[width=7.5cm, angle=0]{sd_RMSECV_loop_times_500.pdf}  % width changes size
-	\includegraphics[width=7.5cm, angle=0]{sd_RMSEP_loop_times_500.pdf} % angle changes orientation
-	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\includegraphics[width=5.5cm, angle=0]{sd_RMSECV_loop_times_500.pdf}  % width changes size
+		\includegraphics[width=5.5cm, angle=0]{sd_RMSEP_loop_times_500.pdf} % angle changes orientation
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
 		\caption{The standard deviation of RMSECV and RMSEP from PLSR of oil on m5 under different loop times}          % a meaningful caption
-	\label{fig:sd_RMSECV_RMSEP}               % label for the figure
+		\label{fig:sd_RMSECV_loop_times_500}               % label for the figure
 	\end{figure}                        % end of figure environment
+
+	Figure \ref{fig:sd_RMSECV_loop_times_500} shows that the standard deviations of RMSECV will decrease as the loop times increases.
+The RMSEP standard deviations will decrease with the increase of the loop times, and then tend to be stable.
+Through figure \ref{fig:sd_RMSECV_loop_times_500} it is easy to see that the loop times is around 350, and the standard deviations of RMSEP will show the stable trends.
+Hence the number of loop times should be set 40$\sim$350 times to get a stable PLSR result.
+Because less than 40 the results will show a big fluctuation and there are not different results for the more than 350 loop times.
 
@@
 			\end{tabular}
-
+			\caption{Papers and related numbers}
 			\label{tab:papers}
@@
 
-		Table \ref{tab:moisture} is the regression for moisture.
+		%Table \ref{tab:moisture} is the regression for moisture.
 		% Please add the following required packages to your document preamble:
@@
 
-	\end{landscape}
-
-	\begin{landscape}
-
-		Table \ref{tab:oil} is the regression for Oil.
+		%Table \ref{tab:oil} is the regression for Oil.
 		% Please add the following required packages to your document preamble:
@@
 		\end{table}
-	\end{landscape}
 
-	\begin{landscape}
-		Table \ref{tab:protein} is the regression for protein.
+		%Table \ref{tab:protein} is the regression for protein.
 		% Please add the following required packages to your document preamble:
@@
 
-	\end{landscape}
-
-	\begin{landscape}
-		Table \ref{tab:starch} is the regression for starch.
+		%Table \ref{tab:starch} is the regression for starch.
 		% Please add the following required packages to your document preamble:
@@
 
+	\begin{appendices}
+		\section{Number of samples}
+		\label{app:Number_of_samples}
+
+			\begin{figure}[h]    % start of figure environment
+			\centering           % put the graph(s) in the centre of the page (horizontally)
+			\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-1-1".png}  % width changes size
+			\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-1-2".png}  % width changes size
+			%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+			\caption{The RMSECV and RMSEP from PLSR of moisture on m5 under different number of calibration set}          % a meaningful caption
+			\label{fig:calibration_1-1}               % label for the figure
+			\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-2-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-2-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of oil on m5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_2-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-3-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-3-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of protein on m5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_3-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-4-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-4-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of starch on m5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_4-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-5-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-5-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of moisture on mp5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_5-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-6-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-6-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of oil on mp5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_6-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-7-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-7-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of protein on mp5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_6-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-8-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-8-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of starch on mp5 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_8-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-9-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-9-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of moisture on mp6 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_9-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-10-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-10-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of oil on mp6 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_10-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-11-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-11-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of protein on mp6 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_11-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-12-1".png}  % width changes size
+	\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-12-2".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The RMSECV and RMSEP from PLSR of starch on mp6 under different number of calibration set}          % a meaningful caption
+	\label{fig:calibration_12-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+		\clearpage
+		\section{Number of components}
+
+		\clearpage
+		\section{Pre-treatment}
+
+		\clearpage
+		\section{Cross-validation}
+
+	\end{appendices}
 \end{document}

### 2019-08-29 MSc Project/Scratch/run.R

@@ -5,7 +5,7 @@ library(ggplot2)
 library(parallel)                                        # load the parallel package
 clnum<-detectCores()                                   # Calculate and set the number of available cores
 cl <- makeCluster(getOption("cl.cores", clnum))          # Initialization parallel
-Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
 if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
 {
   rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
@@ -15,7 +15,7 @@ if (Myriad_flag==TRUE)                                   # FALSE means in PC env
 clusterExport(cl, "rawdata")                             # input the rawdata to parallel
 clusterExport(cl, "Myriad_flag")
 system.time({
-  corn_PLS=function(NV){                                 # n is the number of calibration
+  corn_PLS=function(n){                                 # n is the number of calibration
     library(pls)
     m5data <- rawdata$m5spec$data
     mp5data <- rawdata$mp5spec$data
@@ -23,11 +23,11 @@ system.time({
     propvals <- rawdata$propvals$data
     #m5data <- m5data[,c(-75,-77)]
     #propvals <- propvals[,c(-75,-77)]
-    n=40
-    NV <- 15                                            # number of variables 
+    #n=40
+    NV <- 10                                            # number of variables 
     sample <- sample(1:80)                               # set random order; the begin of reset order
     DF <- data.frame(NIR = I(m5data),                    # input data
-                     y=propvals[,2])
+                     y=propvals[,1])
     class(DF$NIR) <- "matrix"                            # just to be certain, it was "AsIs"
     #str(DF)                                             # check point
     DF$train <- rep(FALSE, 80)
@@ -43,27 +43,27 @@ system.time({
     return(cbind(RMSECV,RMSEP))                          # return 1x2matrix
   }
   #corn_PLS(n)
-  #n <- as.matrix(rep(10,100))                           # the number of calibration, rep(a:b,c): from a to b and repeat c. 
[…]

### 2019-08-29 MSc Project/matplot.R

@@ -1,0 +1,20 @@
+load("/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/no.loop_time_10-500.RData")
+#load("/Users/hongwei/Documents/GitHub/STAT/MSc Project/Scratch/loop_times_10_200_5PlotData.RData")
+load("/Users/hongwei/Documents/GitHub/STAT/MSc Project/Scratch/loop_times_500_10PlotData.RData")
+
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Loop times", ylab="RMSECV",main="Boxplot of RMSECV",cex.lab=1.5,cex.main=1.5)
+boxplot(V3~V1,data=PlotData,xlab="Loop times", ylab="RMSEP",main="Boxplot of RMSEP",cex.lab=1.5,cex.main=1.5)
+sd(PlotData$V3)
+
+test <- aggregate(x=PlotData[c("V2",'V3')], by = list(PlotData$V1), FUN=sd)
+
+plot(test$Group.1,test$V2,xlab="Loop times", ylab="Standard deviation",main="RMSECV",cex.lab=1.5,cex.main=1.5)
+plot(test$Group.1,test$V3,xlab="Loop times", ylab="Standard deviation",main="RMSEP",cex.lab=1.5,cex.main=1.5)
+
+library(ChemometricsWithR)
+wavelengths<-seq(1100, 2498,by=2)
+
+matplot(wavelengths,t(mp5data),lty=1,pch=NULL,type="l",xlab="wavelengths(nm)",ylab="abs",main="Spectra on instrument m5 ")
+Spectra_on_instrument_m5
+plot(m5data[1,])

### 2019-08-29 MSc Project/parallel PLS for corn data.R

@@ -5,8 +5,15 @@ library(ggplot2)
 library(parallel)                                      # 载入parallel包
 clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
 cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
+Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
 system.time({
   corn_PLS=function(n){                                #n is the number of calibration
     library(pls)
@@ -36,16 +43,20 @@ system.time({
     return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
   }
   #corn_PLS(n)
-  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(60,5))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
   PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
   par(mfrow=c(1,2))
-  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
+  boxplot(V2~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSECV",main="PLS of moisture on m5")
[…]

### 2019-08-29 MSc Project/Scratch/My_Analysis.Rmd
half of paper finished

--- 2019-08-23 MSc Project/Scratch/My_Analysis.Rmd
@@
 cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
-rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
-clusterExport(cl, "rawdata")                           # 额外加载变量
+Myriad_flag=TRUE                              # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
 system.time({
@@
   #corn_PLS(n)
-  n <- as.matrix(rep(20:70,300))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
@@
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
-  par(mfrow=c(1,2))
-  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
-  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
-  PlotDataMean <- apply(PlotData,2,mean)
-  PlotDataSd <- apply(PlotData,2,sd)
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSECV",main="PLS of moisture on m5")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSEP",main="PLS of moisture on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
   #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
-  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  ##if (Myriad_flag==TRUE) {
+   # #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
+  #}
+  clnum
 })
@@
 
+a <- as.data.frame(cbind(1,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])
+})
+stopCluster(cl)
+
+b <- as.data.frame(cbind(2,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 10                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+c <- as.data.frame(cbind(3,t(PlsResult)))
+
+PlotData <- rbind(a,b,c)
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSECV",main="PLS of moisture on m5")
+boxplot(V3~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSEP",main="PLS of moisture on m5")
+
 ```
+
+#2~m5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                       # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSECV",main="PLS of moisture on m5")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSEP",main="PLS of moisture on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  ##if (Myriad_flag==TRUE) {
+   # #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
+  #}
+  clnum
+})
+stopCluster(cl)
+
+a <- as.data.frame(cbind(1,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])
+})
+stopCluster(cl)
+
+b <- as.data.frame(cbind(2,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 10                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,2])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+c <- as.data.frame(cbind(3,t(PlsResult)))
+
+PlotData <- rbind(a,b,c)
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSECV",main="PLS of oil on m5")
+boxplot(V3~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSEP",main="PLS of oil on m5")
+
+```
+
+#3~m5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSECV",main="PLS of moisture on m5")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSEP",main="PLS of moisture on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  #if (Myriad_flag==TRUE) {
+    #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
+  #}
+  clnum
+})
+stopCluster(cl)
+
+a <- as.data.frame(cbind(1,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])
+})
+stopCluster(cl)
+
+b <- as.data.frame(cbind(2,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 10                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,3])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+c <- as.data.frame(cbind(3,t(PlsResult)))
+
+PlotData <- rbind(a,b,c)
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSECV",main="PLS of protein on m5")
+boxplot(V3~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSEP",main="PLS of protein on m5")
+
+```
+
+#4~m5
+```{r echo=FALSE,warning=FALSE,message=FALSE}
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                             # input the rawdata to parallel
+clusterExport(cl, "Myriad_flag")
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls)
+    m5data <- rawdata$m5spec$data
+    mp5data <- rawdata$mp5spec$data
+    mp6data <- rawdata$mp6spec$data
+    propvals <- rawdata$propvals$data
+    #m5data <- m5data[,c(-75,-77)]
+    #propvals <- propvals[,c(-75,-77)]
+
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSECV",main="PLS of moisture on m5")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of calibration set", ylab="RMSEP",main="PLS of moisture on m5")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
+  #if (Myriad_flag==TRUE) {
+    #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
+  #}
+  clnum
+})
+stopCluster(cl)
+
+a <- as.data.frame(cbind(1,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(pls) 
+    m5data <-  apply(rawdata$m5spec$data,2,scale)
+    mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+    mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+    propvals <- apply(rawdata$propvals$data,2,scale)
+    NV <- 10                                           #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3])
+})
+stopCluster(cl)
+
+b <- as.data.frame(cbind(2,t(PlsResult)))
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library("MALDIquant")
+library(prospectr)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+#Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
+  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
+}
+clusterExport(cl, "rawdata")                           # 额外加载变量
+system.time({
+  corn_PLS=function(n){                                #n is the number of calibration
+    library(prospectr)
+    library(pls)
+    m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
+      savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+    }))
+    propvals <- rawdata$propvals$data
+
+    NV <- 10                                            #number of variables 
+    sample <- sample(1:80)                             #set random order; the begin of reset order
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,4])
+    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+    #str(DF)                                           #check point
+    DF$train <- rep(FALSE, 80)
+    DF$train[sample<=n] <- TRUE                        #chose calibration
+    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+    #summary(corn.pls,what="all")                      #check point
+    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
+    #print(RMSECV)                                     #check point
+    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
+    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
+    #print(RMSEP)                                      #check point
+    #plot(R2(corn.pls))                                #check point
+    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
+  }
+  #corn_PLS(n)
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  #PlsResult <- apply(n,1,corn_PLS)                     #loop
+  PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
+  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
+  #par(mfrow=c(1,2))
+  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS after scaled")
+  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS after scaled")
+  #PlotDataMean <- apply(PlotData,2,mean)
+  #PlotDataSd <- apply(PlotData,2,sd)
+  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],'\n')
+})
+stopCluster(cl)
+
+c <- as.data.frame(cbind(3,t(PlsResult)))
+
+PlotData <- rbind(a,b,c)
+par(mfrow=c(1,2))
+boxplot(V2~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSECV",main="PLS of starch on m5")
+boxplot(V3~V1,data=PlotData,xlab="Pre-treatment type", ylab="RMSEP",main="PLS of starch on m5")
+
+```

### 2019-08-29 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
half of paper finished

@@
 
-	Introduction
-	The near-infrared spectroscopy mainly reflects the frequency of the vibration of the hydrogen-containing group and the absorption of the frequency doubling at each level.
-Infrared spectroscopy combined with chemometric methods have been widely used for the detection of various plant samples.
-When the samples of plants are tested by near-infrared spectroscopy, this method is cheaper and faster than the traditional chemical method.
+	Near-infrared spectroscopy is one of the spectral methods.
+Infrared spectroscopy combined with chemometric methods has been widely used in medical diagnostics, pharmaceuticals, food and various plant samples \citep{1su2006partial}.
+When the samples of plants are tested by near-infrared spectroscopy, this method is cheaper and faster than the conventional detection by chemical inspection methods.
+Since each wavelength in the spectrum corresponds to a compound bond, it is easy to judge the compound contained in a single compound by infrared spectroscopy.
+But the infrared spectrum has a wide range data.
+This results in a complex structure of the spectrum, so in many cases it is not possible to assign specific wavelength to specific chemical components.
+Therefore, a statistics method is needed to establish a prediction model in which spectral information is associated with sample eigenvalue.
+Because spectral information belongs to high dimension data and has strong multicollinearity, choosing an appropriate regression method is very important for prediction models.
+Multivariate regression analysis, such as principal component analysis (PCA), partial least squares regression (PLSR) or artificial neural networks, are often chosen to predict the required chemical information.
+Among those methods, PLSR has many applications in spectral analysis, and it is a very effective statistic method.
+The PLSR can not only comprehensively take out significant spectral data but also eliminate spectral multicollinearity problems.
+The main idea of algorithm is the multivariate statistical methods which reduce the dimensions of data, highlight the components, and then regression.
 
-	However, although the spectroscopy technique is more convenient, for some samples with similar properties, it is impossible to draw an identification conclusion through an intuitive method.
-Because the detected high-dimensional data can not be read directly.
-Therefore, a stoichiometric method is needed to establish a prediction model in which spectral information is associated with sample features.
-Because spectral information belongs to high latitude data and has strong collinearity, choosing the appropriate regression method is very important for predictive models.
-Among them, common spectral data modeling methods include partial least squares and principal component regression.
-Among them, partial minimization multiplication has many applications in spectral analysis, and it is a very effective chemometric method.
-The partial least squares method can not only comprehensively screen out significant spectral data but also eliminate spectral collinearity problems.
-The main idea of the algorithm is to simplify the data structure and highlight the main contradictory multivariate statistical methods.
+	The NIR spectroscopic data of corn is the most easily accessible high-dimensional public data set on the network.
+In recent years, many papers have analyzed corn data as an example.
+The most common algorithm for analyzing corn infrared spectral data is the PLSR.
+PLSR can effectively reduce the dimensionality of the infrared spectrum.
+This is one of the best ways at the moment.
+Therefore, a large part of the paper is based on the PLS method to improve the accuracy of the prediction.
+And this type of papers always claims that its method has better performance than PLS.
+Although this type of algorithm does show better performance from the results of the analysis, it should be noted that even the same corn NIR data set is analyzed.
+Different sampling methods, different principal component numbers, etc.
+will have an impact on the results.
+Most papers usually show that the new algorithm has smaller RMSECV and RMSEP than PLS.
+however only one regression result cannot judge the superiority of its model.
+And because some specific pre-processing, such as standardization, also makes a big difference in results.
 
-	The infrared spectral data of corn is the most easily obtained high-dimensional infrared spectrum data on the network.
-In recent years, many papers have analyzed corn data as an example.
-The most common algorithm for analyzing corn infrared spectral data is the partial least squares method.
-The partial least squares method can effectively reduce the dimensionality of the infrared spectrum.
-This is one of the best ways at the moment.
-Therefore, a large part of the paper is based on the partial least squares method to improve the accuracy of the prediction.
-And this type of paper also claims that its method has better performance than partial least squares.
-E.g:
+	So the main work of this dissertation is to write a critical overview by reading as much literature as possible about corn data.
+And to find the commonly used options in the partial least squares model, such as different pre-treatment methods, different component selection methods, different cross-validation methods, and so on.
+These may affect the performance of the partial least squares regression model.
+	And then to research the specific effects of each options on the partial least squares regression results based on corn data.
+This part usually uses the results of previous papers as a reference to ensure that the calculation process of dissertation is correct.
+	Finally, my results compares with the results in the papers and proposes a new method to test whether the new algorithm has better performance than PLSR.
 
-	Although this type of algorithm does show better performance from the results of the data, even if you choose the same corn data for analysis, the method of selection, the number of principal components selected, and so on, some related variables will result in the results.
-Make an impact.
-Most papers usually show that the new algorithm has smaller rmsep and rmsep than partial least squares in a regression result.
-So the main research work of this paper is to write a rough critical document by reading as much literature as possible related to corn data.
-Then study how each variable affects the partial least squares regression based on corn data.
-Finally, compare the results in the paper and evaluate whether the new method has more outstanding performance.
+	Of course, as part of dissertation, because there are too many dimensions to explore, and to ensure that the results are stable, it is necessary to perform a sufficient number of loop, which leads to a large amount of calculations in this dissertation.
+In order to solve the problem of computationly heavy, this dissertation first optimizes the code by modifying the program logic for parallel computing.
+Second, by submitting computing tasks to remote servers which is called the high performer computing system, a more stable computing environment and superior computer performance are achieved.
+Finally, because supercomputers have more cores than personal computers, parallel computing will play a bigger role on remote servers.
 
@@
 	\centering           % put the graph(s) in the centre of the page (horizontally)
-	\includegraphics[width=14.5cm, angle=0]{R_cluster.png} % angle changes orientation
+	\includegraphics[width=14.5cm, angle=0]{"R_cluster".jpeg} % angle changes orientation
 	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
@@
 
+	Selecting different sample sizes as a calibration set has two different types of effects on PLSR. The difference between the two different types of effects is mainly in prediction part, the RMSEP.
+
+	The first effect is that as the number of sample in calibration set increases, the prediction of the model will become better and better.
+The RMSEP of PLSR will become smaller and smaller.
+When the number of sample in calibration set reaches a certain limit, the prediction of PLSR will tend to be stable.
+That is to say, regardless of the number of sample in calibration set, the RMSEP will tend to be stable.
+
+	Figure \ref{fig:samples_1} is the PLSR of moisture on m5 which is the first type effect. As the sample size increases, its prediction will stabilize.
+
+				\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-1-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-1-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of moisture on m5 under different number of calibration set.}          % a meaningful caption
+		\label{fig:samples_1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	The effect of the second type is that as the number of sample in calibration set increases, the RMSEP will drop significantly.
+As the sample size continues to increase to a threshold, the RMSEP will be very slowly smaller, but its variance will become larger and larger.
+In other words, the prediction of models will become more and more unstable.
+Please note that this is similar to the model's over-fitting, but it is not.
+The specific impact is that when the sample size is too big, each new sample will bring more but limited information to models, so the overall RMSEP will slowly decline.
+But when the calibration set size is much more than the prediction set, two things will happen.
+One is that the sample from calibration set will surround the predictors.
+This means that when using regression model for prediction, since there are enough calibration points similar to the prediction points, which makes the prediction easy, there may be cases where the RMSEP is extremely low.
+Another situation is that the calibration points do not surround the prediction points.
+The prediction point interval will not match the calibration point interval.
+This will lead to deviations in models.
+This makes RMSEP bigger.
+An extreme case can be considered when there is only one predicted point if the point is an outlier.
+Then the predictions will get very bad.
+
+	As we can see figure \ref{fig:sample_2}.
+The regression of the oil content on mp5 shows that this is second type effect.
+As the sample size increases, RMSEP will continue to decrease, but its variance will decrease first and then increase.
+
+				\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-6-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_calibration/unnamed-chunk-6-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of oil on mp5 under different number of calibration set.}          % a meaningful caption
+		\label{fig:sample_2}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	In order to research the specific impact of sample size on the PLS model. All corn data is used for regression.
+	First select one of the three spectrums as an independent variable $X$.
+Then select one of the four constituents as the dependent variable $Y$.
+Set the number of components to 10.
+Use the leave-one-out cross validation and calculate the RMSECV of the model.
+Then the model is used to predict the remaining prediction samples.
+The predicted error deviation is recorded as RMSEP.
+Observe the changes in RMSECV and RMSEP by changing the number of calibration set samples.
+Finally, different independent variables $X$ from three spectrums and different dependent variables $Y$ from four constituents are selected to continue the PLSR.
+The specific calculation results of the complete partial least squares model are detailed in appendix \ref{app:Number_of_samples}.
+
 	\subsection{Number of components}
 	\label{sec:Number of Components}
+
+	The number of components is the most important parameter in PLSR.
+A change in this parameter will result in a big change in PLSR.
+The number of components represents that several independent variables will be selected as regressions in PLSR.
+As the number of components increases, the regression performe of models should be getting better and better.
+However, when the number of components is too large and over the threshold, there will be a situation of overfitting.
+The model's RMSECV and RMSEP will be reduced to a minimum and then rise again, and the variance will gradually increase during the rise process.
+
+	The figure \ref{fig:component_1} shows that the PLSR of starch content on mp5 under different number of components.
+From the figure \ref{fig:component_1} we can see that when the number of components exceeds 10, RMSECV and RMSEP will become larger and more unstable.
+
+		\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-8-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-8-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of starch on mp5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:component_1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	The reason for the deterioration of the regression model is that too many principal components include some irrelevant details as part of the model, so the prediction set will be poorly predicted.
+This is the significant over-fitting problem we often say.
+
+	All the regression results on different components show in appendix \ref{app:Number_of_components}.
+	It is worth noting that when the independent variable $X$ selects the m5 spectrum, figures \ref{fig:components_1-1}, \ref{fig:components_2-1}, \ref{fig:components_3-1}, \ref{fig:components_4-1} show a trend that violates theory.
+As the number of components selected increases, the RMSECV and RMSEP  will continue to decrease and eventually stabilize.
+The reasons for this trend are not yet explained.
+So in the future this can be used as a research direction.
 
@@
 
+				\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-1-1".png}  % width changes size
+		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-2-1".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of moisture and oil on m5 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:pretreatment-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-3-1".png}  % width changes size
+		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-4-1".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of protein and starch on m5 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:pre-treatment-2}               % label for the figure
+	\end{figure}                        % end of figure environment
+
 	\subsection{Cross-validation}
 	\label{sec:Cross-Validation}
+
+		\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7cm, angle=0]{"LOO cross validation".pdf}  % width changes size
+		\includegraphics[width=7cm, angle=0]{"K-fold cross validation".pdf}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{RMSEP curves for the corn data under LOO cross-validation  and k-fold cross-validation}          % a meaningful caption
+		\label{fig:Cross-validation-1}               % label for the figure
+	\end{figure}                        % end of figure environment
 
@@
 
-	\begin{landscape}
+	The results of PLSR calculated in the previous were compared with the following eight papers.
+In most papers on corn data, PLSR is used as a reference algorithm.
+However, these PLSR results appearing in the paper only give RMSECV and RMSEP.
+This has to question whether the new algorithm is really better than partial least squares regression, or the new algorithm is only one time that the regression result is better than PLSR.
+Therefore, this dissertation uses the same parameters of PLSR as mentioned in other papers to repeat the experiments.
+The average and standard deviation of RMSECV and RMSEP were calculated by repeating 50 experiments every times.
+Then the calculated regression results are compared with the results of those papers.
+	This dissertation compares with the following eight papers. Because the title of papers is too long, each paper is numbered for discussion. The results of the numbering are shown as following.
 
-		\begin{table}[]
-			\begin{tabular}{ll}
-				\hline
-				Number & Paper's title                                                                                                                          \\ \hline
-				1      & A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples \\
-				2      & A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration            \\
-				3      & Reduced PCR/PLSR models by subspace projections                                                                                        \\
-				4      & Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra             \\
-				5      & Cross-validation for the selection of spectral variables using the successive projections algorithm                                    \\
-				6      & A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm                        \\
-				7      & Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD)                                       \\
-				8      & Using consensus interval partial least square in near infrared spectra analysis                                                        
-			\end{tabular}
-			\caption{Papers and related numbers}
-			\label{tab:papers}
-		\end{table}
+	\begin{enumerate}
+		\item A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples \citep{1su2006partial}.
 
-	\end{landscape}
+		\item A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration \citep{2yun2014strategy}.
+
+		\item Reduced PCR/PLSR models by subspace \citep{4ergon2006reduced}.
+
+		\item Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra \citep{5zheng2012stability}.
+
+		\item Cross-validation for the selection of spectral variables using the successive projections algorithm \citep{3galvao2007cross}.
+
+		\item A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm \citep{7galvao2008variable}.
+
+		\item Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD) \citep{6zheng2015pretreating}.
+
+		\item Using consensus interval partial least square in near infrared spectra analysis \citep{8ji2015using}
+
+	\end{enumerate}
+
+	As shown in table \ref{tab:moisture}. The headers of the table mean:
+
+	\begin{enumerate}
+
+	\item Paper: the corresponding number can be found in section \ref{sec:Compare with papers} and each number corresponds to an identical paper.
+
+	\item Data set: the regression models use one of m5, mp5 or mp6 spectrum as an independent variable $X$.
+
+	\item Pre-treatment: preprocessing of corn data and SG(m,p,w) means m differentiation order, p polynomial order and w window size.
+
+	\item Calibration set: the number of calibration set samples, and the corresponding number of prediction set samples is 80 - number of calibration set samples.
+The value in parentheses represent the type of cross validation.
+
+	\item Number of components: the number of  components used in PLSR and it is the same as papers setting.
+
+	\item Moisture: there are two sub-options of RMSECV and RMSEP under Moisture. All data representing this table is the regression of the moisture.
+
+	\item PLS in papers: the PLSR result in corresponding numbered papers.
+
+	\item Developed method: the new algorithm result from corresponding numbered papers.
+
+\end{enumerate}
 
@@
 				4                    & mp5                  & Scale                & 40(LOO)    & 10 &                  & 0.405(0.0467)   &   &        & 0.357  &   &         & 0.265   &   &   &   \\
-				5                    & m5                   & SG(1,2,13)           & 60(3-fold) & 5  &                  & 0.0547(0.00942) &   &        & 0.040  &   &         & 0.012   &   &   &   \\
-				6                    & m5                   & SG(1,2,21)           & 60(LOO)    & 6  &                  & 0.0396(0.00625) &   &        & 0.045  &   &         & 0.019   &   &   &   \\
+				5                    & m5                   & SG(1,2,13)*           & 60(3-fold) & 5  &                  & 0.0547(0.00942) &   &        & 0.040  &   &         & 0.012   &   &   &   \\
+				6                    & m5                   & SG(1,2,21)*           & 60(LOO)    & 6  &                  & 0.0396(0.00625) &   &        & 0.045  &   &         & 0.019   &   &   &   \\
 				8                    & m5                   & Delete 75 , 77       & 52(LOO)    & 10 & 0.0221(0.0018)   & 0.0194(0.00298) &   & 0.0124 & 0.0157 &   & 0.0047  & 0.0056  &   &   &   
@@
 
-			\caption{regression of moisture.The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+			\caption{regression of moisture.The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.
+			*SG(m,p,w)=savitzkyGolay filler with m as differentiation order, p as polynomial order and w as window size.}
 			\label{tab:moisture}
@@
 				3                    & mp5                  & Scale                & 40(LOO)    & 14 &                 & 0.694(0.095)    &   &        & 0.6912 &   &        & 0.6902         &         &    &                 \\
-				5                    & m5                   & SG(1,2,13)           & 60(3-fold) & 12 &                 & 0.0329(0.00672) &   &        & 0.029  &   &        & 0.022          &         &    &                 \\
-				6                    & m5                   & SG(1,2,21)           & 60(LOO)    & 10 &                 & 0.0505(0.0103)  &   &        & 0.028  &   &        & 0.030          &         &    &                 \\
-				7                    & m5                   & SG(0,2,13)           & 64(5-fold) & 7  & 0.0827(0.00419) & 0.0716(0.0116)  &   & 0.0729 & 0.0855 &   &        & 0.0400         &         &    &                 \\
-				7                    & m5                   & SG(1,2,13)           & 64(5-fold) & 7  & 0.0639(0.00357) & 0.0548(0.012)   &   & 0.0577 & 0.0682 &   & 0.0363 & 0.0400         &         &    &                 \\
-				7                    & m5                   & SG(2,2,13)           & 64(5-fold) & 7  & 0.0480(0.00312) & 0.0368 (0.0088) &   & 0.0370 & 0.0397 &   & 0.0363 & 0.0400         &         &    &                 \\
+				5                    & m5                   & SG(1,2,13)*           & 60(3-fold) & 12 &                 & 0.0329(0.00672) &   &        & 0.029  &   &        & 0.022          &         &    &                 \\
+				6                    & m5                   & SG(1,2,21)*           & 60(LOO)    & 10 &                 & 0.0505(0.0103)  &   &        & 0.028  &   &        & 0.030          &         &    &                 \\
+				7                    & m5                   & SG(0,2,13)*           & 64(5-fold) & 7  & 0.0827(0.00419) & 0.0716(0.0116)  &   & 0.0729 & 0.0855 &   &        & 0.0400         &         &    &                 \\
+				7                    & m5                   & SG(1,2,13)*           & 64(5-fold) & 7  & 0.0639(0.00357) & 0.0548(0.012)   &   & 0.0577 & 0.0682 &   & 0.0363 & 0.0400         &         &    &                 \\
+				7                    & m5                   & SG(2,2,13)*           & 64(5-fold) & 7  & 0.0480(0.00312) & 0.0368 (0.0088) &   & 0.0370 & 0.0397 &   & 0.0363 & 0.0400         &         &    &                 \\
 				8                    & m5                   & Delete 75 , 77       & 52(LOO)    & 10 & 0.0651(0.00662) & 0.0604(0.00876) &   & 0.0613 & 0.0673 &   & 0.0483 & 0.0546         &         &    &
@@
 
-			\caption{regression of oil. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+			\caption{regression of oil. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.
+			*SG(m,p,w)=savitzkyGolay filler with m as differentiation order, p as polynomial order and w as window size.}
 			\label{tab:oil}
@@
 				3                    & mp5                  & Scale                & 40(LOO)    & 8  &                  & 0.37(0.0485)  &   &        & 0.4466 &   &        & 0.4349 &   &   &   \\
-				5                    & m5                   & SG(1,2,13)           & 60(3-fold) & 6  &                  & 0.107(0.0195) &   &        & 0.119  &   &        & 0.040  &   &   &   \\
-				6                    & m5                   & SG(1,2,21)           & 60(LOO)    & 7  &                  & 0.102(0.0186) &   &        & 0.110  &   &        & 0.033  &   &   &   \\
+				5                    & m5                   & SG(1,2,13)*           & 60(3-fold) & 6  &                  & 0.107(0.0195) &   &        & 0.119  &   &        & 0.040  &   &   &   \\
+				6                    & m5                   & SG(1,2,21)*           & 60(LOO)    & 7  &                  & 0.102(0.0186) &   &        & 0.110  &   &        & 0.033  &   &   &   \\
 				8                    & m5                   & Delete 75 , 77       & 52(LOO)    & 13 & 0.119 ( 0.0155 ) & 0.11(0.0169)  &   & 0.1080 & 0.1353 &   & 0.0429 & 0.0846 &   &   &   
@@
 
-			\caption{regression of protein. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+			\caption{regression of protein. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.
+			*SG(m,p,w)=savitzkyGolay filler with m as differentiation order, p as polynomial order and w as window size.}
 			\label{tab:protein}
@@
 				3                    & mp5                  & Scale                & 40(LOO)    & 9  &                & 0.513(0.0779) &   &        & 0.5010 &   &        & 0.4443         &         &    &               \\
-				5                    & m5                   & SG(1,2,13)           & 60(3-fold) & 6  &                & 0.239(0.0449) &   &        & 0.196  &   &        & 0.100          &         &    &               \\
-				6                    & m5                   & SG(1,2,21)           & 60(LOO)    & 5  &                & 0.258(0.0453) &   &        & 0.228  &   &        & 0.101          &         &    &               \\
-				7                    & m5                   & SG(0,2,13)           & 64(5-fold) & 8  & 0.333(0.0226)  & 0.283(0.0624) &   & 0.312  & 0.214  &   & 0.240  & 0.219          &         &    &               \\
-				7                    & m5                   & SG(1,2,13)           & 64(5-fold) & 8  & 0.2412(0.0171) & 0.221(0.049)  &   & 0.248  & 0.221  &   & 0.240  & 0.219          &         &    &               \\
-				7                    & m5                   & SG(2,2,13)           & 64(5-fold) & 8  & 0.318(0.0252)  & 0.302(0.061)  &   & 0.347  & 0.228  &   & 0.240  & 0.219          &         &    &               \\
+				5                    & m5                   & SG(1,2,13)*           & 60(3-fold) & 6  &                & 0.239(0.0449) &   &        & 0.196  &   &        & 0.100          &         &    &               \\
+				6                    & m5                   & SG(1,2,21)*           & 60(LOO)    & 5  &                & 0.258(0.0453) &   &        & 0.228  &   &        & 0.101          &         &    &               \\
+				7                    & m5                   & SG(0,2,13)*           & 64(5-fold) & 8  & 0.333(0.0226)  & 0.283(0.0624) &   & 0.312  & 0.214  &   & 0.240  & 0.219          &         &    &               \\
+				7                    & m5                   & SG(1,2,13)*           & 64(5-fold) & 8  & 0.2412(0.0171) & 0.221(0.049)  &   & 0.248  & 0.221  &   & 0.240  & 0.219          &         &    &               \\
+				7                    & m5                   & SG(2,2,13)*           & 64(5-fold) & 8  & 0.318(0.0252)  & 0.302(0.061)  &   & 0.347  & 0.228  &   & 0.240  & 0.219          &         &    &               \\
 				8                    & m5                   & Delete 75 , 77       & 52(LOO)    & 10 & 0.292(0.0312)  & 0.282(0.043)  &   & 0.2579 & 0.2356 &   & 0.1137 & 0.1188         &         &    &
@@
 
-			\caption{regression of starch. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
+			\caption{regression of starch.
+The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.*SG(m,p,w)=savitzkyGolay filler with m as differentiation order, p as polynomial order and w as window size.}
 			\label{tab:starch}
@@
 
+\begin{table}[h]
+			\centering           % put the graph(s) in the centre of the page (horizontally)
+	\begin{tabular}{llllll}
+
+		\hline
+		\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Prediction\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of \\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant \\ F value (0.05)\end{tabular} \\ \hline
+		1 & 20 & 0.159 & 0.139 & 1.31 & 2.124155 \\
+		2 & 16 & 0.0201 & 0.00035 & 3298.04 & 2.333484 \\
+		3 & 40 & 0.3506 & 0.3485 & 1.01 & 1.692797 \\
+		4 & 40 & 0.357 & 0.265 & 1.81 & 1.692797 \\
+		5 & 20 & 0.040 & 0.012 & 11.11 & 2.124155 \\
+		6 & 20 & 0.045 & 0.019 & 5.61 & 2.124155 \\
+		8 & 26 & 0.0157 & 0.0056 & 7.86 & 1.929213
+	\end{tabular}
+\caption{F-test on regression of moisture.}
+\label{tab:F-moisture}
+
+\end{table}
+
+	\begin{table}[h]
+			\centering 
+		\begin{tabular}{llllll}
+			\hline
+			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant\\ F value (0.05)\end{tabular} \\ \hline
+			1 & 20 & 0.107 & 0.0948 & 1.27 & 2.124155 \\
+			3 & 40 & 0.6912 & 0.6902 & 1.00 & 1.692797 \\
+			5 & 20 & 0.029 & 0.022 & 1.74 & 2.124155 \\
+			6 & 20 & 0.028 & 0.030 & 0.87 & 2.124155 \\
+			7 & 16 & 0.0855 & 0.0400 & 4.57 & 2.333484 \\
+			7 & 16 & 0.0682 & 0.0400 & 2.91 & 2.333484 \\
+			7 & 16 & 0.0397 & 0.0400 & 0.99 & 2.333484 \\
+			8 & 26 & 0.0673 & 0.0546 & 1.52 & 1.929213
+		\end{tabular}
+	\caption{F-test on regression of oil.}
+	\label{tab:F-oil}
+	\end{table}
+
+	\begin{table}[h]
+			\centering 
+		\begin{tabular}{llllll}
+			\hline
+			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant\\ F value (0.05)\end{tabular} \\ \hline
+			1 & 20 & 0.150 & 0.145 & 1.07 & 2.124155 \\
+			3 & 40 & 0.4466 & 0.4349 & 1.05 & 1.692797 \\
+			5 & 20 & 0.119 & 0.040 & 8.85 & 2.124155 \\
+			6 & 20 & 0.110 & 0.033 & 11.11 & 2.124155 \\
+			8 & 26 & 0.1353 & 0.0846 & 2.56 & 1.929213
+		\end{tabular}
+		\caption{F-test on regression of protein.}
+	\label{tab:F-protein}
+	\end{table}
+
+	\begin{table}[h]
+					\centering 
+		\begin{tabular}{llllll}
+			\hline
+			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant \\ F value (0.05)\end{tabular} \\ \hline
+			1 & 20 & 0.370 & 0.358 & 1.07 & 2.124155 \\
+			3 & 40 & 0.5010 & 0.4443 & 1.27 & 1.692797 \\
+			5 & 20 & 0.196 & 0.100 & 3.84 & 2.124155 \\
+			6 & 20 & 0.228 & 0.101 & 5.10 & 2.124155 \\
+			7 & 16 & 0.214 & 0.219 & 0.95 & 2.333484 \\
+			7 & 16 & 0.221 & 0.219 & 1.02 & 2.333484 \\
+			7 & 16 & 0.228 & 0.219 & 1.08 & 2.333484 \\
+			8 & 26 & 0.2356 & 0.1188 & 3.93 & 1.929213
+		\end{tabular}
+			\caption{F-test on regression of starch.}
+	\label{tab:F-statch}
+	\end{table}
+
 	\section{Conclusions}
@@
 
+	\clearpage	
 	\addcontentsline{toc}{section}{References} % to add references to table of contents
@@
 
+	\clearpage
 	\begin{appendices}
@@
 			%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-			\caption{The RMSECV and RMSEP from PLSR of moisture on m5 under different number of calibration set}          % a meaningful caption
+			\caption{The RMSECV and RMSEP from PLSR of moisture on m5 under different number of calibration set.}          % a meaningful caption
 			\label{fig:calibration_1-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of oil on m5 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of oil on m5 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_2-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of protein on m5 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of protein on m5 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_3-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of starch on m5 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of starch on m5 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_4-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of moisture on mp5 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of moisture on mp5 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_5-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of oil on mp5 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of oil on mp5 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_6-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of protein on mp5 under different number of calibration set}          % a meaningful caption
-	\label{fig:calibration_6-1}               % label for the figure
+	\caption{The RMSECV and RMSEP from PLSR of protein on mp5 under different number of calibration set.}          % a meaningful caption
+	\label{fig:calibration_7-1}               % label for the figure
 \end{figure}                        % end of figure environment
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of starch on mp5 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of starch on mp5 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_8-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of moisture on mp6 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of moisture on mp6 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_9-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of oil on mp6 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of oil on mp6 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_10-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of protein on mp6 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of protein on mp6 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_11-1}               % label for the figure
@@
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-	\caption{The RMSECV and RMSEP from PLSR of starch on mp6 under different number of calibration set}          % a meaningful caption
+	\caption{The RMSECV and RMSEP from PLSR of starch on mp6 under different number of calibration set.}          % a meaningful caption
 	\label{fig:calibration_12-1}               % label for the figure
@@
 		\section{Number of components}
+		\label{app:Number_of_components}
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-1-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-1-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of moisture on m5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_1-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-2-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-2-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of oil on m5 under different number of components. And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_2-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-3-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-3-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of protein on m5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_3-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-4-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-4-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of starch on m5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_4-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-5-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-5-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of moisture on mp5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_5-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-6-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-6-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of oil on mp5 under different number of components. And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_6-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-7-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-7-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of protein on mp5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_7-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-8-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-8-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of starch on mp5 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_8-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-9-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-9-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of moisture on mp6 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_9-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-10-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-10-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of oil on mp6 under different number of components. And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_10-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-11-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-11-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of protein on mp6 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_11-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-12-1".png}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/number_of_components/unnamed-chunk-12-2".png}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{The RMSECV and RMSEP from PLSR of starch on mp6 under different number of components.
+And 60 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+		\label{fig:components_12-1}               % label for the figure
+	\end{figure}                        % end of figure environment
 
@@
 		\section{Pre-treatment}
+		\label{app:pre-treatment}
+
+			\begin{figure}[h]    % start of figure environment
+			\centering           % put the graph(s) in the centre of the page (horizontally)
+			\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-1-1".png}  % width changes size
+			\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-2-1".png}  % width changes size
+			%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+			\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of moisture and oil on m5 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+			\label{fig:pretreatment-1-1}               % label for the figure
+		\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-3-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-4-1".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of protein and starch on m5 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+	\label{fig:pre-treatment-3-1}               % label for the figure
+\end{figure}                        % end of figure environment
 

### 2019-08-29 MSc Project/parallel PLS for corn data.R

@@ -26,7 +26,7 @@ system.time({
     
     NV <- 10                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(m5data),                  #input data
+    DF <- data.frame(NIR = I(mp5data),                  #input data
                      y=propvals[,1])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
     #str(DF)                                           #check point
@@ -43,7 +43,7 @@ system.time({
     return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
   }
   #corn_PLS(n)
-  n <- as.matrix(rep(60,5))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(40,10))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
   PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results

### 2019-08-29 MSc Project/parallel SavitzkyGlolay PLS for corn data.R

@@ -24,7 +24,7 @@ system.time({
     }))
     propvals <- rawdata$propvals$data
     
-    NV <- 5                                            #number of variables 
+    NV <- 10                                            #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
     DF <- data.frame(NIR = I(m5data),                  #input data
                      y=propvals[,1])
@@ -43,7 +43,7 @@ system.time({
     return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
   }
   #corn_PLS(n)
-  n <- as.matrix(rep(20:70,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(40,100))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
   PlsResult <- parSapply(cl,n,corn_PLS)               #optimizated loop
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results

### 2019-08-29 MSc Project/parallel scaled PLS for corn data.R

@@ -14,10 +14,10 @@ system.time({
     mp5data <-  apply(rawdata$mp5spec$data,2,scale)
     mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
     propvals <- apply(rawdata$propvals$data,2,scale)
-    NV <- 8                                           #number of variables 
+    NV <- 10                                           #number of variables 
     sample <- sample(1:80)                             #set random order; the begin of reset order
-    DF <- data.frame(NIR = I(mp5data),                  #input data
-                     y=propvals[,3])
+    DF <- data.frame(NIR = I(m5data),                  #input data
+                     y=propvals[,1])
     class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
     #str(DF)                                           #check point
     DF$train <- rep(FALSE, 80)
@@ -33,7 +33,7 @@ system.time({
     return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
   }
   #corn_PLS(n)
-  n <- as.matrix(rep(40,50))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
+  n <- as.matrix(rep(40,100))                        #the number of calibration, rep(a:b,c): from a to b and repeat c. 
   #PlsResult <- apply(n,1,corn_PLS)                     #loop
   PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
   PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results

### 2019-08-31 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
finished paper!!!!!!

@@
 \title{The NIR Corn Data Set}
-\author{Hongwei PENG \vspace{2cm} \\
+\author{YZPH8 \vspace{2cm} \\
 	Supervisor : Prof Tom Fearn \vspace{2cm} \\
@@
 	\section{Abstruct}
-	These algorithms will often claim that their new algorithm has a better performs.
-So the purpose of this dissertation is to search for as many different papers as possible, and write a critical overall to find the most efficient measure that can evaluate whether the model performs well and quantify the improvements mentioned in the paper.
+
+	One of the most easily accessible public data sets of high-dimensional NIR spectroscopic data is the so-called corn data.
+Its analysis has been reported in many publications, usually with the claim that some new method of data analysis performs better than the standard ones.
+The most common method of spectral analysis is partial least squares regression (PLSR).
+
+	First of all, the main job of this dissertation is to write a critical overview by reading as much literature as possible about corn data.
+Then summarize the patterns that affect PLSR.
+These patterns include pre-treatment, sample splitting,  number of samples, cross-validation and number of components.
+
+	Second, using the corn data to establish PLS model to research the specific impact of each patterns on the partial least squares regression results.
+Firstly, as the sample size increases, the prediction results of PLSR will get better and better and then tend to be stable or unstable but still keep better.
+Secondly, as the number of components increases, the prediction of PLSR will be better and better, and then worse.
+thirdly standardization is not a good pre-processing in the spectral analysis.
+Usually the effect of using the SavitzkyGolay filter will be better than not doing any pre-processing.
+Finally, the cross validation should be determined based on the original data.
+A k-fold cross validation is recommended when the sample data is too large.
+
+	Moreover, select some papers that use corn data, and repeat the experiments in those papers to summarize the developed methods in papers.
+Analyze whether the difference between the developed methods and the standard method (PLS) is obvious and assess the developed methods made for improvements.
+Furthermore,  evaluate the difference between the developed methods and PLS, and construct an approximate F-statistics to detect whether the performance is significantly improved.
+
+	last but not least, as part of dissertation, because there are too many dimensions to explore, and to ensure that the results are stable, it is necessary to perform a sufficient number of loop, which leads to a large amount of calculations in this dissertation.
+In order to solve the problem of computationly heavy, this dissertation first optimizes the code by modifying the program logic for parallel computing.
+Second, by submitting computing tasks to remote servers which is called the high performer computing system, a more stable computing environment and superior computer performance are achieved.
+Finally, because supercomputers have more cores than personal computers, parallel computing will play a bigger role on remote servers.
 	\newpage           % start a new page
@@
 	\section{Acknowledgements} 
- 	I would thank
+ I would like to thank my supervisor Professor Tom Fearn for his consistent support and guidance during this project.
+
+ I would also like to thank my parents and Chihyi CHANG for supporting me during the compilation of this dissertation.
+
+ Finally, I would also like to thank Dr. Chuling DING and Dr. Kevin Bronik for providing guidance about HPC.
+
 	\newpage           % start a new page
@@
 
-	\section{Literature reviews}
-	\label{sec:liter}
+	%\section{Literature reviews}
+%	\label{sec:liter}
 
@@
 	Firstly, the effect of each conditions on partial least squares regression (PLSR) is observed by different performance of PLSR based on corn data under different conditions.
-Then find out as much papers using corn data as possible to compare the results in papers with the results in dissertation.
+Secondly find out as much papers using corn data as possible to compare the results in papers with the results in dissertation.
 In this way, we can observe whether the new algorithm has a significant improvement compared to PLSR.
@@
 
-	After setting anaconda environment, the interactive operation interface under tmux shell is as figure \ref{fig:R_cluster}.
+	After setting anaconda environment, the interactive operation interface under tmux shell is as Figure \ref{fig:R_cluster}.
 
@@
 Then continue to cycle this process, get the figure of RMSECV and RMSEP based on different loop times.
-Through above steps, the  figure \ref{fig:sd_RMSECV_RMSEP} based on the partial least squares result under different cycle times can be obtained.
-Left graph of figure \ref{fig:sd_RMSECV_RMSEP} is RMSECV and the right boxplot is RMSEP.
+Through above steps, the  Figure \ref{fig:sd_RMSECV_RMSEP} based on the partial least squares result under different cycle times can be obtained.
+Left graph of Figure \ref{fig:sd_RMSECV_RMSEP} is RMSECV and the right boxplot is RMSEP.
 
@@
 The RMSEP standard deviations will decrease with the increase of the loop times, and then tend to be stable.
-Through figure \ref{fig:sd_RMSECV_loop_times_500} it is easy to see that the loop times is around 350, and the standard deviations of RMSEP will show the stable trends.
+Through Figure \ref{fig:sd_RMSECV_loop_times_500} it is easy to see that the loop times is around 350, and the standard deviations of RMSEP will show the stable trends.
 Hence the number of loop times should be set 40$\sim$350 times to get a stable PLSR result.
@@
 
-	As we can see figure \ref{fig:sample_2}.
+	As we can see Figure \ref{fig:sample_2}.
 The regression of the oil content on mp5 shows that this is second type effect.
@@
 Finally, different independent variables $X$ from three spectrums and different dependent variables $Y$ from four constituents are selected to continue the PLSR.
-The specific calculation results of the complete partial least squares model are detailed in appendix \ref{app:Number_of_samples}.
+The specific calculation results of the complete partial least squares model are detailed in Appendix \ref{app:Number_of_samples}.
 
@@
 
-	The figure \ref{fig:component_1} shows that the PLSR of starch content on mp5 under different number of components.
-From the figure \ref{fig:component_1} we can see that when the number of components exceeds 10, RMSECV and RMSEP will become larger and more unstable.
+	The Figure \ref{fig:component_1} shows that the PLSR of starch content on mp5 under different number of components.
+From the Figure \ref{fig:component_1} we can see that when the number of components exceeds 10, RMSECV and RMSEP will become larger and more unstable.
 
@@
 
-	All the regression results on different components show in appendix \ref{app:Number_of_components}.
-	It is worth noting that when the independent variable $X$ selects the m5 spectrum, figures \ref{fig:components_1-1}, \ref{fig:components_2-1}, \ref{fig:components_3-1}, \ref{fig:components_4-1} show a trend that violates theory.
+	All the regression results on different components show in Appendix \ref{app:Number_of_components}.
+	It is worth noting that when the independent variable $X$ selects the m5 spectrum, Figures \ref{fig:components_1-1}, \ref{fig:components_2-1}, \ref{fig:components_3-1}, \ref{fig:components_4-1} show a trend that violates theory.
 As the number of components selected increases, the RMSECV and RMSEP  will continue to decrease and eventually stabilize.
@@
 
-				\begin{figure}[h]    % start of figure environment
-		\centering           % put the graph(s) in the centre of the page (horizontally)
-		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-1-1".png}  % width changes size
-		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-2-1".png}  % width changes size
-		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-		\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of moisture and oil on m5 under different pre-treatment.
-"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
-		\label{fig:pretreatment-1}               % label for the figure
-	\end{figure}                        % end of figure environment
-
-	\begin{figure}[h]    % start of figure environment
-		\centering           % put the graph(s) in the centre of the page (horizontally)
-		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-3-1".png}  % width changes size
-		\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-4-1".png}  % width changes size
-		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
-		\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of protein and starch on m5 under different pre-treatment.
-"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
-		\label{fig:pre-treatment-2}               % label for the figure
-	\end{figure}                        % end of figure environment
+	In section \ref{sec:treat}, there were four common pretreatments.
+The last pre-processing is to delete the outliers.
+When the outliers are deleted, the model can be unaffected by extreme values, so that a better model can be established.
+However, the subjectivity of this scheme is too strong, so quantitative discussions cannot be conducted here.
+So this dissertation focuses on three different treatments.
+	\begin{enumerate}
+	\item Nothing to deal with data \citep{1su2006partial}.
+
+	\item Scale the data \citep{4ergon2006reduced}.
+
+	\item SavitzkyGolay filter processing on the data \citep{3galvao2007cross}.
+
+\end{enumerate}
+
+First, the corn data was divided into two parts, among which 40 samples were randomly selected as the calibration set, and the remaining 40 samples were used as the prediction set.
+Then set the number of components to 10.
+Preprocess the data and then enter 100 cycles PLSR.
+The results of the calculations are available in Appendix \ref{app:pre-treatment}.
+The Figure \ref{fig:pre-treatment-1-1} is the boxplot of RMSECV and RMSEP from 100 loop times PLSR  of oil on m5 under different pre-treatment.
+"1" stands for none pre-treatment; "2" stands for scale $X$; "3" stands for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-2-1".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The boxplot of RMSECV and RMSEP under different pre-treatment.}          % a meaningful caption
+	\label{fig:pre-treatment-1-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+	As can be seen from Figure \ref{fig:pre-treatment-1-1}, standardization is the most inappropriate pre-processing of the data.
+According to all tables in Appendix \ref{app:pre-treatment}, it can be seen that the standardized pretreatment has the worst regression effect for each of the corn spectra.
+	Because it has the largest rmsecv and rmsep.
+This is mainly because the standardization makes the value close to zero become close to "-1".
+Being close to zero in spectroscopy means that the spectrum at this band is meaningless.
+But standardization makes a number that was originally meaningless a non-zero value.
+This brings more useless information to the model.
+This is why standardization is a poor preprocessing method in spectroscopy.
+
+	According to Appendix \ref{app:pre-treatment}, we can see that the regression results of the SavitzkyGolay filter are better than the results of no pre-treatment.
+This is mainly because SavitzkyGolay filter smoothes data, so that the data with the displacement can be corrected, and SavitzkyGolay filter preprocessing makes  regression models more robust.
+However, in some cases, no pre-processing will result in better results, so you need to consider the two before building the model.
 
@@
 
-		\begin{figure}[h]    % start of figure environment
-		\centering           % put the graph(s) in the centre of the page (horizontally)
-		\includegraphics[width=7cm, angle=0]{"LOO cross validation".pdf}  % width changes size
-		\includegraphics[width=7cm, angle=0]{"K-fold cross validation".pdf}  % width changes size
+	According to section \ref{cross-validation}, cross-validation is divided into two categories.
+In this dissertation will discuss leave-one-out cross-validation (LOO) and k-fold cross-validation (K-fold).
+The most intuitive difference is that LOO will consume more computer resources.
+But in fact, when the amount of data is too large, LOO will be more likely to fall into the over-fitting problem.
+
+	In the process of regression modeling, cross-validation is the action that has the least impact on the results.
+However, if an inappropriate cross-validation is chosen, it will lead to overfitting or unstable regression results.
+Cross-validation will influence the process of selecting the number of components in PLSR.
+Figure \ref{fig:Cross-validation-1} is the RMSECV as a function of the number of components.
+The left image is based on LOO and the right image is based on 2-fold.
+It should be noted here that in order to unify the variable names in dissertation, the RMSECV here is the same variable as RMSEP in the cross-validation.
+
+		\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"LOO cross validation".pdf}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"K-fold cross validation".pdf}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{RMSEP curves for the corn data under LOO cross-validation  and k-fold cross-validation.}          % a meaningful caption
+		\label{fig:Cross-validation-1}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	Usually in the process of PLSR, we will select the corresponding number of components according to Figure \ref{fig:Cross-validation-1}.
+The inflection point and the lowest point are usually chosen.
+In Figure \ref{fig:Cross-validation-1}, according to the left side image, 11 will be the number of components under LOO, and according to 2-fold on the right side image, 9 will be the number of components.
+So, if using LOO, a larger number of components will be chosen.
+But Figure \ref{fig:Cross-validation-1} is not obvious, and because k-fold is random, we repeat the 2-fold as much as possible.
+The Figure \ref{fig:Cross-validation-2} shows the results based on 100 times 2-fold cross-validation.
+
+			\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"LOO cross validation2".pdf}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"K-fold cross validation2".pdf}  % width changes size
 		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
 		\caption{RMSEP curves for the corn data under LOO cross-validation  and k-fold cross-validation}          % a meaningful caption
-		\label{fig:Cross-validation-1}               % label for the figure
-	\end{figure}                        % end of figure environment
+		\label{fig:Cross-validation-2}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	Then zoom in Figure \ref{fig:Cross-validation-2} and fix the number of components from 7 to 18 to get Figure \ref{fig:Cross-validation-3}.
+
+	\begin{figure}[h]    % start of figure environment
+		\centering           % put the graph(s) in the centre of the page (horizontally)
+		\includegraphics[width=7.5cm, angle=0]{"LOO cross validation3".pdf}  % width changes size
+		\includegraphics[width=7.5cm, angle=0]{"K-fold cross validation3".pdf}  % width changes size
+		%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+		\caption{RMSEP curves for the corn data under LOO cross-validation  and k-fold cross-validation}          % a meaningful caption
+		\label{fig:Cross-validation-3}               % label for the figure
+	\end{figure}                        % end of figure environment
+
+	As can be seen from the Figure \ref{fig:Cross-validation-3}, the RMSECV based on 2-fold is larger than the RMSECV based on LOO.
+This may cause RMSECV curve based on K-fold to enter the inflection point and the lowest point in advance.
+Thereby a smaller number of components is obtained.
+Moreover, the RMSECV based on LOO will be smaller than RMSECV based in K-fold at the same number of components.
+This is mainly because during the cross-validation process, LOO will use all data excepted one prediction sample to regress the one.
+At this time, the model will have better performance and will make the RMSECV value smaller, so when selecting the principal component, LOO will make people choose the bigger number of components.
+
+	When the amount of sample data is small, the difference between LOO and K-fold is not obvious.
+However, it should be noted that when the amount of data is too large, the large number of principal components obtained from LOO can easily cause the model over-fitting, which is not what we hope.
+Unfortunately, the corn data sample is not large enough, so we can't clearly show the difference between LOO and K-fold here.
+finally, when the sample size looks like big, choosing cross-valiation should be carefully considered to prevent over-fitting problems.
 
@@
 
-	As shown in table \ref{tab:moisture}. The headers of the table mean:
+	As shown in Table \ref{tab:moisture}. The headers of the table mean:
 
@@
 \end{enumerate}
+
+Table \ref{tab:moisture} is the PLSR result of moisture.
+Table \ref{tab:moisture} shows for the first paper, although the developed method has a smaller RMSEP compared to PLSR.
+However, the RMSEP of developed method in first paper is within one-fold variance of RMSEP by PLSR in this dissertation.
+So it's hard to think that the new method has a significant improvement over PLSR.
+The developed method in the second paper got a surprising RMSEP.
+This is a very surprising result and perhaps this is a fact.
+From this paper, we can't see anything obviously wrong, maybe it is true that selecting a small number of wavelengths works better for these data.
+In Table \ref{tab:moisture}, there are two lines of result for the third paper.
+The third paper claims that it uses the m5 spectrum, but in fact, according to the parameters mentioned in this paper, the mp5 spectrum is used to obtain the PLSR result which is more similar to the result in third paper.
+So the third paper might have used a different spectrum than it claimed.
+And according to the PLS result of the third paper, compared with the fourth paper.
+The PLS in third paper may use 10 components instead of the 12 it claims.
+But we can see from the results that its developed method has no better results than PLS.
+In the 4th, 5th 6th and 8th paper, according to the results in Table \ref{tab:moisture}, the developed method does have a better RMSEP than the PLS.
+It shows that these new methods have a better performance in the regression of moisture.
+
+	Table \ref{tab:oil} is a regression result of the oil.
+According to Table \ref{tab:oil}, we can see that the developed method mentioned in the first paper is not very good, because the RMSEP based on developed method is similar to the RMSEP of PLSR.
+The new algorithm based on third paper has not seen a significant improvement compared to the PLSR.
+However, it is hard to judge whether there is not a significant difference between the new method and PLS.
+Also for the fifth paper, although the RMSEP based on the developed algorithm is smaller than the RMSEP based on PLSR, the difference between the new and old algorithm is small, and it is impossible to visually judge whether the developed algorithm and PLSR are significantly different.
+The seventh paper proposes a non-integral Savitzky–Golay differentiation method.
+The developed method has a more significant improvement than integral Savitzky–Golay filters with 0 and 1 differentiation order.
+But there is no way to tell that the new method has a significant difference compared to Savitzky–Golay filters with 2 differentiation order.
+And the new algorithm mentioned in the eighth paper also can not judge the obvious difference with PLS.
+
+	Table \ref{tab:protein} is a regression result of the protein.
+It can be seen from Table \ref{tab:protein} that the developed algorithm regression performance of the first and third paper is not much different from the PLSR.
+Even in some special cases, PLSR shows better regression results.
+The new regression model in the fifth, sixth and eighth paper has a significant improvement over the PLSR.
+
+	Table \ref{tab:starch} is a regression result of the starch.
+Table \ref{tab:starch} shows that the results of the new algorithm in the first, third and seventh paper are not much different from those obtained from PLSR.
+The standard deviation of RMSEP can be used to measure the impact of random sampling on the results.
+From the standard deviation of RMSEP, it can be known that the PLSR has not a big probability that the new algorithm better than it.
+The new methods of the fifth, sixth and eighth papers all perform better than PLSR.
 
@@
 
-	\subsection{Developed method significant test}
+	\subsection{Developed method's significant test}
 	\label{sec: test}
 
+	In section \ref{sec:Compare with papers}, although we calculated the difference between PLS and the developed method, there is no evaluation index to evaluate whether there is a significant difference between the two method.
+Because RMSEP does not obey the common distribution, which is why it is difficult to test, this section gives an approximate test method.
+This method is true when the model's bias is much smaller than the variance.
+According to section \ref{sec:eva}, RMSEP is calculated as follows, it can be divided into two parts, variance and bias.
+
+		\begin{equation}
+	RMSEP^2={\frac{1}{m}\sum_{i=1}^{m} (\hat y_i-y_i)^2}=Var(\hat{y})+Bias(\hat{y},y)^2 \approx Var(\hat{y})
+		\end{equation}
+
+		Here, if the model's bias is much smaller than the variance, then the BIOS can be ignored. Thus, RMSEP obeys the $\chi^2$ distribution.
+
+				\begin{equation}
+		\dfrac{df*Var(\hat{y})}{\sigma} \sim \chi_{df}^2
+		\end{equation}
+		\begin{conditions}
+			df     &  degree of freedom for the prediction set \\
+			\sigma    &    the variance of sample
+		\end{conditions}
+
+		Therefore, the F-value corresponding to the chi-square distribution can be constructed to check whether the difference between the two groups is significant. F value structure is as follows.
+
+				\begin{equation}
+	\frac{RMSEP_{1}^{2}}{RMSEP_{2}^{2}} \sim F(df_1,df_2)
+		\end{equation}
+	\begin{conditions}
+	df     &  degree of freedom for the prediction set and $df_1 = df_2$ in here \\
+	RMSEP_{1}    &    RMSEP based on PLS \\
+	RMSEP_{2}    &    RMSEP based on developed method \\
+\end{conditions}
+
+			The degree of freedom $df$ equals the number m of samples of the prediction set.
+
+		\begin{equation}
+	RMSEP=\sqrt{\frac{1}{m}\sum_{i=1}^{m} \mathrm{e}_{i}^2}
+		\end{equation}
+
+		Where $\mathrm{e}_i \sim N(0,\sigma)$. Therefore, the degrees of freedom of sum of $e_i$ are m.
+
+		The fourth paper on the regression of moisture as an example.
+RMSEP based on PLS equals to 0.357.
+RMSEP based on developed method equals to 0.265.
+So F-value equals to 1.81.
+The number of samples in the prediction set is 40, so under 0.05 confidence level, the F-statistic with 40-40 degrees of freedom equls to 1.692797 which is smaller than the F-value.
+Hence the developed method in the fourth paper is significant better than PLS.
+
+		But what we need to pay attention to is that this is just an approximate test method. There are two main problems with this model.
+
+	\begin{enumerate}
+
+		\item The model assumes that the bias must be much smaller than the variance, which is true in most of time.
+However, in some situation, the bias distribution is non-central chi-square distribution.
+If the bias does not less than the variance, this test will be invalid.
+
+		\item The hypothesis of the F-statistic includes two chi-square distribution variables and are independent to each other.
+But in this test, because the PLSR and the developed method are based on the same data set.
+So $RMSEP_1$ and $RMSEP_2$ are not independent.
+Compared with the previous problem, this trouble will have more serious consequences, so the lack of independence between the two variables is the main factor causing the model to be inaccurate.
+
+	\end{enumerate}
+
+		Although this model has some problems, the test is still of reference. To some extent, it can be explained whether the developed regression method has a significant improvement.
+
+		The calculation results of all the papers are shown in the Table \ref{tab:F-moisture}, \ref{tab:F-oil}, \ref{tab:F-protein} and \ref{tab:F-statch}.
+
+		Table \ref{tab:F-moisture} shows a significant difference in moisture based on PLS and developed method.
+
 \begin{table}[h]
@@
 		\hline
-		\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Prediction\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of \\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant \\ F value (0.05)\end{tabular} \\ \hline
+		\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Prediction\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of \\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F value & \begin{tabular}[c]{@{}l@{}}Significant \\ F statistic (0.05)\end{tabular} \\ \hline
 		1 & 20 & 0.159 & 0.139 & 1.31 & 2.124155 \\
@@
 
+		Table \ref{tab:F-oil} shows a significant difference in oil based on PLS and developed method.
+
 	\begin{table}[h]
@@
 			\hline
-			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant\\ F value (0.05)\end{tabular} \\ \hline
+			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F value & \begin{tabular}[c]{@{}l@{}}Significant\\ F statistic (0.05)\end{tabular} \\ \hline
 			1 & 20 & 0.107 & 0.0948 & 1.27 & 2.124155 \\
@@
 
+		Table \ref{tab:F-protein} shows a significant difference in protein based on PLS and developed method.
+
 	\begin{table}[h]
@@
 			\hline
-			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant\\ F value (0.05)\end{tabular} \\ \hline
+			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F value & \begin{tabular}[c]{@{}l@{}}Significant\\ F statistic (0.05)\end{tabular} \\ \hline
 			1 & 20 & 0.150 & 0.145 & 1.07 & 2.124155 \\
@@
 
+		Table \ref{tab:F-statch} shows a significant difference in statch based on PLS and developed method.
+
 	\begin{table}[h]
@@
 			\hline
-			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F statistic & \begin{tabular}[c]{@{}l@{}}Significant \\ F value (0.05)\end{tabular} \\ \hline
+			\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ PLS in papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed method\end{tabular} & F value & \begin{tabular}[c]{@{}l@{}}Significant \\ F statistic (0.05)\end{tabular} \\ \hline
 			1 & 20 & 0.370 & 0.358 & 1.07 & 2.124155 \\
@@
 
+	This dissertation uses corn data to build PLS models. Study the specific effects of each patterns on PLSR.
+
+	 Firstly, from this dissertation, it can be known that as the number of sample in calibration set increases, the prediction of the model will become better and better.
+The RMSEP of PLSR will become smaller and smaller.
+When the number of sample in calibration set reaches a certain limit, there are two situations.
+The prediction of PLSR will tend to be stable, or the RMSEP will be very slowly smaller, but the prediction of models will become more and more unstable.
+
+	Secondly, the number of components is the most important pattern in PLSR.
+As the number of components increases, the regression performe of models should be getting better and better.
+However, when the number of components is too large and over the threshold, there will be a situation of overfitting.
+The model's RMSECV and RMSEP will reach to a minimum and then rise again, and the variance will gradually and fastly increase during the rise process.
+
+	Thirdly, standardization is the most inappropriate pre-processing of the data.
+Because the standardization makes the value close to zero become close to "-1".
+the pionts close to zero in spectroscopy mean no information.
+But standardization makes those points that was originally meaningless a non-zero value.
+This brings more useless information to the model and chaos the regression.
+This is why standardization is a poor preprocessing method in spectroscopy.
+Furthermore the SavitzkyGolay filter pre-treatment are better than no pre-treatment in most of time.
+Because SavitzkyGolay filter smoothes data and fixes the incorrect displacement, and SavitzkyGolay filter preprocessing makes  regression models more robust.
+However, in some cases, no pre-processing will result in better results.
+
+	Fourthly, in the process of regression modeling, cross-validation is the action that has the least impact on the results.
+However, if an inappropriate cross-validation is chosen, it will lead to overfitting or unstable regression results.
+When the amount of sample data is small, there is no difference between LOO and K-fold.
+However, it should be noted that when the amount of data becomes large, the bigger number of components based on LOO maybe cause the model over-fitting.
+Choosing cross-valiation should be carefully and considering to prevent over-fitting problems.
+
+	Finally, RMSEP does not obey the common distribution, which is why it is difficult to test, this section gives an approximate test method.
+The F-statistic corresponding to the chi-square distribution can be constructed to check whether the difference between the two groups is significant.
+F-value structure is $RMSEP_{1}^{2}/RMSEP_{2}^{2}$.
+
+	As part of dissertation, because this problem is computationly heavy, this dissertation first optimizes the code by modifying the program logic for parallel computing.
+Submitting computing tasks to the high performer computing system (HPC).
+And because supercomputers have more cores than personal computers, parallel computing will play a better role on remote servers.
+
 	\clearpage	
@@
 			\centering           % put the graph(s) in the centre of the page (horizontally)
-			\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-1-1".png}  % width changes size
-			\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-2-1".png}  % width changes size
+			\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-1-1".png}  % width changes size
+			\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-2-1".png}  % width changes size
 			%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
 			\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of moisture and oil on m5 under different pre-treatment.
-"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
 			\label{fig:pretreatment-1-1}               % label for the figure
@@
 	\centering           % put the graph(s) in the centre of the page (horizontally)
-	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-3-1".png}  % width changes size
-	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/figure/unnamed-chunk-4-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-3-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-4-1".png}  % width changes size
 	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
 	\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of protein and starch on m5 under different pre-treatment.
-"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
 	\label{fig:pre-treatment-3-1}               % label for the figure
@@
 
-		\clearpage
-		\section{Cross-validation}
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-5-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-6-1".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of moisture and oil on mp5 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+	\label{fig:pretreatment-5-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-7-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-8-1".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of protein and starch on mp5 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+	\label{fig:pre-treatment-7-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+			\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-9-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-10-1".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of moisture and oil on mp6 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+	\label{fig:pretreatment-9-1}               % label for the figure
+\end{figure}                        % end of figure environment
+
+\begin{figure}[h]    % start of figure environment
+	\centering           % put the graph(s) in the centre of the page (horizontally)
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-11-1".png}  % width changes size
+	\includegraphics[width=7cm, angle=0]{"/Users/hongwei/Documents/GitHub/STAT/MSc Project/paper_writing/pre-treatment/unnamed-chunk-12-1".png}  % width changes size
+	%\vspace*{-0.25cm}    % manual adjustment of vertical spacing
+	\caption{The boxplot of RMSECV and RMSEP from 100 loop times PLSR of protein and starch on mp6 under different pre-treatment.
+"1" stand for none pre-treatment; "2" stand for scale $X$; "3" stand for savitzkyGolay filler with 1differentiation order, 2 polynomial order, 21 window size.
+And 40 samples as calibration set take leave-one-out as cross validation.}          % a meaningful caption
+	\label{fig:pre-treatment-11-1}               % label for the figure
+\end{figure}                        % end of figure environment
 

### 2019-08-31 MSc Project/parallel-cross-validation.R

@@ -1,0 +1,167 @@
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")   # Myriad dir
+
+
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+#m5data <- m5data[,c(-75,-77)]
+#propvals <- propvals[,c(-75,-77)]
+n <- 80
+NV <- 40                                           #number of variables 
+sample <- sample(1:80)                             #set random order; the begin of reset order
+DF <- data.frame(NIR = I(mp5data),                  #input data
+                 y=propvals[,4])
+class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
+#str(DF)                                           #check point
+DF$train <- rep(FALSE, 80)
+DF$train[sample<=n] <- TRUE                        #chose calibration
+corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
+plot(RMSEP(corn.pls), legendpos = "topright",xlab="Number of components", ylab="RMSECV(RMSEP in cross-validation process)",main="PLS of starch on mp5 with leave-one-out cross-validation")
+corn.pls1 <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="CV",K=3, jackknife = TRUE, subset = train)
+plot(RMSEP(corn.pls1), legendpos = "topright",xlab="Number of components", ylab="RMSECV(RMSEP in cross-validation process)",main="PLS of starch on mp5 with 3-fold cross-validation")
+
+
+
+
+
+
+
+
+
+
+
+
+
+library(R.matlab)
+library(pls) 
+library(lars)
+library(ggplot2)
+library(parallel)                                      # 载入parallel包
+clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
+cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
+Myriad_flag=F                                        # myriad_flag TRUE means in cluster environment 
+if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
+{
+  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
+} else {
[…]

### 2019-08-31 MSc Project/parallel-pre-treatment.R

@@ -1,12 +1,12 @@
 ---
-title: "Parallel all papers PLS for corn data"
+  title: "Parallel all papers PLS for corn data"
 author: "Hongwei Peng"
 date: "28/08/2019"
 output: html_document
 ---
-
-#1~m5
-```{r echo=FALSE,warning=FALSE,message=FALSE}
+  
+  #1~m5
+  ```{r echo=FALSE,warning=FALSE,message=FALSE}
 library(R.matlab)
 library(pls) 
 library(lars)
@@ -64,7 +64,7 @@ system.time({
   #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
   #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
   ##if (Myriad_flag==TRUE) {
-   # #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
+  # #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
   #}
   clnum
 })
@@ -265,7 +265,7 @@ system.time({
   #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
   #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
   ##if (Myriad_flag==TRUE) {
-   # #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
+  # #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
   #}
   clnum
 })
@@ -466,7 +466,7 @@ system.time({
   #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
   #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
   #if (Myriad_flag==TRUE) {
-    #save(PlotData,file="1~m5_Number_of_Calibration_set_PlotData.RData")                  # save results in myriad
[…]

### 2019-09-05 MSc Project/PPT_writing/presentation_MSc_project_Hongwei.tex
finish dissertation！！！！

% comment out (using a %) exactly 1 of the 2 lines immediately below
%\documentclass[handout]{beamer}   % to produce a handout
\documentclass{beamer}             % to produce slide show with pauses etc.

%\usepackage{xeCJK}
%\setCJKmainfont{SimSun}

\usepackage{ucltemplate}
\usepackage{hyperref}  % to enable hyperlinks to websites to be produced.
   \usepackage[utf8]{inputenc}

\setbeamertemplate{footline}{\normalsize\hfill\insertframenumber/\inserttotalframenumber} % add slide number

\newenvironment{conditions}[1][where:]
{%
	#1\tabularx{\textwidth-\widthof{#1}}[t]{
		>{$}l<{$} @{${}={}$} X@{}
	}%
}
{\endtabularx\\[\belowdisplayskip]}

\setbeamertemplate{navigation symbols}{} %no navigation symbols on the bottom right of the slides

% To force beamer to include table and figure numbers
% This is just for the purposes of the STAT0034 workshop: usually one would not want cross-references in a presentation
\setbeamertemplate{caption}[numbered]

% for nice-looking inequality signs
\let\leq=\leqslant
\let\geq=\geqslant

% Choose the color you like
\usecolortheme{lightblue}
%\usecolortheme{black}
%\usecolortheme{darkred}

% Pick a colour (a blue) for the weblinks
\definecolor{links}{HTML}{2B65EC}
\hypersetup{colorlinks, linkcolor=, urlcolor = links}

% Information for title page
\title{\bf The NIR Corn Data Set}
\author{Hongwei PENG \vspace{1cm} \\
	Supervisor : Prof Tom Fearn\\
	Department of Statistical Science \\
	University College London}
\institute{Department of Statistical Science}
\date{\today}

% Start the document
\begin{document}

\begin{frame}
	\titlepage
\end{frame}

	\begin{frame}{Datasets}
	Corn data is the most readily available high-dimensional Near-infrared spectral data. This data was published on the Internet (http://www.eigenvector.com/data/Corn/index.html) by Eigenvector Research, Inc. in 2005. The data consisted of 80 corn samples measured on three different NIR spectrometers named m5, mp5 and mp6. The spectral wavelength range is 1100$\sim$2498nm with an interval of 2nm. Hence there are 700 channels for each spectrum in each sample. Figure is the plot of spectra on m5 and mp5.
\end{frame}

\begin{frame}{Datasets}

	% A picture can be included as an pdf using \includegraphics
	% The construction below with tabular and minipage is one
	% way to create a good layout.
	\begin{tabular}{cc}
		\begin{minipage}{2in}
			\includegraphics[width=2.2in]{Spectra_on_instrument_m5.pdf}
		\end{minipage}
		&
		\begin{minipage}{2in}
			\includegraphics[width=2.2in]{Spectra_on_instrument_mp5.pdf}
		\end{minipage}
	\end{tabular}
\end{frame}

		\begin{frame}
				\begin{tabular}{cc}
					\begin{minipage}{5in}
				\includegraphics[width=4.3in]{tab-moisture.png}
					\end{minipage}
					\end{tabular}
		\end{frame}

	\begin{frame}[containsverbatim]{Compare with papers}

\begin{table}[h]
	\centering           % put the graph(s) in the centre of the page (horizontally)

	\begin{tabular}{llllll}

		\hline
		\multicolumn{1}{c}{Paper} & \begin{tabular}[c]{@{}l@{}}Prediction\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP\\ of PLS in\\ papers\end{tabular} & \begin{tabular}[c]{@{}l@{}}RMSEP of\\ developed\\ method\end{tabular} & F value & \begin{tabular}[c]{@{}l@{}}Significant \\ F statistic\\ (0.05)\end{tabular} \\ \hline
		1 & 20 & 0.159 & 0.139 & 1.31 & 2.124155 \\
		2 & 16 & 0.0201 & 0.00035 & 3298.04 & 2.333484 \\
		3 & 40 & 0.3506 & 0.3485 & 1.01 & 1.692797 \\
		4 & 40 & 0.357 & 0.265 & 1.81 & 1.692797 \\
		5 & 20 & 0.040 & 0.012 & 11.11 & 2.124155 \\
		6 & 20 & 0.045 & 0.019 & 5.61 & 2.124155 \\
		8 & 26 & 0.0157 & 0.0056 & 7.86 & 1.929213
	\end{tabular}
	\caption{F-test on regression of moisture.}
	\label{tab:F-moisture}

\end{table}

	\end{frame}

	\begin{frame}[containsverbatim]{Compare with papers}

	In section, although we calculated the difference between PLS and the developed method, there is no evaluation index to evaluate whether there is a significant difference between the two method. Because RMSEP does not obey the common distribution, which is why it is difficult to test, this section gives an approximate test method. This method is true when the model's bias is much smaller than the variance. According to section, RMSEP is calculated as follows, it can be divided into two parts, variance and bias.

	\begin{equation}
	RMSEP^2={\frac{1}{m}\sum_{i=1}^{m} (\hat y_i-y_i)^2}=Var(\hat{y})+Bias(\hat{y},y)^2 \approx Var(\hat{y})
	\end{equation}

	Here, if the model's bias is much smaller than the variance, then the BIOS can be ignored. Thus, RMSEP obeys the $\chi^2$ distribution.

	\begin{equation}
	\dfrac{df*Var(\hat{y})}{\sigma} \sim \chi_{df}^2
	\end{equation}

	Therefore, the F-value corresponding to the chi-square distribution can be constructed to check whether the difference between the two groups is significant. F value structure is as follows.

	\begin{equation}
	\frac{RMSEP_{1}^{2}}{RMSEP_{2}^{2}} \sim F(df_1,df_2)
	\end{equation}

		\end{frame}

\end{document}

### 2019-09-05 MSc Project/matplot.R
save

@@ -12,9 +12,41 @@ test <- aggregate(x=PlotData[c("V2",'V3')], by = list(PlotData$V1), FUN=sd)
 plot(test$Group.1,test$V2,xlab="Loop times", ylab="Standard deviation",main="RMSECV",cex.lab=1.5,cex.main=1.5)
 plot(test$Group.1,test$V3,xlab="Loop times", ylab="Standard deviation",main="RMSEP",cex.lab=1.5,cex.main=1.5)
 
+
+
+
 library(ChemometricsWithR)
 wavelengths<-seq(1100, 2498,by=2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <- rawdata$m5spec$data
+mp5data <- rawdata$mp5spec$data
+mp6data <- rawdata$mp6spec$data
+propvals <- rawdata$propvals$data
+matplot(wavelengths,t(m5data),lty=1,pch=NULL,type="l",xlab="wavelengths(nm)",ylab="abs",main="Spectra on instrument m5 ")
 
-matplot(wavelengths,t(mp5data),lty=1,pch=NULL,type="l",xlab="wavelengths(nm)",ylab="abs",main="Spectra on instrument m5 ")
-Spectra_on_instrument_m5
-plot(m5data[1,])
+
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <-  apply(rawdata$m5spec$data,2,scale)
+mp5data <-  apply(rawdata$mp5spec$data,2,scale)
+mp6data <-  apply(rawdata$mp6spec$data,2,scale) 
+propvals <- apply(rawdata$propvals$data,2,scale)
+matplot(wavelengths,t(m5data),lty=1,pch=NULL,type="l",xlab="wavelengths(nm)",ylab="abs",main="Scaled spectra on instrument m5 ")
+
+
+library(prospectr)
+wavelengths<-seq(1100, 2458,by=2)
+rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
+m5data <-  t(apply(rawdata$m5spec$data,1,function(x) {
+  savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+}))
+mp5data <- t(apply(rawdata$mp5spec$data,1,function(x) {
+  savitzkyGolay(x,1,2,21)                          #SavitzkyGolay filler
+}))
+mp6data <- t(apply(rawdata$mp6spec$data,1,function(x) {
[…]
